### 2017-05-17 Paper/plos-latex-template/plos_latex_template.tex
early draft of paper

% Template for PLoS
% Version 3.3 June 2016
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Research Synergy and Drug Development: Bright Stars in Neighboring Constellations} % Please use "title case" (capitalize all terms in the title except conjunctions, prepositions, and articles).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Samet Keserci\textsuperscript{1},
%Samet Keserci\textsuperscript{1,2\Yinyang},
Eric Livingston\textsuperscript{2},
Lingtian Wan\textsuperscript{1,\textcurrency},
Alexander R. Pico\textsuperscript{3},
%Name5 Surname\textsuperscript{2\ddag},
%Name6 Surname\textsuperscript{2\ddag},
George Chacko\textsuperscript{1*},
%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Netelabs, NET ESolutions Corporation, McLean, VA, USA
\\
\textbf{2} Elsevier Research Intelligence, Elsevier Inc., Bethesda, MD, USA
\\
\textbf{3} Gladstone Institutes, University of California San Francisco, San Francisco, CA, USA
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
%\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
%\ddag These authors also contributed equally to this work.

% Current address notes
\textcurrency Current Address: Facebook Corporation, Menlo Park, CA, USA % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address 
% \textcurrency c Insert third current address

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
*Correspondence: george@nete.com
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}

Scientific advances such as development of a new drug or biological are collaborative and involve the contributions of many scientists.  Data mining and network analysis of public and commercial data sources can be used to describe the set of collaborative activities or `cure networks' that result in new therapeutics. To explore the relationship across cure networks- the extent to which nodes are common across networks, we have conducted case studies of five anti-cancer therapeutics. We have mined data drawn from public and commercial sources, constructed linkages based on unique identifiers, and modeled the data as networks. We have enriched the content of these networks by annotating them with information on awards that supported the research in these networks as well as peer review that preceded these awards. This approach can be extended beyond drug development to study any major scientific advance. Such studies support portfolio analysis and a public understanding of the benefits of research, this methodology can be extended beyond cures to scientific advances in general. [In fact we're talking about the digital transformation of science history scholarship].[These studies help us understand that which came before and leave it in a form that others can use].[cite Jean-Michel Maldame's work]

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author Summary}
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}

Data mining of public data sources coupled with network analysis allows the assembly and quantitative description of research discoveries that were influential in the development of a breakthrough therapeutic or `cure' \cite {bib1}.  The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents progress from basic research to a cure is termed a `cure network'. Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will uncover previous influential discovery (\textit{ibid}).

Williams and colleagues have elegantly demonstrated the feasibility of this approach using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}). These authors observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-related research over a period greater than 100 years. Such studies provide evidence for the  broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases, support strategic communications to oversight bodies, and communication of the societal value of research \cite {bib2}.

Extending the methodology to study additional cures as well as other significant research advances is a logical next step. Ascertaining the nature of the interactions, if any, between networks, is also of considerable interest since it would support an understanding of common features of science networks as well as research events that have been influential across multiple networks.

To address these questions, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer. We have extended the original approach to (i) include a data from a commercially available bibliographic database with disambiguated author identifiers (ii) modified the original data mining methods and network metrics (iii) added new node types to include grants and peer review data (iv) refactored the network analysis code of Williams et al. for better performance. (v) mapped publications and authors across all five networks. We present the results of these case studies as a step towards mapping the universe of FDA-approved drugs and biologicals.

% Place tables after the first paragraph in which they are cited.
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Case Studies of Five Anti-Cancer Agents}}
\vspace{1.5 mm}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline

%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & FDA Approval Date & Unique Identifier & US Patent & Publication Date  \\ \hline
$Alemtuzumab$ & May 2001 & BLA: 103948 & US5846534 & Dec 1998\\ \hline
$Imatinib$ & May 2001 & NDA: 021335 & US5521184 &  May 1996 \\ \hline
$Nelarabine$ & Oct 2005 & NDA: 021877 & US5424295 & Jun 1995  \\ \hline
$Ramucirumab$ & Apr 2014 & BLA: 125477 & US7498414 & Mar 2009  \\ \hline
$Sunitinib$ & Jan 2006  & NDA: 021938  & US6573293 & Jun 2003 \\ \hline
\end{tabular}
\vspace{1.5 mm}
\begin{flushleft} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies. The active ingredient for each of these five therapeutics is listed in column 1. While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic. The publication date for each patent is listed in the last column. 
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

\section*{Materials and Methods}

A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans between 2001 and 2014, were chosen for this study (Table 1). Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab are humanized antibodies that target cell surface receptors.

For each of these therapeutics, a set of relevant citations was constructed based on the assumptions articulated by Williams et al. but with specific modifications detailed below. An allowance of 2 months was also made for `publication lag' when assembling referenced material. For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included. A first generation of citations was created as a list of PubMed IDs (pmids) harvested from seven different data sources (below).  
\begin {itemize}
\item Clinical trials. The national clinical trials database (clinicaltrials.gov) was searched for clinical trials of the five therapeutics that completed on or the data of FDA approval. Both cited references and publications from these clinical trials were collected if they were published within the approval date plus two months period. PubMed was also searched with the unique identifier (NCT number) of any clinical trials that were identified to capture publications associated with the clinical trials that were not displayed in clinical trials.gov. To capture clinical trials publications that are not available in clinicaltrials.gov, PubMed was searched using the therapeutic name as keyword, publication type as "clinical trial", and an appropriate date restriction as in searches of clinicaltrials.gov. For example, the search term ((("alemtuzumab"[Supplementary Concept] OR "alemtuzumab"[All Fields]) OR ("alemtuzumab"[Supplementary Concept] OR "alemtuzumab"[All Fields] OR "campath"[All Fields])) AND ("1900/0101"[PDAT] : "2001/07/31"[PDAT])) AND "clinical trial"[Publication Type] was used to identify publications typed as clinical trials for Alemtuzumab that were published on or before July 31, 2001.

\item Regulatory documents. drugs@fda (https://www.accessdata.fda.gov/scripts/cder/daf/) was searched for each of the five therapeutics and cited references in the medical review of the approval process were manually extracted and matched to pmids.

\item FDA Approval Summaries. These articles published in journals by FDA staff (approval summaries were available for all five therapeutics), contain cited references that were extracted using Scopus. approval summaries were available for all five therapeutics. If the published date of a citation exceeded the approval date plus two months, the publication was not included.

\item Patents. For each therapeutic a single patent was identified that best represented the most relevant invention to the therapeutic at hand. Identification of a patent was performed using multiple web sources: PubMed, Google Patents, EspaceNet, and drugbank.ca. The US patent number was used to identify the patent and the non-patent citation list from Google patent was manually processed by searching PubMed for appropriate pmids. While we developed a citation matching tool for non-patent literature, the precision and recall rates from manual searches was far higher and were used to generate the data in this study.

\item Reviews: We treated review articles published after FDA approval  as independent documents describing the development of a therapeutic. Accordingly, PubMed was searched for review articles of a therapeutic that were published between the date of FDA approval and one year following the date of approval. Cited references in these reviews were also extracted as above.

\item Literature searches were also performed using PubMed with a date range of 1900/01/01 to two months post-FDA approval. For example, the search term ((alemtuzumab) OR campath) AND ("1900/01/01"[Date - Publication] : "2001/07/31"[Date - Publication]) was used to retrieve articles of interest relevant to alemtuzumab.
\end{itemize}

Pmids from the seven different sources above (citing\_pmid) were combined, deduplicated, and matched to Scopus IDs (citing\_eid) using Scopus APIs. These eids were used to extract cited references (cited\_eid), which were then mapped back to pmids (cited\_pmid). The data are summarized in Table 2. Using the Scopus database, this list was mapped to Scopus eids and a second generation of cited references was extracted. These were mapped to pmids First and second generation pmids were both mapped to NIH grants and peer review data using information made publicly available by NIH. The resultant data were modeled as hierarchical networks using a simple dictionary of N node types to unambiguously identify nodes and interactions between them. The networks were analyzed using metrics based on network topology.

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Mapping Publications}}
\vspace{1.5 mm}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & citing\_pmid count & citing\_eid count & cited\_eid count  & cited\_pmid count  \\ \hline
$Alemtuzumab$ & 599 & 587 & 8840 & 7071\\ \hline
$Imatinib$ & 1380 & 1373 & 27326 &  23340 \\ \hline
$Nelarabine$ & 104 & 104 & 2476 & 1990  \\ \hline
$Ramucirumab$ & 1820 & 1804 & 48587 & 40973  \\ \hline
$Sunitinib$ & 1512  & 1509  & 33895 & 28661 \\ \hline
\end{tabular}
\vspace{1.5 mm}
\begin{flushleft} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies. The active ingredient for each of these five therapeutics is listed in column 1. While multiple patents are often associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic. The publication date for each patent is listed in the last column. 
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

Available awards (projects) and link tables publications up to 2016 were downloaded from NIH ExPORTER and used to link publications to NIH awards and study sections where grant applications were reviewed for scientific merit before an award was made. The assembled data were modeled as a network for each therapeutic and stored as node lists and edge lists. 
exporter

For these data, we calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams \cite {bib1}  with some modifications to the RBR as follows. The original RBR was defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author. The background dataset was constructed by keyword searches of PubMed. However, a potential weakness of the keyword based approach is that keywords do not effectively capture the field or the total ouput of an author even if multiple background samples are taken. We created two new variants, nRBR and dRBR. nRBR uses all publications in our set of five therapeutics as background. dRBR takes advantage of the Scopus author\_id to capture the total output of an author and use it as background.

Citation data for all five networks were combined and a globalPIR score was calculated. The globalPIR score was normalized to the sum of PIR scores within each network.

\subsection*{Etiam eget sapien nibh.}

% For figure citations, please use "Fig" instead of "Figure".
Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Place figure captions after the first paragraph in which they are cited.
\begin{figure}[!h]
\caption{{\bf Bold the figure title.}
Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

% Results and Discussion can be combined.
\section*{Results and Discussion}

No idea what to say...

%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}
\subsubsection*{3rd Level Heading.}

Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat.

\begin{enumerate}
	\item{react}
	\item{diffuse free particles}
	\item{increment time by dt and go to 1}
\end{enumerate}

\subsection*{Sed ac quam id nisi malesuada congue.}

Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\begin{itemize}
	\item First bulleted item.
	\item Second bulleted item.
	\item Third bulleted item.
\end{itemize}

\section*{Discussion}

Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero~\cite{bib3}.

\section*{Conclusion}

CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Appendix}.

\section*{Supporting Information}

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 File.}
\label{S1_File}
{\bf Lorem Ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Video.}
\label{S1_Video}
{\bf Lorem Ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Appendix.}
\label{S1_Appendix}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

\begin{eqnarray}
\label{eq:schemeP} 
	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
\end{eqnarray}

\nolinenumbers

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
\begin{thebibliography}{10}

\bibitem{bib1}
Williams RS, Lotia S., Holloway AK, Pico AR.
\newblock {{F}rom Scientific Discovery to Cures: Bright Stars within a Galaxy.}
\newblock Cell. 2015 Sep; 163:21--23

\bibitem{bib2}
Lauer MS.
\newblock {{P}CSK9 Inhibitors: Lots of Work Done, Lots More to Do.}
\newblock Ann Intern Med. 2016 Mar; 164(9):624-625.

\bibitem{bib3}
Wang M., Zhao Y.., Zhang B.
\newblock {{E}fficient Test and Visualization of Multi-Set Intersections.}
\newblock Sci. Rep. 2015 Nov; doi:10.1038/srep16923

\bibitem{bib4}
O'Shea JJ, Kanno, Y., Chan AC.
\newblock {{I}n Search of Magic Bullets: The Golden Age of Immunotherapeutics}
\newblock Cell. 2014 Mar; 157:227-240

\bibitem{bib5}
Maldame, J.
\newblock {{T}he Importance Of The History Of Science In Intellectual Formation}
\newblock Scripta Varia 2002 104:237-248

\bibitem{bibn}
Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
infection through a transposon insertion followed by a {D}uplication}.
\newblock PLoS Genet. 2011 Oct;7(10):e1002337.

\end{thebibliography}

\end{document}

### 2017-05-22 assembly/load_interim_results.R
used colClasses to coerce SID to character

@@ -3,18 +3,18 @@ rm(list=ls())
 # Load 9 csv files from Eric Livingston into a list
 
 setwd("~/NETELabs_CaseStudies/assembly/interim_results")
-temp <- list.files(pattern="*.csv")
-interim_results <- list()
-for (i in 1:length(temp)) {
-	interim_results[[i]] <- read.csv(temp[i],stringsAsFactors=FALSE,header=TRUE)
-}
-names(interim_results) <- temp
-rm(i)
-save(interim_results,file="interim_results.RData")
+#temp <- list.files(pattern="*.csv")
+#interim_results <- list()
+#for (i in 1:length(temp)) {
+#	interim_results[[i]] <- read.csv(temp[i],stringsAsFactors=FALSE,header=TRUE)
+#}
+#names(interim_results) <- temp
+#rm(i)
+#save(interim_results,file="interim_results.RData")
 
-# Extract pub_out (pmid-SID) and pub_cites (PubSID to SID) from list as data frames
-pub_out <- interim_results[['pub_out.csv']]
-pub_cites <- interim_results[['pub_cites.csv']]
+# Read in pub_out (pmid-SID) and pub_cites (PubSID to SID) 
+pub_out <- read.csv("pub_out.csv",colClasses=rep("character",6))
+pub_cites <- read.csv("pub_cites.csv",colClasses=rep("character",9))
 # free up memory
 rm(interim_results)
 # print str stats
@@ -23,15 +23,15 @@ str(pub_cites)
 
 # load Stage I files that Eric used to generate pub_out and pub_cites
 alem <- read.csv("~/NETELabs_CaseStudies/assembly/alemtuzumab_assembly/alem_eric_stage1.csv",
-stringsAsFactors=FALSE)
+colClasses=c(rep("character,9")))
 imat <- read.csv("~/NETELabs_CaseStudies/assembly/imatinib_assembly/imat_eric_stage1.csv",
-stringsAsFactors=FALSE)
+colClasses=c(rep("character,9")))
 nela <- read.csv("~/NETELabs_CaseStudies/assembly/nelarabine_assembly/nela_eric_stage1.csv",
-stringsAsFactors=FALSE)
+colClasses=c(rep("character,9")))
 ramu <- read.csv("~/NETELabs_CaseStudies/assembly/ramucirumab_assembly/ramu_eric_stage1.csv",
-stringsAsFactors=FALSE)
[…]

### 2017-05-23 assembly/load_interim_results.R
fixed syntax error

@@ -3,35 +3,35 @@ rm(list=ls())
 # Load 9 csv files from Eric Livingston into a list
 
 setwd("~/NETELabs_CaseStudies/assembly/interim_results")
-#temp <- list.files(pattern="*.csv")
-#interim_results <- list()
-#for (i in 1:length(temp)) {
+# temp <- list.files(pattern="*.csv")
+# interim_results <- list()
+# for (i in 1:length(temp)) {
 #	interim_results[[i]] <- read.csv(temp[i],stringsAsFactors=FALSE,header=TRUE)
 #}
-#names(interim_results) <- temp
-#rm(i)
-#save(interim_results,file="interim_results.RData")
+# names(interim_results) <- temp
+# rm(i)
+# save(interim_results,file="interim_results.RData")
 
 # Read in pub_out (pmid-SID) and pub_cites (PubSID to SID) 
 pub_out <- read.csv("pub_out.csv",colClasses=rep("character",6))
 pub_cites <- read.csv("pub_cites.csv",colClasses=rep("character",9))
 # free up memory
-rm(interim_results)
+# rm(interim_results)
 # print str stats
 str(pub_out)
 str(pub_cites)
 
 # load Stage I files that Eric used to generate pub_out and pub_cites
 alem <- read.csv("~/NETELabs_CaseStudies/assembly/alemtuzumab_assembly/alem_eric_stage1.csv",
-colClasses=c(rep("character,9")))
+colClasses=c(rep("character",9)))
 imat <- read.csv("~/NETELabs_CaseStudies/assembly/imatinib_assembly/imat_eric_stage1.csv",
-colClasses=c(rep("character,9")))
+colClasses=c(rep("character",9)))
 nela <- read.csv("~/NETELabs_CaseStudies/assembly/nelarabine_assembly/nela_eric_stage1.csv",
-colClasses=c(rep("character,9")))
+colClasses=c(rep("character",9)))
 ramu <- read.csv("~/NETELabs_CaseStudies/assembly/ramucirumab_assembly/ramu_eric_stage1.csv",
-colClasses=c(rep("character,9")))
+colClasses=c(rep("character",9)))
 suni <- read.csv("~/NETELabs_CaseStudies/assembly/sunitinib_assembly/suni_eric_stage1.csv",
-colClasses=c(rep("character,9")))
+colClasses=c(rep("character",9)))
 
[…]

### 2017-05-23 Paper/plos-latex-template/plos_latex_template.tex
edits

@@
 \documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+\usepackage[top=0.85in,left=2in,footskip=0.75in]{geometry}
 
@@
 \setlength{\headheight}{27.023pt}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\lhead{\includegraphics[width=3.0in]{PLOS-submission.eps}}
 \rfoot{\thepage/\pageref{LastPage}}
 \renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
+\fancyheadoffset[L]{1.25in}
+\fancyfootoffset[L]{1.25in}
 \lfoot{\sf PLOS}
@@
 %Name6 Surname\textsuperscript{2\ddag},
-George Chacko\textsuperscript{1*},
+ \& George Chacko\textsuperscript{1*}
 %with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
@@
 
-Scientific advances such as development of a new drug or biological are collaborative and involve the contributions of many scientists.
-Data mining and network analysis of public and commercial data sources can be used to describe the set of collaborative activities or `cure networks' that result in new therapeutics.
-To explore the relationship across cure networks- the extent to which nodes are common across networks, we have conducted case studies of five anti-cancer therapeutics.
-We have mined data drawn from public and commercial sources, constructed linkages based on unique identifiers, and modeled the data as networks.
-We have enriched the content of these networks by annotating them with information on awards that supported the research in these networks as well as peer review that preceded these awards.
-This approach can be extended beyond drug development to study any major scientific advance.
-Such studies support portfolio analysis and a public understanding of the benefits of research, this methodology can be extended beyond cures to scientific advances in general.
-[In fact we're talking about the digital transformation of science history scholarship].[These studies help us understand that which came before and leave it in a form that others can use].[cite Jean-Michel Maldame's work]
+Drug discovery and the subsequent availability of new breakthrough therapeutics or `cures' are compelling examples of societal benefit from advances in research.
+Such advances are invariably collaborative, involving the contributions of many scientists building upon prior theory and experiment.
+Data mining of public and commercial data sources coupled with analysis of `cure networks' is a scalable digital methodology for assembling and analyzing the scientific history of these advances.
+The methodology for assembling is extensible beyond cure networks and such studies support (i) efficiency in  exploring  science history (ii) an improved documenting and understanding of collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
+In addition, they help make the scientific environment more citizen-accessible.
+Building upon techniques for single cure networks, we have conducted a case study of five anti-cancer therapeutics for the purpose of exploring the relationship across these networks.
+We have enriched the content of these networks by annotating them with information on research awards as well as peer review that preceded these awards.
+Applying retrospective citation discovery, we have identified a core set of publications cited in the networks for all five therapeutics and additional intersections in pairwise interactions between networks.
 
@@
 \linenumbers
-
 % Use "Eq" instead of "Equation" for equation citations.
@@
 
-Data mining of public data sources coupled with network analysis allows the assembly and quantitative description of research discoveries that were influential in the development of a breakthrough therapeutic or `cure' \cite {bib1}.
-The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents progress from basic research to a cure is termed a `cure network'.
+Data mining of public data sources coupled with network analysis allows the assembly and quantitative description of research discoveries that were influential in the development of a breakthrough therapeutic or `cure'.
+The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents progress from basic research to a cure is termed a `cure network' \cite {bib1}.
 Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will uncover previous influential discovery (\textit{ibid}).
-
 Williams and colleagues have elegantly demonstrated the feasibility of this approach using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}).
 These authors observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-related research over a period greater than 100 years.
-Such studies provide evidence for the  broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases, support strategic communications to oversight bodies, and communication of the societal value of research \cite {bib2}.
 
-Extending the methodology to study additional cures as well as other significant research advances is a logical next step.
-Ascertaining the nature of the interactions, if any, between networks, is also of considerable interest since it would support an understanding of common features of science networks as well as research events that have been influential across multiple networks.
+Such studies provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases, support strategic communications to oversight bodies, and communication of the societal value of research\cite {bib2,bib3}.
+Extending this digital methodology to study additional cures as well as significant research advances in general is a logical next step.
+Ascertaining the nature of the interactions, if any, between networks, is also of considerable interest since it would support an understanding of collaboration across networks as well as common features of science networks.
 
@@
 (v) mapped publications and authors across all five networks.
+
 We present the results of these case studies as a step towards mapping the universe of FDA-approved drugs and biologicals.
+Beyond drug discovery and cures, however, this simple digital methodology can be used to support efficient explorations of science history, gain an understanding of collaboration across domains, enrich portfolio analysis, planning and optimization, enable communications of the societal value of research, and help make the scientific environment more citizen-accessible.
 
+\section*{Materials and Methods} 
 % Place tables after the first paragraph in which they are cited.
+A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration was selected for this study (Table 1).
+Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab are humanized antibodies that target cell surface receptors.
+ For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.\cite{bib1} but with specific modifications detailed below.
+An allowance of 2 months was made for `publication lag' when assembling referenced material.
+For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included.
+For each of the five therapeutics, a first-generation list of PubMed IDs (citing\_pmid) was harvested from the five different data sources (below).
 \begin{table}[!ht]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-\caption{
-{\bf Case Studies of Five Anti-Cancer Agents}}
-\vspace{1.5 mm}
+\scalebox{0.9}{
 \begin{tabular}{|l+l|l|l|l|l|l|l|}
 \hline
-
 %\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
@@
 $Sunitinib$ & Jan 2006  & NDA: 021938  & US6573293 & Jun 2003 \\ \hline
-\end{tabular}
-\vspace{1.5 mm}
-\begin{flushleft} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies.
+\end{tabular}}
+\vspace{2 mm}
+\caption{
+{\bf Case Studies of Five Anti-Cancer Agents} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies.
 The active ingredient for each of these five therapeutics is listed in column 1.
 While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic.
-The publication date for each patent is listed in the last column.
-\end{flushleft}
+The publication date for each patent is listed in the last column.}
+%\begin{flushleft}  
+%\end{flushleft}
 \label{table1}
-\end{adjustwidth}
+%\end{adjustwidth}
 \end{table}
 
-\section*{Materials and Methods}
-
-A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans between 2001 and 2014, were chosen for this study (Table 1).
-Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab are humanized antibodies that target cell surface receptors.
-
-For each of these therapeutics, a set of relevant citations was constructed based on the assumptions articulated by Williams et al.
-but with specific modifications detailed below.
-An allowance of 2 months was also made for `publication lag' when assembling referenced material.
-For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included.
-A first generation of citations was created as a list of PubMed IDs (pmids) harvested from seven different data sources (below).
-\begin {itemize}
-\item Clinical trials.
-The national clinical trials database (clinicaltrials.gov) was searched for clinical trials of the five therapeutics that completed on or the data of FDA approval.
+\textbf{Clinical trials} The national clinical trials database (clinicaltrials.gov) was searched for clinical trials of the five therapeutics that completed on or the data of FDA approval.
 Both cited references and publications from these clinical trials were collected if they were published within the approval date plus two months period.
 PubMed was also searched with the unique identifier (NCT number) of any clinical trials that were identified to capture publications associated with the clinical trials that were not displayed in clinical trials.gov.
-To capture clinical trials publications that are not available in clinicaltrials.gov, PubMed was searched using the therapeutic name as keyword, publication type as "clinical trial", and an appropriate date restriction as in searches of clinicaltrials.gov.
-For example, the search term ((("alemtuzumab"[Supplementary Concept] OR "alemtuzumab"[All Fields]) OR ("alemtuzumab"[Supplementary Concept] OR "alemtuzumab"[All Fields] OR "campath"[All Fields])) AND ("1900/0101"[PDAT] : "2001/07/31"[PDAT])) AND "clinical trial"[Publication Type] was used to identify publications typed as clinical trials for Alemtuzumab that were published on or before July 31, 2001.
+To capture clinical trials publications that are not available in clinicaltrials.gov, PubMed was searched using the therapeutic name as keyword, publication type as ``clinical trial'', and an appropriate date restriction as in searches of clinicaltrials.gov.
+For example, the search term (((``alemtuzumab"[Supplementary Concept] OR ``alemtuzumab"[All Fields]) OR (``alemtuzumab"[Supplementary Concept] OR ``alemtuzumab"[All Fields] OR ``campath"[All Fields])) AND (``1900/0101"[PDAT] : ``2001/07/31''[PDAT])) AND ``clinical trial"[Publication Type] was used to identify publications of clinical trials for Alemtuzumab.
 
-\item Regulatory documents.
-drugs@fda (https://www.accessdata.fda.gov/scripts/cder/daf/) was searched for each of the five therapeutics and cited references in the medical review of the approval process were manually extracted and matched to pmids.
-
-\item FDA Approval Summaries.
-These articles published in journals by FDA staff (approval summaries were available for all five therapeutics), contain cited references that were extracted using Scopus.
-approval summaries were available for all five therapeutics.
+\textbf{FDA documents} The drugs@fda website\cite{bib6} was searched for each of the five therapeutics and cited references in the medical review document were manually extracted and matched to pmids.
+FDA Approval Summaries, articles published in journals by FDA staff, were available for all five therapeutics and contain cited references.
 If the published date of a citation exceeded the approval date plus two months, the publication was not included.
 
-\item Patents.
-For each therapeutic a single patent was identified that best represented the most relevant invention to the therapeutic at hand.
-Identification of a patent was performed using multiple web sources: PubMed, Google Patents, EspaceNet, and drugbank.ca.
-The US patent number was used to identify the patent and the non-patent citation list from Google patent was manually processed by searching PubMed for appropriate pmids.
-While we developed a citation matching tool for non-patent literature, the precision and recall rates from manual searches was far higher and were used to generate the data in this study.
+\textbf{Patents} For each therapeutic a single patent was identified that best represented the most relevant invention to the therapeutic at hand.
+Identification of this patent was performed using multiple web sources.
+The US patent number was then used to identify the patent and the non-patent citation list from Google Patents \cite{bib8} was manually processed by searching PubMed for appropriate pmids.
+While we developed a citation matching tool for non-patent literature for this purpose, the precision and recall rates from manual searches was far higher and were used to generate the data in this study.
 
-\item Reviews: We treated review articles published after FDA approval  as independent documents describing the development of a therapeutic.
-Accordingly, PubMed was searched for review articles of a therapeutic that were published between the date of FDA approval and one year following the date of approval.
-Cited references in these reviews were also extracted as above.
+\textbf{Post-approval literature reviews} Review articles published after a therapeutic's approval by the FDA are independent assessments of the the development of a therapeutic.
+Accordingly, PubMed was searched for review articles of a therapeutic that were published between the date of FDA approval and one year following the date of approval and cited references in these reviews were extracted using PubMed and Scopus.
 
-\item Literature searches were also performed using PubMed with a date range of 1900/01/01 to two months post-FDA approval.
-For example, the search term ((alemtuzumab) OR campath) AND ("1900/01/01"[Date - Publication] : "2001/07/31"[Date - Publication]) was used to retrieve articles of interest relevant to alemtuzumab.
-\end{itemize}
+\textbf{Pre-approval literature searches} Literature searches were performed using PubMed with a date range of 1900/01/01 to two months post-FDA approval.
+For example, the search term ((alemtuzumab) OR campath) AND (``1900/01/01"[Date - Publication] : ``2001/07/31"[Date - Publication]) was used to retrieve articles of interest relevant to alemtuzumab.
 
-Pmids from the seven different sources above (citing\_pmid) were combined, deduplicated, and matched to Scopus IDs (citing\_eid) using Scopus APIs.
-These eids were used to extract cited references (cited\_eid), which were then mapped back to pmids (cited\_pmid).
-The data are summarized in Table 2.
-Using the Scopus database, this list was mapped to Scopus eids and a second generation of cited references was extracted.
-These were mapped to pmids First and second generation pmids were both mapped to NIH grants and peer review data using information made publicly available by NIH.
-The resultant data were modeled as hierarchical networks using a simple dictionary of N node types to unambiguously identify nodes and interactions between them.
-The networks were analyzed using metrics based on network topology.
+Citing\_pmids from the five different sources above  were combined and deduplicated.
+Using the Scopus database and its APIs, these citing\_pmids were mapped to ScopusIds (citing\_sid) and a second generation of cited references (cited\_sid) was extracted., These cited\_sids, were in turn, mapped back to pmids (cited\_pmid).
+Whereas mapping between PubMed and Scopus identifiers at the citing\_pmid and citing\_eid stage resulted in 1\% or less information loss, mapping at the cited\_eid to cited\_pmid resulted in 15-20 \% information loss.
+Accordingly the Scopus data  was used as the backbone of the publication component of the network and cited\_pmid was treated as an annotation layer.
+These observations are summarized in Table 2 and include the count of null values when mapping from citing\_sid to cited\_sid.
 
 \begin{table}[!ht]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-\caption{
-{\bf Mapping Publications}}
-\vspace{1.5 mm}
-\begin{tabular}{|l+l|l|l|l|l|l|l|}
+\scalebox{0.9}{\begin{tabular}{|l+l|l|l|l|l|l|l|}
 \hline
@@
 Therapeutic & citing\_pmid count & citing\_eid count & cited\_eid count  & cited\_pmid count  \\ \hline
-$Alemtuzumab$ & 599 & 587 & 8840 & 7071\\ \hline
-$Imatinib$ & 1380 & 1373 & 27326 &  23340 \\ \hline
-$Nelarabine$ & 104 & 104 & 2476 & 1990  \\ \hline
-$Ramucirumab$ & 1820 & 1804 & 48587 & 40973  \\ \hline
-$Sunitinib$ & 1512  & 1509  & 33895 & 28661 \\ \hline
-\end{tabular}
-\vspace{1.5 mm}
-\begin{flushleft} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies.
-The active ingredient for each of these five therapeutics is listed in column 1.
-While multiple patents are often associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic.
-The publication date for each patent is listed in the last column.
-\end{flushleft}
-\label{table1}
-\end{adjustwidth}
+$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
+$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
+$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
+$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
+$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
+\end{tabular}}
+\vspace{2.5 mm}
+\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies.
+A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature.
+Citing\_pmids were mapped to Scopus identifiers (citing\_eid), which were used, in turn, to retrieve literature cited by this foundational set (cited\_eid).
+Cited\_eids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field}
+\label{table2}
+%\end{adjustwidth}
 \end{table}
 
-Available awards (projects) and link tables publications up to 2016 were downloaded from NIH ExPORTER and used to link publications to NIH awards and study sections where grant applications were reviewed for scientific merit before an award was made.
-The assembled data were modeled as a network for each therapeutic and stored as node lists and edge lists.
-exporter
+Citing and cited pmids were both mapped to NIH grants and peer review panels using information made publicly available by NIH through NIH ExPORTER.
+Since Special Emphasis Panels vary in scientific interests from year to year, we restricted our mapping to chartered study sections, which have defined scientific interests and relatively stable reviewer membership.
+The resultant data were modeled as hierarchical networks and analyzed using metrics based on network topology.
+We calculated the propagated in-degree rank (PIR) metric of Williams \cite {bib1}.
+PIR represents the sum of weighted citation scores for all articles in a network that can be attributed to an author.
+In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a globalPIR score, which was normalized to the sum of PIR scores within each network.
 
-For these data, we calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams \cite {bib1}  with some modifications to the RBR as follows.
-The original RBR was defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author.
-The background dataset was constructed by keyword searches of PubMed.
-However, a potential weakness of the keyword based approach is that keywords do not effectively capture the field or the total ouput of an author even if multiple background samples are taken.
-We created two new variants, nRBR and dRBR.
-nRBR uses all publications in our set of five therapeutics as background.
-dRBR takes advantage of the Scopus author\_id to capture the total output of an author and use it as background.
-
-Citation data for all five networks were combined and a globalPIR score was calculated. The globalPIR score was normalized to the sum of PIR scores within each network.
+We also calculated the RBR metric of Williams et al.
+(\textit{ibid}) with some modifications.
+The RBR metric is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author.
+In its original specification, the background dataset for RBR was constructed by keyword searches of PubMed.
+A potential weakness of this keyword based approach is that keywords do not effectively capture the field or the total output of an author even if multiple background samples are taken.
+Therefore, we created two new variants of the RBR; network RBR (nRBR) and document-based RBR (dRBR).
+nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total output of an author and use it as background.
+Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively.
 
@@
 \section*{Results and Discussion}
+\subsection*{Network Features}
+\subsection*{Intersection Across Networks} this is a 
+\subsection*{Supporting awards and peer-review}
+\subsection*{Future Directions}
+
+\begin{table}[!ht]
+%\begin{adjustwidth}{-0.51in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\vspace{2.5 mm}
+\scalebox{0.8}{
+\begin{tabular}{|l| l| l| l| l| l| l| l|}
+\hline
+alem(A) & imat(I) & nela(N) & ramu(R) & suni(S) & combination  & intersection\_count &no\_of\_drugs\\ 
+ \hline
+%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
+X & X & X & X & X & AINRS &  \textbf{14} & 5 \\ 
+\hline
+X & X &  & X & X & AIRS & \textbf{107} & 4 \\ 
+\hline
+X & X & X & X &  & AINR &  28 & 4 \\ 
+\hline
+X & X & X &  & X & AINS &  25 & 4 \\ 
+\hline
+& X & X & X & X & INRS &  22 & 4 \\ 
+\hline
+X &  & X & X & X & ANRS &  16 & 4 \\ 
+\hline 
+& X &  & X & X & IRS & \textbf{1762} & 3 \\ 
+\hline
+X & X &  & X &  & AIR & 231 & 3 \\ 
+\hline
+X & X &  &  & X & AIS & 211 & 3 \\ 
+\hline
+X &  &  & X & X & ARS & 156 & 3 \\ 
+\hline
+X & X & X &  &  & AIN &  81 & 3 \\ 
+\hline
+X &  & X & X &  & ANR &  56 & 3 \\ 
+\hline 
+& X & X &  & X & INS &  49 & 3 \\ 
+\hline
+& X & X & X &  & INR &  44 & 3 \\ 
+\hline
+ &  & X & X & X & NRS &  40 & 3 \\ 
+\hline
+X &  & X &  & X & ANS &  32 & 3 \\ 
+\hline 
+&  &  & X & X & RS & \textbf{7442} & 2 \\ 
+\hline
+& X &  &  & X & IS & 5415 & 2 \\ 
+\hline
+& X &  & X &  & IR & 2507 & 2 \\ 
+\hline
+X & X &  &  &  & AI & 1240 & 2 \\ 
+\hline
+X &  &  & X &  & AR & 448 & 2 \\ 
+\hline
+X &  &  &  & X & AS & 359 & 2 \\ 
+\hline
+X &  & X &  &  & AN & 334 & 2 \\ 
+\hline 
+& X & X &  &  & IN & 232 & 2 \\ 
+\hline
+&  & X & X &  & NR & 115 & 2 \\ 
+\hline 
+ &  & X &  & X & NS & 111 & 2 \\ 
+\hline
+&  &  & X &  & R & \textbf{49006} & 1 \\ 
+\hline 
+&  &  &  & X & S & 34257 & 1 \\ 
+\hline 
+& X &  &  &  & I & 27706 & 1 \\ 
+\hline
+X &  &  &  &  & A & 8978 & 1 \\ 
+\hline
+&  & X &  &  & N & 2498 & 1 \\ 
+\hline
+\end{tabular}}
+\vspace{2.5 mm}
+\caption{
+{\bf Intersecting Publications Across Networks} Intersections were calculated for the set of publications associated with each network.
+Both citing and cited references were included in each set and  Scopus identifiers were used to to minimize information loss (Table 2).
+Intersection counts are shown for all possible combinations of the five therapeutics.
+The largest intersection count in each combination group is shown in boldface.
+Therapeutic names are abbreviated as follows: Alemtuzumab as alem(A), Imatinib as imat(I), Nelarabine as nela(N), Ramucirumab as ramu(R), and Sunitinib as suni(S).
+}
+
+%\begin{flushleft} Intersections were calculated for the set of publications associated with each network.
+Both citing and cited references were included in each set and  Scopus Ids were used as identifiers to minimize loss of data when mapping back to pmids.
+Intersection counts are shown for all possible combinations of the five therapeutics.
+The largest intersection count in each combination group is shown in boldface.
+%\end{flushleft}
+\label{table3}
+%\end{adjustwidth}
+\end{table}
 
@@
 
+\bibitem{bib6}
+Federal Drug Administration.
+\newblock {{D}rugs@FDA: FDA Approved Drug Products}
+\newblock https://www.accessdata.fda.gov/scripts/cder/daf/
+
+\bibitem{bib7}
+National Institutes of Health.
+\newblock {{N}IH ExPORTER}
+\newblock https://exporter.nih.gov/
+
+\bibitem{bib8}
+Google Corporation
+\newblock {{G}oogle Patents}
+\newblock https://patents.google.com/
+
 \bibitem{bibn}

### 2017-05-25 Paper/plos-latex-template/plos_latex_template.tex
today's edits

@@
 Drug discovery and the subsequent availability of new breakthrough therapeutics or `cures' are compelling examples of societal benefit from advances in research.
-Such advances are invariably collaborative, involving the contributions of many scientists building upon prior theory and experiment.
-Data mining of public and commercial data sources coupled with analysis of `cure networks' is a scalable digital methodology for assembling and analyzing the scientific history of these advances.
-The methodology for assembling is extensible beyond cure networks and such studies support (i) efficiency in  exploring  science history (ii) an improved documenting and understanding of collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
-In addition, they help make the scientific environment more citizen-accessible.
-Building upon techniques for single cure networks, we have conducted a case study of five anti-cancer therapeutics for the purpose of exploring the relationship across these networks.
-We have enriched the content of these networks by annotating them with information on research awards as well as peer review that preceded these awards.
-Applying retrospective citation discovery, we have identified a core set of publications cited in the networks for all five therapeutics and additional intersections in pairwise interactions between networks.
+Such advances are invariably collaborative, involving the contributions of many scientists in a `cure network' where prior theory and experiment is built upon.
+Data mining of public and commercial data sources coupled with network analysis is a scalable digital methodology for assembling and analyzing the history of scientific advances.
+This methodology is extensible beyond cure networks and its use supports (i) efficiency in  exploring  the scientific history of a research advance (ii) improved documenting and understanding of collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
+Building upon prior techniques for single cure networks and linking the work of approximately 200,000 authors in 100,000 scientific publications, we have conducted a case study of five anti-cancer therapeutics for the purpose of exploring the relationship across networks.
+We have enriched the content of these five networks by annotating them with information on research awards as well as peer review that preceded these awards.
+Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as a core set of awards from the National Institutes of Health that supported this research.
+Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented by these networks.
 
@@
 For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included.
-For each of the five therapeutics, a first-generation list of PubMed IDs (citing\_pmid) was harvested from the five different data sources (below).
+For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (below).
 \begin{table}[!ht]
@@
 \textbf{Clinical trials} The national clinical trials database (clinicaltrials.gov) was searched for clinical trials of the five therapeutics that completed on or the data of FDA approval.
-Both cited references and publications from these clinical trials were collected if they were published within the approval date plus two months period.
-PubMed was also searched with the unique identifier (NCT number) of any clinical trials that were identified to capture publications associated with the clinical trials that were not displayed in clinical trials.gov.
-To capture clinical trials publications that are not available in clinicaltrials.gov, PubMed was searched using the therapeutic name as keyword, publication type as ``clinical trial'', and an appropriate date restriction as in searches of clinicaltrials.gov.
+Both cited references and publications from these clinical trials were collected if they were published within the approval date plus two months.
+To capture publications associated with the clinical trials that were not displayed in clinical trials.gov, PubMed was also searched with the unique identifier (NCT number) of any clinical trials that were identified.
+To capture publications of clinical trials not registered in clinicaltrials.gov, PubMed was searched using the therapeutic name as keyword, publication type as ``clinical trial'', and an appropriate date restriction as in searches of clinicaltrials.gov.
 For example, the search term (((``alemtuzumab"[Supplementary Concept] OR ``alemtuzumab"[All Fields]) OR (``alemtuzumab"[Supplementary Concept] OR ``alemtuzumab"[All Fields] OR ``campath"[All Fields])) AND (``1900/0101"[PDAT] : ``2001/07/31''[PDAT])) AND ``clinical trial"[Publication Type] was used to identify publications of clinical trials for Alemtuzumab.
@@
 The US patent number was then used to identify the patent and the non-patent citation list from Google Patents \cite{bib8} was manually processed by searching PubMed for appropriate pmids.
-While we developed a citation matching tool for non-patent literature for this purpose, the precision and recall rates from manual searches was far higher and were used to generate the data in this study.
+While we developed a citation matching tool for non-patent literature for this purpose, the accuracy of manual searches was far higher and were used to generate the data in this study.
 
@@
 Citing\_pmids from the five different sources above  were combined and deduplicated.
-Using the Scopus database and its APIs, these citing\_pmids were mapped to ScopusIds (citing\_sid) and a second generation of cited references (cited\_sid) was extracted., These cited\_sids, were in turn, mapped back to pmids (cited\_pmid).
-Whereas mapping between PubMed and Scopus identifiers at the citing\_pmid and citing\_eid stage resulted in 1\% or less information loss, mapping at the cited\_eid to cited\_pmid resulted in 15-20 \% information loss.
-Accordingly the Scopus data  was used as the backbone of the publication component of the network and cited\_pmid was treated as an annotation layer.
+Using the Scopus database and its APIs, these citing\_pmids were mapped to Scopus identifiers (citing\_sid) from which a second generation of cited references (cited\_sid) was extracted., These cited\_sids, were in turn, mapped back to pmids (cited\_pmid).
+Whereas mapping between PubMed and Scopus identifiers at the citing\_pmid and citing\_sid stage resulted in 1\% or less information loss, mapping at the cited\_sid to cited\_pmid resulted in 15-20 \% information loss.
+Accordingly the Scopus data  was used as the backbone of the publication component of the network and the cited\_pmid information was treated as an annotation layer.
 These observations are summarized in Table 2 and include the count of null values when mapping from citing\_sid to cited\_sid.
-
-\begin{table}[!ht]
-%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\scalebox{0.9}{\begin{tabular}{|l+l|l|l|l|l|l|l|}
-\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
-Therapeutic & citing\_pmid count & citing\_eid count & cited\_eid count  & cited\_pmid count  \\ \hline
-$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
-$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
-$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
-$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
-$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
-\end{tabular}}
-\vspace{2.5 mm}
-\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies.
-A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature.
-Citing\_pmids were mapped to Scopus identifiers (citing\_eid), which were used, in turn, to retrieve literature cited by this foundational set (cited\_eid).
-Cited\_eids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field}
-\label{table2}
-%\end{adjustwidth}
-\end{table}
 
@@
 nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total output of an author and use it as background.
-Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively.
+Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively.\\
+\vspace{2.5 mm}
+
+\textbf{Notation and Calculations}
+\begin {itemize}
+\item $d_i =$  therapeutic, e.g., alemtuzumab(alem) or imatinib(imat)
+\item $N_i =$ the network of a therapeutic $d_i$;
+\item $\mathcal{N}$ = union of all networks $N_i$
+\item $\mathcal{G}$ the global network - the set of all authors and publications in $\mathcal{N}$ 
+\item $\mathcal{M}$ the set of all subnetworks - ie $\{N_1,N_2,N_3,N_4,N_5\}$
+\item $c_n(\mathfrak{p})$ citation of a publication $\mathfrak{p}$ in a network $n$
+\item $\mathcal{C}_\mathfrak{p}^n$ =the set of publications which cites $\mathfrak{p}$ in a network $n$
+\item $wc_n(\mathfrak{p})$  weighted citation of a publication $\mathfrak{p}$ in a network $n$
+\item $\mathcal{A}_\mathfrak{a}^n$ the set of publications for an author $\mathfrak{a}$ in a network $n$
+\item $pir_n(\mathfrak{a})$ the PIR  score of an author in a Network $n$ in $\mathcal{M}$
+\item $npir(\mathfrak{a})$ the PIR score of an author  $\mathfrak{a}$ in the Network  $\mathcal{N}$ 
+\item $ir(\mathfrak{a})$ partitioning of a research metric for an author $\mathfrak{a}$ 
+\item $ic_{d_i}(\mathfrak{a})$ = total \# in-degree count for an author $\mathfrak{a}$  for drug $d_i$. (ie. = $\|\mathcal{A}_\mathfrak{a}^{d_i}\|$)
+\item $ic_n(\mathfrak{a})$ = total \# in-degree count for an author $\mathfrak{a}$  in  $\mathcal{N}$ (i.e = $\|\mathcal{A}_\mathfrak{a}^{N}\|$)
+\item $ nrbr_{d_i}(\mathfrak{a}) $ modified RBR score normalized to its network $\mathcal{N}$ for a drug $d_i$
+\item $ grbr_{d_i}(\mathfrak{a}) $ modified RBR score normalized to the global network $\mathcal{G}$  for a drug $d_i$
+\end{itemize}
+
+\textbf{PIR Score}: We define the global network $\mathcal{N}$ as the union of the each individual sub-network of a therapeutic $d_i$. In other words 
+$$ \mathcal{N} = \cup_{i =1}^{5} \mathcal{N}_i $$
+Let $c_n(\mathfrak{p})$ be the citation score of the the paper $\mathfrak{p}$ in a network $n$, and $\mathcal{C}_\mathfrak{p}^n$ be the set of publication which cites $\mathfrak{p}$.
+Then we define the weighted citation of a paper $\mathfrak{p}$ as $$wc_n(\mathfrak{p}) = c_n(\mathfrak{p}) + \sum_{g\in \mathcal{C}_\mathfrak{p}^n}  c_n(g) $$
+Let $\mathcal{A}_a^n$ be the set of publications for an author $\mathfrak{a}$ in a Network $n$.
+Then the PIR score  for an author $\mathfrak{a}$  in network $n$ is defined as $$ pir_n(\mathfrak{a}) =  \sum_{p\in \mathcal{A}_a^n}  wc_n(\mathfrak{p}) $$
+
+More simply, the PIR score for an author  $\mathfrak{a}$ in a Network $n$ is  $$ pir_n(\mathfrak{a}) =  \sum_{p\in \mathcal{A}_a^n } \big[c_n(p) + \sum_{g\in \mathcal{C}_\mathfrak{p}^n}  c_n(g)\big] $$
+
+Next we define the nPIR score $npir(\mathfrak{a})$, which is $pir$ score based on the  total network $\mathcal{N}$.
+For convenience, instead of denoting it $pir_N$, we use $npir$   Furthermore  we define the isolation of  research  metric $ir(\mathfrak{a}):\mathcal{R}\rightarrow [1,\infty]$  of an author $\mathfrak{a}$ as
+$$ir(\mathfrak{a})= \dfrac{ npir({\mathfrak{a}})} {\sum_{1}^{5} pir_{d_i}(\mathfrak{a})} $$
+where $\mathcal{R}$ is the set of all authors in $\mathcal{N}$  and  $pir_{d_i}(\mathfrak{a})$ is the PIR score of the author $\mathfrak{a}$ restricted to only drug network $\mathcal{D}_i$ .
+If $ir(\mathfrak{a})$ approaches 1, the author's $\mathfrak{a}$ contribution to each drug is partitioned.
+The greater the $ir$, the closer  the interaction of the author's papers between the networks.
+
+\textbf{RBR Score}:
+\begin{itemize}
+\item nRBR or network RBR is the ratio of an authors' count of publications in a network to the total number of the publications in the global Network. 
+Lets define in-degree count $ic_{d_i}(\mathfrak{a})$ of an author $\mathfrak{a}$ as the total number of the publication which is in the network $\mathcal{N}_i$ of the drug $d_i$, similarly lets $ic_{n}$ be the number of the paper that author $\mathfrak{a}$ published in the total Network(5-drug's network) $\mathcal{N}$.
+Then we define, nRBR of an author $\mathfrak{a}$  for a drug $d_i$ as follow.
+$$ nrbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{N}(\mathfrak{a})}$$
+\item gRBR or global RBR is the ratio of an author's count of publications in a network to the author's total publication count.
+$\mathcal{G}$.
+Thus, $grbr$ score of an author  $\mathfrak{a}$  for the drug $d_i$ is defined as
+$$grbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{G}(\mathfrak{a})}$$
+where $ic_{G}$ is the total number of publication that an author $\mathfrak{a}$ currently has.
+\end{itemize}
 
@@
 % Place figure captions after the first paragraph in which they are cited.
+
+% Results and Discussion can be combined.
+\section*{Results and Discussion}
+
+Scientific publications form the backbone of each of these five networks.
+The initial assumptions of appropriate citation and retrospective citation discovery (Introduction) suggest that network nodes that are common to multiple networks are likely to be influential.
+Accordingly.
+we explored the extent and nature of intersections across networks, we calculated intersection counts for all possible combinations of Alemtuzumab, Imatinib, Nelarabine, Ramucirumab, and Sunitinib (Table 3).
+14 publications are cited in all five networks and are shown in Table 4.
+
+\begin{table}[!ht]
+\begin{adjustwidth}{-1.0in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\scalebox{0.8}{\begin{tabular}{|l+l|l|l|l|l|l|l|}
+\hline
+%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
+\hline
+SourceYear & SourceName & Author(s) \\ 
+  \hline
+1958 & J. Am. Stat. Assoc. & Kaplan E.R., Meier P. \\ 
+1963 & Science & Jerne, N. K. and Nordin, A. A.  \\ 
+1972 & J R Stat Soc & Cox DR.  \\ 
+1976 & Anal. Biochem. & Bradford MM \\ 
+1977 & Br J Cancer & R. Peto, M.C. Pike, and P. Armitage  \\ 
+1977 & Proc. Natl. Acad. Sci. & Sanger, F., S. Nicklen, and A.R. Coulson.  \\ 
+1983 & J Immunol Methods & Mosmann T  \\ 
+1984 & Adv Enzyme Regul & T.C. Chou, and P. Talalay  \\ 
+1989 & Molecular Cloning: A Laboratory Manual & Sambrook, J., Fritsch, E. and Maniatis, T.  \\ 
+1994 & Acta Crystallogr D & Collaborative Computational Project 4 \\ 
+1994 & Acta Crystallogr. A & Navaza J.  \\ 
+1997 & Cell & Levine, A. J. \\ 
+1997 & Am. J. Pathol. & Perez-Atayde, A. R., Sallan, S. E., Tedrow, U., Connors, S., Allred, E., and Folkman, J.  \\ 
+1998 & CA: A Cancer Journal for Clinicians & SH Landis T Murray S Bolden PA Wingo \\ 
+\hline
+\end{tabular}}
+\vspace{2.5 mm}
+\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies.
+A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature.
+Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve literature cited by this foundational set (cited\_sid).
+Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field}
+\label{table4}
+\end{adjustwidth}
+\end{table}
+
+Thus, we also applied intersection analysis as above at a finer level of granularity by computing intersection counts for first generation citations (citing\_pmid) and second generation citations (cited\_sid).
+The results are displayed as Venn diagrams in Figures 1 and 2 respectively.
+Strikingly, no publications are common to all five networks at the first generation level although a single publication, the highly influential work of Kohler and Milstein\cite{bibKohler}, is cited in four out of five networks.
+All 14 publications cited in our set of five networks were in the second generation of citations and another 198 were found  across various the four-network combinations, roughly an order of magnitude greater than the case of cited references.
+We manually grouped the 14 publications using high level descriptive terms and noted statistical techniques (5 publications), molecular and cell biological methods (4), analytical and structural biochemistry techniques (3) and cancer biology (2).
+Of these last two, one is a review of the p53 gene [cite] and the second is a study of angiogenesis in children with acute lymphoblastic leukemia [cite].
+Thus, the majority of this small set of 14 publications concerns methods that are heavily cited in these therapeutic development networks.
+We are actively working on characterizing the entire dataset as well as intersecting subsets using methods that would scale to thousands of publications and these results will be shared in another publication [needs to be reworded].
+
+\begin{table}[!ht]
+%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\scalebox{0.9}{
+\begin{tabular}{|l+l|l|l|l|l|l|l|}
+\hline
+%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
+Therapeutic & citing\_pmid count & citing\_sid count & cited\_sid count  & cited\_pmid count  \\ \hline
+$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
+$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
+$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
+$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
+$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
+\end{tabular}
+}
+\vspace{2.5 mm}
+\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies.
+A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature.
+Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve cited publications (cited\_sid).
+Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field}
+\label{table2}
+%\end{adjustwidth}
+\end{table}
+
 \begin{figure}[!h]
-\caption{{\bf Bold the figure title.}
-Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\centering
+\includegraphics[scale=0.15]{citing_pmid.png}
+\caption{{\bf Publications Common To First Generation References in Networks}
+Intersections were calculated across all five networks for citing\_pmids (the first generation of references) as well as cited\_sids (the second generation of references) and displayed as a Venn diagram.
+No publications are common to all five networks.
+A single publication is cited in four of five networks.
+Abbreviations: alem (Alemtuzumab),imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
 \label{fig1}
@@
 
-% Results and Discussion can be combined.
-\section*{Results and Discussion}
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.15]{cited_sid.png}
+\caption{{\bf Publications Common To Second Generation References in Networks}
+Intersections were calculated across all five networks for cited\_sids (the first generation of references) as well as cited\_sids (the second generation of references) and displayed as a Venn diagram.
+14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
+\label{fig2}
+\end{figure}
+
 \subsection*{Network Features}
@@
 The largest intersection count in each combination group is shown in boldface.
-Therapeutic names are abbreviated as follows: Alemtuzumab as alem(A), Imatinib as imat(I), Nelarabine as nela(N), Ramucirumab as ramu(R), and Sunitinib as suni(S).
+Therapeutic names are abbreviated as follows: alem (Alemtuzumab), imat(Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni (Sunitinib).
 }
@@
 \end{table}
-
-No idea what to say...
 
@@
 
-\section*{Discussion}
-
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero~\cite{bib3}.
+%\section*{Discussion}
 
@@
 
+\begin{figure}[!h]
+\caption{{\bf Bold the figure title.}
+Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\includegraphics{citing_pmid.png}
+\label{fig2}
+\end{figure}
+
 % Either type in your references using
@@
 
-\bibitem{bib1}
+\bibitem{bibWilliams}
 Williams RS, Lotia S., Holloway AK, Pico AR.
@@
 
-\bibitem{bib2}
+\bibitem{bibLauer}
 Lauer MS.
@@
 
-\bibitem{bib3}
-Wang M., Zhao Y.., Zhang B.
-\newblock {{E}fficient Test and Visualization of Multi-Set Intersections.}
-\newblock Sci. Rep. 2015 Nov; doi:10.1038/srep16923
-
-\bibitem{bib4}
+\bibitem{bibChan}
 O'Shea JJ, Kanno, Y., Chan AC.
@@
 
-\bibitem{bib5}
+\bibitem{bibMaldame}
 Maldame, J.
@@
 
-\bibitem{bib6}
+\bibitem{bibFDA}
 Federal Drug Administration.
@@
 
-\bibitem{bib7}
+\bibitem{bibNIHExPORTER}
 National Institutes of Health.
@@
 
-\bibitem{bib8}
+\bibitem{bibGooglePatents}
 Google Corporation
@@
 \newblock https://patents.google.com/
+
+\bibitem{bibKohler}
+K\"ohler, G., Milstein, C.
+\newblock { {C}ontinuous cultures of fused cells secreting antibody of predefined specificity.}
+\newblock Nature. 1975 256: 495?497
 

### 2017-05-25 assembly/exp_proj_link.R
today's edits

@@ -1,0 +1,144 @@
+# Merge with projects and peer review data
+
+# load interim results files into a list
+rm(list=ls())
+# Load 9 csv files from Eric Livingston into a list
+
+setwd("~/NETELabs_CaseStudies/assembly/interim_results")
+# temp <- list.files(pattern="*.csv")
+# interim_results <- list()
+# for (i in 1:length(temp)) {
+#	interim_results[[i]] <- read.csv(temp[i],stringsAsFactors=FALSE,header=TRUE)
+#}
+# names(interim_results) <- temp
+# rm(i)
+# save(interim_results,file="interim_results.RData")
+
+# Read in pub_out (pmid-SID) and pub_cites (PubSID to SID) 
+pub_out <- read.csv("pub_out.csv",colClasses=rep("character",6))
+pub_cites <- read.csv("pub_cites.csv",colClasses=rep("character",9))
+# free up memory
+# rm(interim_results)
+# print str stats
+str(pub_out)
+str(pub_cites)
+
+# Read in exporter link and projects data
+exp_link <- read.csv("~//NETELabs_CaseStudies/assembly/final_results/exporter_links.csv",colClasses=(rep("character",2)))
+exp_projects <- read.csv("~//NETELabs_CaseStudies/assembly/final_results/exporter_projects.csv",colClasses=(rep("character",9)))
+
+
+# load Stage I files that Eric used to generate pub_out and pub_cites
+alem <- read.csv("~/NETELabs_CaseStudies/assembly/alemtuzumab_assembly/alem_eric_stage1.csv",
+colClasses=c(rep("character",9)))
+imat <- read.csv("~/NETELabs_CaseStudies/assembly/imatinib_assembly/imat_eric_stage1.csv",
+colClasses=c(rep("character",9)))
+nela <- read.csv("~/NETELabs_CaseStudies/assembly/nelarabine_assembly/nela_eric_stage1.csv",
+colClasses=c(rep("character",9)))
+ramu <- read.csv("~/NETELabs_CaseStudies/assembly/ramucirumab_assembly/ramu_eric_stage1.csv",
+colClasses=c(rep("character",9)))
[…]

### 2017-05-30 Paper/plos-latex-template/Supplemental.tex
new edits

--- 2017-05-17 Paper/plos-latex-template/plos_latex_template.tex
@@
 %
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file 
-% and leave only the final text of your manuscript. 
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that 
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
-%
-% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column. 
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Please contact latex@plos.org with any questions.
-%
 % % % % % % % % % % % % % % % % % % % % % % % %
 
+% Created to hold supplementary information
+
 \documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+\usepackage[top=0.85in,left=2in,footskip=0.75in]{geometry}
 
@@
 % Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Research Synergy and Drug Development: Bright Stars in Neighboring Constellations} % Please use "title case" (capitalize all terms in the title except conjunctions, prepositions, and articles).
-}
-\newline
 % Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Samet Keserci\textsuperscript{1},
-%Samet Keserci\textsuperscript{1,2\Yinyang},
-Eric Livingston\textsuperscript{2},
-Lingtian Wan\textsuperscript{1,\textcurrency},
-Alexander R. Pico\textsuperscript{3},
-%Name5 Surname\textsuperscript{2\ddag},
-%Name6 Surname\textsuperscript{2\ddag},
-George Chacko\textsuperscript{1*},
-%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
-\\
-\bigskip
-\textbf{1} Netelabs, NET ESolutions Corporation, McLean, VA, USA
-\\
-\textbf{2} Elsevier Research Intelligence, Elsevier Inc., Bethesda, MD, USA
-\\
-\textbf{3} Gladstone Institutes, University of California San Francisco, San Francisco, CA, USA
-\\
-\bigskip
-
 % Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
@@
 % Current address notes
-\textcurrency Current Address: Facebook Corporation, Menlo Park, CA, USA % change symbol to "\textcurrency a" if more than one current address note
+% change symbol to "\textcurrency a" if more than one current address note
 % \textcurrency b Insert second current address 
@@
 % Use the asterisk to denote corresponding authorship and provide email address in note below.
-*Correspondence: george@nete.com
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
+\section*{Supporting Information for Keserci et al.}
 
-Scientific advances such as development of a new drug or biological are collaborative and involve the contributions of many scientists.
-Data mining and network analysis of public and commercial data sources can be used to describe the set of collaborative activities or `cure networks' that result in new therapeutics.
-To explore the relationship across cure networks- the extent to which nodes are common across networks, we have conducted case studies of five anti-cancer therapeutics.
-We have mined data drawn from public and commercial sources, constructed linkages based on unique identifiers, and modeled the data as networks.
-We have enriched the content of these networks by annotating them with information on awards that supported the research in these networks as well as peer review that preceded these awards.
-This approach can be extended beyond drug development to study any major scientific advance.
-Such studies support portfolio analysis and a public understanding of the benefits of research, this methodology can be extended beyond cures to scientific advances in general.
-[In fact we're talking about the digital transformation of science history scholarship].[These studies help us understand that which came before and leave it in a form that others can use].[cite Jean-Michel Maldame's work]
+% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
+\paragraph*{Notation and Calculations} 
+\textbf{}
+\begin {itemize}
+\item $d_i =$  therapeutic, e.g., alemtuzumab(alem) or imatinib(imat)
+\item $N_i =$ the network of a therapeutic $d_i$;
+\item $\mathcal{N}$ = union of all networks $N_i$
+\item $\mathcal{G}$ the global network - the set of all authors and their publications in the Scopus database
+\item $\mathcal{M}$ the set of all subnetworks - ie $\{N_1,N_2,N_3,N_4,N_5\}$
+\item $c_n(\mathfrak{p})$ citation of a publication $\mathfrak{p}$ in a network $n$
+\item $\mathcal{C}_\mathfrak{p}^n$ =the set of publications which cites $\mathfrak{p}$ in a network $n$
+\item $wc_n(\mathfrak{p})$  weighted citation of a publication $\mathfrak{p}$ in a network $n$
+\item $\mathcal{A}_\mathfrak{a}^n$ the set of publications for an author $\mathfrak{a}$ in a network $n$
+\item $pir_n(\mathfrak{a})$ the PIR  score of an author in a Network $n$ in $\mathcal{M}$
+\item $npir(\mathfrak{a})$ the PIR score of an author  $\mathfrak{a}$ in the Network  $\mathcal{N}$ 
+\item $ir(\mathfrak{a})$ partitioning of a research metric for an author $\mathfrak{a}$ 
+\item $ic_{d_i}(\mathfrak{a})$ = total \# in-degree count for an author $\mathfrak{a}$  for drug $d_i$. (ie. = $\|\mathcal{A}_\mathfrak{a}^{d_i}\|$)
+\item $ic_n(\mathfrak{a})$ = total \# in-degree count for an author $\mathfrak{a}$  in  $\mathcal{N}$ (i.e = $\|\mathcal{A}_\mathfrak{a}^{N}\|$)
+\item $ nrbr_{d_i}(\mathfrak{a}) $ modified RBR for an author in a drug network, $d_i$, that is normalized to the author's publications in all five networks $\mathcal{N}$ 
+\item $ grbr_{d_i}(\mathfrak{a}) $ modified RBR for any author in all five drug networks that is normalized to the global network $\mathcal{G}$ 
+\end{itemize}
+\vspace{2 mm}
 
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-%\section*{Author Summary}
-%Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+\paragraph{Propagated Indegree Rank (PIR)} We define the global network $\mathcal{N}$ as the union of the each individual sub-network of a therapeutic $d_i$. In other words 
+$$ \mathcal{N} = \cup_{i =1}^{5} \mathcal{N}_i $$
+Let $c_n(\mathfrak{p})$ be the citation score of the the paper $\mathfrak{p}$ in a network $n$, and $\mathcal{C}_\mathfrak{p}^n$ be the set of publication which cites $\mathfrak{p}$.
+Then we define the weighted citation of a paper $\mathfrak{p}$ as $$wc_n(\mathfrak{p}) = c_n(\mathfrak{p}) + \sum_{g\in \mathcal{C}_\mathfrak{p}^n}  c_n(g) $$
+Let $\mathcal{A}_a^n$ be the set of publications for an author $\mathfrak{a}$ in a Network $n$.
+Then the PIR score  for an author $\mathfrak{a}$  in network $n$ is defined as $$ pir_n(\mathfrak{a}) =  \sum_{p\in \mathcal{A}_a^n}  wc_n(\mathfrak{p}) $$
 
-\linenumbers
+More simply, the PIR score for an author  $\mathfrak{a}$ in a Network $n$ is  $$ pir_n(\mathfrak{a}) =  \sum_{p\in \mathcal{A}_a^n } \big[c_n(p) + \sum_{g\in \mathcal{C}_\mathfrak{p}^n}  c_n(g)\big] $$
 
-% Use "Eq" instead of "Equation" for equation citations.
-\section*{Introduction}
+Next we define the nPIR score $npir(\mathfrak{a})$, which is $pir$ score based on the  total network $\mathcal{N}$.
+For convenience, instead of denoting it $pir_N$, we use $npir$   Furthermore  we define the isolation of  research  metric $ir(\mathfrak{a}):\mathcal{R}\rightarrow [1,\infty]$  of an author $\mathfrak{a}$ as
+$$ir(\mathfrak{a})= \dfrac{ npir({\mathfrak{a}})} {\sum_{1}^{5} pir_{d_i}(\mathfrak{a})} $$
+where $\mathcal{R}$ is the set of all authors in $\mathcal{N}$  and  $pir_{d_i}(\mathfrak{a})$ is the PIR score of the author $\mathfrak{a}$ restricted to only drug network $\mathcal{D}_i$ .
+If $ir(\mathfrak{a})$ approaches 1, the author's $\mathfrak{a}$ contribution to each drug is partitioned.
+The greater the $ir$, the closer  the interaction of the author's papers between the networks.
 
-Data mining of public data sources coupled with network analysis allows the assembly and quantitative description of research discoveries that were influential in the development of a breakthrough therapeutic or `cure' \cite {bib1}.
-The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents progress from basic research to a cure is termed a `cure network'.
-Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will uncover previous influential discovery (\textit{ibid}).
+\paragraph{Ratio of Basic Rankings (RBR)}
+\begin{itemize}
+\item nRBR or network RBR is the ratio of an authors' count of publications in a network to the total number of the author's publications in the global Network. 
+Lets define in-degree count $ic_{d_i}(\mathfrak{a})$ of an author $\mathfrak{a}$ as the total number of the publication which is in the network $\mathcal{N}_i$ of the drug $d_i$, similarly lets $ic_{n}$ be the number of the paper that author $\mathfrak{a}$ published in the total Network(5-drug's network) $\mathcal{N}$.
+Then we define, nRBR of an author $\mathfrak{a}$  for a drug $d_i$ as follow.
+$$ nrbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{N}(\mathfrak{a})}$$
+\item gRBR or global RBR is the ratio of an author's count of publications in a network to the author's total publication count.
+$\mathcal{G}$.
+Thus, $grbr$ score of an author  $\mathfrak{a}$  for the drug $d_i$ is defined as
+$$grbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{G}(\mathfrak{a})}$$
+where $ic_{G}$ is the total number of publication that an author $\mathfrak{a}$ currently has.
+\end{itemize}
+\clearpage
 
-Williams and colleagues have elegantly demonstrated the feasibility of this approach using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}).
-These authors observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-related research over a period greater than 100 years.
-Such studies provide evidence for the  broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases, support strategic communications to oversight bodies, and communication of the societal value of research \cite {bib2}.
-
-Extending the methodology to study additional cures as well as other significant research advances is a logical next step.
-Ascertaining the nature of the interactions, if any, between networks, is also of considerable interest since it would support an understanding of common features of science networks as well as research events that have been influential across multiple networks.
-
-To address these questions, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer.
-We have extended the original approach to (i) include a data from a commercially available bibliographic database with disambiguated author identifiers (ii) modified the original data mining methods and network metrics (iii) added new node types to include grants and peer review data (iv) refactored the network analysis code of Williams et al.
-for better performance.
-(v) mapped publications and authors across all five networks.
-We present the results of these case studies as a step towards mapping the universe of FDA-approved drugs and biologicals.
-
-% Place tables after the first paragraph in which they are cited.
 \begin{table}[!ht]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
+\vspace{2.5 mm}
+\scalebox{0.8}{
+\begin{tabular}{|l| l| l| l| l| l| l| l|}
+\hline
+alem(A) & imat(I) & nela(N) & ramu(R) & suni(S) & combination  & intersection\_count &no\_of\_drugs\\ 
+ \hline
+%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
+X & X & X & X & X & AINRS &  \textbf{14} & 5 \\ 
+\hline
+X & X &  & X & X & AIRS & \textbf{107} & 4 \\ 
+\hline
+X & X & X & X &  & AINR &  28 & 4 \\ 
+\hline
+X & X & X &  & X & AINS &  25 & 4 \\ 
+\hline
+& X & X & X & X & INRS &  22 & 4 \\ 
+\hline
+X &  & X & X & X & ANRS &  16 & 4 \\ 
+\hline 
+& X &  & X & X & IRS & \textbf{1762} & 3 \\ 
+\hline
+X & X &  & X &  & AIR & 231 & 3 \\ 
+\hline
+X & X &  &  & X & AIS & 211 & 3 \\ 
+\hline
+X &  &  & X & X & ARS & 156 & 3 \\ 
+\hline
+X & X & X &  &  & AIN &  81 & 3 \\ 
+\hline
+X &  & X & X &  & ANR &  56 & 3 \\ 
+\hline 
+& X & X &  & X & INS &  49 & 3 \\ 
+\hline
+& X & X & X &  & INR &  44 & 3 \\ 
+\hline
+ &  & X & X & X & NRS &  40 & 3 \\ 
+\hline
+X &  & X &  & X & ANS &  32 & 3 \\ 
+\hline 
+&  &  & X & X & RS & \textbf{7442} & 2 \\ 
+\hline
+& X &  &  & X & IS & 5415 & 2 \\ 
+\hline
+& X &  & X &  & IR & 2507 & 2 \\ 
+\hline
+X & X &  &  &  & AI & 1240 & 2 \\ 
+\hline
+X &  &  & X &  & AR & 448 & 2 \\ 
+\hline
+X &  &  &  & X & AS & 359 & 2 \\ 
+\hline
+X &  & X &  &  & AN & 334 & 2 \\ 
+\hline 
+& X & X &  &  & IN & 232 & 2 \\ 
+\hline
+&  & X & X &  & NR & 115 & 2 \\ 
+\hline 
+ &  & X &  & X & NS & 111 & 2 \\ 
+\hline
+&  &  & X &  & R & \textbf{49006} & 1 \\ 
+\hline 
+&  &  &  & X & S & 34257 & 1 \\ 
+\hline 
+& X &  &  &  & I & 27706 & 1 \\ 
+\hline
+X &  &  &  &  & A & 8978 & 1 \\ 
+\hline
+&  & X &  &  & N & 2498 & 1 \\ 
+\hline
+\end{tabular}}
+\vspace{2.5 mm}
 \caption{
-{\bf Case Studies of Five Anti-Cancer Agents}}
-\vspace{1.5 mm}
-\begin{tabular}{|l+l|l|l|l|l|l|l|}
-\hline
-
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
-Therapeutic & FDA Approval Date & Unique Identifier & US Patent & Publication Date  \\ \hline
-$Alemtuzumab$ & May 2001 & BLA: 103948 & US5846534 & Dec 1998\\ \hline
-$Imatinib$ & May 2001 & NDA: 021335 & US5521184 &  May 1996 \\ \hline
-$Nelarabine$ & Oct 2005 & NDA: 021877 & US5424295 & Jun 1995  \\ \hline
-$Ramucirumab$ & Apr 2014 & BLA: 125477 & US7498414 & Mar 2009  \\ \hline
-$Sunitinib$ & Jan 2006  & NDA: 021938  & US6573293 & Jun 2003 \\ \hline
-\end{tabular}
-\vspace{1.5 mm}
-\begin{flushleft} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies.
-The active ingredient for each of these five therapeutics is listed in column 1.
-While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic.
-The publication date for each patent is listed in the last column.
-\end{flushleft}
+{\bf Intersecting Publications Across Networks} Intersections were calculated for the set of publications associated with each network.
+Both citing and cited references were included in each set and  Scopus identifiers were used to to minimize information loss (Table 2).
+Intersection counts are shown for all possible combinations of the five therapeutics.
+The largest intersection count in each combination group is shown in boldface.
+Therapeutic names are abbreviated as follows: alem (Alemtuzumab), imat(Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni (Sunitinib).
+}
 \label{table1}
-\end{adjustwidth}
 \end{table}
 
-\section*{Materials and Methods}
-
-A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans between 2001 and 2014, were chosen for this study (Table 1).
-Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab are humanized antibodies that target cell surface receptors.
-
-For each of these therapeutics, a set of relevant citations was constructed based on the assumptions articulated by Williams et al.
-but with specific modifications detailed below.
-An allowance of 2 months was also made for `publication lag' when assembling referenced material.
-For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included.
-A first generation of citations was created as a list of PubMed IDs (pmids) harvested from seven different data sources (below).
-\begin {itemize}
-\item Clinical trials.
-The national clinical trials database (clinicaltrials.gov) was searched for clinical trials of the five therapeutics that completed on or the data of FDA approval.
-Both cited references and publications from these clinical trials were collected if they were published within the approval date plus two months period.
-PubMed was also searched with the unique identifier (NCT number) of any clinical trials that were identified to capture publications associated with the clinical trials that were not displayed in clinical trials.gov.
-To capture clinical trials publications that are not available in clinicaltrials.gov, PubMed was searched using the therapeutic name as keyword, publication type as "clinical trial", and an appropriate date restriction as in searches of clinicaltrials.gov.
-For example, the search term ((("alemtuzumab"[Supplementary Concept] OR "alemtuzumab"[All Fields]) OR ("alemtuzumab"[Supplementary Concept] OR "alemtuzumab"[All Fields] OR "campath"[All Fields])) AND ("1900/0101"[PDAT] : "2001/07/31"[PDAT])) AND "clinical trial"[Publication Type] was used to identify publications typed as clinical trials for Alemtuzumab that were published on or before July 31, 2001.
-
-\item Regulatory documents.
-drugs@fda (https://www.accessdata.fda.gov/scripts/cder/daf/) was searched for each of the five therapeutics and cited references in the medical review of the approval process were manually extracted and matched to pmids.
-
-\item FDA Approval Summaries.
-These articles published in journals by FDA staff (approval summaries were available for all five therapeutics), contain cited references that were extracted using Scopus.
-approval summaries were available for all five therapeutics.
-If the published date of a citation exceeded the approval date plus two months, the publication was not included.
-
-\item Patents.
-For each therapeutic a single patent was identified that best represented the most relevant invention to the therapeutic at hand.
-Identification of a patent was performed using multiple web sources: PubMed, Google Patents, EspaceNet, and drugbank.ca.
-The US patent number was used to identify the patent and the non-patent citation list from Google patent was manually processed by searching PubMed for appropriate pmids.
-While we developed a citation matching tool for non-patent literature, the precision and recall rates from manual searches was far higher and were used to generate the data in this study.
-
-\item Reviews: We treated review articles published after FDA approval  as independent documents describing the development of a therapeutic.
-Accordingly, PubMed was searched for review articles of a therapeutic that were published between the date of FDA approval and one year following the date of approval.
-Cited references in these reviews were also extracted as above.
-
-\item Literature searches were also performed using PubMed with a date range of 1900/01/01 to two months post-FDA approval.
-For example, the search term ((alemtuzumab) OR campath) AND ("1900/01/01"[Date - Publication] : "2001/07/31"[Date - Publication]) was used to retrieve articles of interest relevant to alemtuzumab.
-\end{itemize}
-
-Pmids from the seven different sources above (citing\_pmid) were combined, deduplicated, and matched to Scopus IDs (citing\_eid) using Scopus APIs.
-These eids were used to extract cited references (cited\_eid), which were then mapped back to pmids (cited\_pmid).
-The data are summarized in Table 2.
-Using the Scopus database, this list was mapped to Scopus eids and a second generation of cited references was extracted.
-These were mapped to pmids First and second generation pmids were both mapped to NIH grants and peer review data using information made publicly available by NIH.
-The resultant data were modeled as hierarchical networks using a simple dictionary of N node types to unambiguously identify nodes and interactions between them.
-The networks were analyzed using metrics based on network topology.
-
-\begin{table}[!ht]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\caption{
-{\bf Mapping Publications}}
-\vspace{1.5 mm}
-\begin{tabular}{|l+l|l|l|l|l|l|l|}
-\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
-Therapeutic & citing\_pmid count & citing\_eid count & cited\_eid count  & cited\_pmid count  \\ \hline
-$Alemtuzumab$ & 599 & 587 & 8840 & 7071\\ \hline
-$Imatinib$ & 1380 & 1373 & 27326 &  23340 \\ \hline
-$Nelarabine$ & 104 & 104 & 2476 & 1990  \\ \hline
-$Ramucirumab$ & 1820 & 1804 & 48587 & 40973  \\ \hline
-$Sunitinib$ & 1512  & 1509  & 33895 & 28661 \\ \hline
-\end{tabular}
-\vspace{1.5 mm}
-\begin{flushleft} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies.
-The active ingredient for each of these five therapeutics is listed in column 1.
-While multiple patents are often associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic.
-The publication date for each patent is listed in the last column.
-\end{flushleft}
-\label{table1}
-\end{adjustwidth}
-\end{table}
-
-Available awards (projects) and link tables publications up to 2016 were downloaded from NIH ExPORTER and used to link publications to NIH awards and study sections where grant applications were reviewed for scientific merit before an award was made.
-The assembled data were modeled as a network for each therapeutic and stored as node lists and edge lists.
-exporter
-
-For these data, we calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams \cite {bib1}  with some modifications to the RBR as follows.
-The original RBR was defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author.
-The background dataset was constructed by keyword searches of PubMed.
-However, a potential weakness of the keyword based approach is that keywords do not effectively capture the field or the total ouput of an author even if multiple background samples are taken.
-We created two new variants, nRBR and dRBR.
-nRBR uses all publications in our set of five therapeutics as background.
-dRBR takes advantage of the Scopus author\_id to capture the total output of an author and use it as background.
-
-Citation data for all five networks were combined and a globalPIR score was calculated. The globalPIR score was normalized to the sum of PIR scores within each network.
-
-\subsection*{Etiam eget sapien nibh.}
-
-% For figure citations, please use "Fig" instead of "Figure".
-Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
-
-% Place figure captions after the first paragraph in which they are cited.
-\begin{figure}[!h]
-\caption{{\bf Bold the figure title.}
-Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
-\label{fig1}
-\end{figure}
-
-% Results and Discussion can be combined.
-\section*{Results and Discussion}
-
-No idea what to say...
-
-%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
-\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}
-\subsubsection*{3rd Level Heading.}
-
-Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
-
-\begin{enumerate}
-	\item{react}
-	\item{diffuse free particles}
-	\item{increment time by dt and go to 1}
-\end{enumerate}
-
-\subsection*{Sed ac quam id nisi malesuada congue.}
-
-Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
-
-\begin{itemize}
-	\item First bulleted item.
-	\item Second bulleted item.
-	\item Third bulleted item.
-\end{itemize}
-
-\section*{Discussion}
-
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero~\cite{bib3}.
-
-\section*{Conclusion}
-
-CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
-Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna.
-Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-Nam condimentum sem eget mollis euismod.
-Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex.
-Nunc est dui, sodales sed mauris nec, auctor sagittis leo.
-Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor.
-For more information, see \nameref{S1_Appendix}.
-
-\section*{Supporting Information}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{S1_Fig}
-{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
-
-\paragraph*{S2 Fig.}
-\label{S2_Fig}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 File.}
-\label{S1_File}
-{\bf Lorem Ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Video.}
-\label{S1_Video}
-{\bf Lorem Ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Appendix.}
-\label{S1_Appendix}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Table.}
-\label{S1_Table}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\section*{Acknowledgments}
-Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Nam id pretium nisi.
-Sed ac quam id nisi malesuada congue.
-Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
-
-\begin{eqnarray}
-\label{eq:schemeP} 
-	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
-\end{eqnarray}
-
-\nolinenumbers
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here.
-% 
-\begin{thebibliography}{10}
-
-\bibitem{bib1}
-Williams RS, Lotia S., Holloway AK, Pico AR.
-\newblock {{F}rom Scientific Discovery to Cures: Bright Stars within a Galaxy.}
-\newblock Cell. 2015 Sep; 163:21--23
-
-\bibitem{bib2}
-Lauer MS.
-\newblock {{P}CSK9 Inhibitors: Lots of Work Done, Lots More to Do.}
-\newblock Ann Intern Med. 2016 Mar; 164(9):624-625.
-
-\bibitem{bib3}
-Wang M., Zhao Y.., Zhang B.
-\newblock {{E}fficient Test and Visualization of Multi-Set Intersections.}
-\newblock Sci. Rep. 2015 Nov; doi:10.1038/srep16923
-
-\bibitem{bib4}
-O'Shea JJ, Kanno, Y., Chan AC.
-\newblock {{I}n Search of Magic Bullets: The Golden Age of Immunotherapeutics}
-\newblock Cell. 2014 Mar; 157:227-240
-
-\bibitem{bib5}
-Maldame, J.
-\newblock {{T}he Importance Of The History Of Science In Intellectual Formation}
-\newblock Scripta Varia 2002 104:237-248
-
-\bibitem{bibn}
-Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
-\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
-infection through a transposon insertion followed by a {D}uplication}.
-\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
-
-\end{thebibliography}
-
 \end{document}

### 2017-05-30 Paper/plos-latex-template/plos_latex_template.tex
new edits

@@
 %
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file 
-% and leave only the final text of your manuscript. 
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that 
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-%  Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-%   DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-%   For figure citations, please use "Fig" instead of "Figure".
-%   See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
-%
-% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column. 
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Please contact latex@plos.org with any questions.
-%
 % % % % % % % % % % % % % % % % % % % % % % % %
 
+% Created to hold supplementary information
+
 \documentclass[10pt,letterpaper]{article}
+
 \usepackage[top=0.85in,left=2in,footskip=0.75in]{geometry}
@@
 Such advances are invariably collaborative, involving the contributions of many scientists in a `cure network' where prior theory and experiment is built upon.
-Data mining of public and commercial data sources coupled with network analysis is a scalable digital methodology for assembling and analyzing the history of scientific advances.
-This methodology is extensible beyond cure networks and its use supports (i) efficiency in  exploring  the scientific history of a research advance (ii) improved documenting and understanding of collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
-Building upon prior techniques for single cure networks and linking the work of approximately 200,000 authors in 100,000 scientific publications, we have conducted a case study of five anti-cancer therapeutics for the purpose of exploring the relationship across networks.
+To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble component events in the history of a cure and analyze them.
+The methodology is extensible beyond cure networks and its use supports (i) efficiency in  exploring  the scientific history of a research advance (ii) improved documenting and understanding of collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
+Building upon techniques for single networks and linking the work of approximately 250,000 authors in 100,000 scientific publications, we have conducted a case study of five anti-cancer therapeutics for the purpose of exploring the relationship across networks.
 We have enriched the content of these five networks by annotating them with information on research awards as well as peer review that preceded these awards.
@@
 
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-%\section*{Author Summary}
-%Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+\linenumbers
 
-\linenumbers
-% Use "Eq" instead of "Equation" for equation citations.
 \section*{Introduction}
 
-Data mining of public data sources coupled with network analysis allows the assembly and quantitative description of research discoveries that were influential in the development of a breakthrough therapeutic or `cure'.
-The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents progress from basic research to a cure is termed a `cure network' \cite {bib1}.
+Data mining of public data sources coupled with network analysis enables the assembly and quantitative description of research discoveries that were influential in the development of a breakthrough therapeutic or `cure'.
+The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents the progress of concepts from basic research to a cure is termed a `cure network' \cite {bibWilliams}.
 Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will uncover previous influential discovery (\textit{ibid}).
-Williams and colleagues have elegantly demonstrated the feasibility of this approach using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}).
+Further, when coupled with the knowledge that accrues from the use of the drug, the knowledge of a drug development network enables a recursive learning of the pathogenesis of the disease it is being used to treat\cite{bibChan}.
+
+Beyond using a digital methodology to assemble a set of facts about a major scientific advance, however, these studies support a contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time\cite{bibMaldame}.
+Williams and colleagues have elegantly demonstrated the feasibility and value of data mining and network analysis using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}).
 These authors observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-related research over a period greater than 100 years.
+Such studies (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases (ii) support strategic communications to oversight bodies, and (iii) help communicate the societal value of research\cite {bibMaldame,bibLauer}.
 
-Such studies provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases, support strategic communications to oversight bodies, and communication of the societal value of research\cite {bib2,bib3}.
-Extending this digital methodology to study additional cures as well as significant research advances in general is a logical next step.
+Extending this methodology to study additional cures and significant research advances in general is a logical next step.
 Ascertaining the nature of the interactions, if any, between networks, is also of considerable interest since it would support an understanding of collaboration across networks as well as common features of science networks.
+Lastly, scaling from case studies to mapping the entire domain of drug development may be beneficial in understanding and optimizing activities in the pharmaceutical industry.
 
-To address these questions, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer.
-We have extended the original approach to (i) include a data from a commercially available bibliographic database with disambiguated author identifiers (ii) modified the original data mining methods and network metrics (iii) added new node types to include grants and peer review data (iv) refactored the network analysis code of Williams et al.
+To address these questions, we have enhanced the original approach to (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extended single network analysis to map publications and authors across multiple networks (v) refactored the network analysis code of Williams et al.
 for better performance.
-(v) mapped publications and authors across all five networks.
+To evaluate these extensions, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer.
+We present the results of this case study as a step towards mapping the universe of FDA-approved drugs and biologicals and a dataset that can be interrogated by other researchers.
 
-We present the results of these case studies as a step towards mapping the universe of FDA-approved drugs and biologicals.
-Beyond drug discovery and cures, however, this simple digital methodology can be used to support efficient explorations of science history, gain an understanding of collaboration across domains, enrich portfolio analysis, planning and optimization, enable communications of the societal value of research, and help make the scientific environment more citizen-accessible.
-
-\section*{Materials and Methods} 
-% Place tables after the first paragraph in which they are cited.
-A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration was selected for this study (Table 1).
+\section*{Materials and Methods}  A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration was selected for this study (Table 1).
 Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab are humanized antibodies that target cell surface receptors.
- For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.\cite{bib1} but with specific modifications detailed below.
-An allowance of 2 months was made for `publication lag' when assembling referenced material.
+For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.\cite{bibWilliams} but with specific modifications detailed below.
+An allowance of 2 months was also made for `publication lag' when assembling referenced material.
 For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included.
 For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (below).
+
 \begin{table}[!ht]
@@
 
-Citing and cited pmids were both mapped to NIH grants and peer review panels using information made publicly available by NIH through NIH ExPORTER.
-Since Special Emphasis Panels vary in scientific interests from year to year, we restricted our mapping to chartered study sections, which have defined scientific interests and relatively stable reviewer membership.
+\begin{table}[!ht]
+%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\scalebox{0.9}{
+\begin{tabular}{|l+l|l|l|l|l|l|l|}
+\hline
+%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
+Therapeutic & citing\_pmid count & citing\_sid count & cited\_sid count  & cited\_pmid count  \\ \hline
+$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
+$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
+$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
+$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
+$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
+\end{tabular}
+}
+\vspace{2.5 mm}
+\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies.
+A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature (Materials and Methods).
+Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve cited publications (cited\_sid).
+Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field}
+\label{table2}
+%\end{adjustwidth}
+\end{table}
+
+Both citing and cited pmids were mapped to NIH grants and peer review panels (study sections) using information made publicly available by NIH through NIH ExPORTER.
+The Center for Scientific Review at NIH organizes the review of the majority of grant applications submitted to the NIH and has over 170 chartered study sections with defined scientific interests and relatively stable reviewer membership.
+Thus, we enriched our network data by identifying those study sections associated with the awards that supported publications in our networks.
+Since Special Emphasis Panels vary in scientific interests from year to year, we restricted our mapping to chartered study sections at the Center for Scientific Review.
+
 The resultant data were modeled as hierarchical networks and analyzed using metrics based on network topology.
-We calculated the propagated in-degree rank (PIR) metric of Williams \cite {bib1}.
+We calculated the propagated in-degree rank (PIR) metric of Williams \cite {bibWilliams}.
 PIR represents the sum of weighted citation scores for all articles in a network that can be attributed to an author.
 In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a globalPIR score, which was normalized to the sum of PIR scores within each network.
-
-We also calculated the RBR metric of Williams et al.
+Secondly, we calculated the RBR metric of Williams et al.
 (\textit{ibid}) with some modifications.
@@
 nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total output of an author and use it as background.
-Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively.\\
+Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively.
+The details of how these metrics were calculated are provided in supplementary material \nameref{S1_File}.\\
 \vspace{2.5 mm}
 
-\textbf{Notation and Calculations}
-\begin {itemize}
-\item $d_i =$  therapeutic, e.g., alemtuzumab(alem) or imatinib(imat)
-\item $N_i =$ the network of a therapeutic $d_i$;
-\item $\mathcal{N}$ = union of all networks $N_i$
-\item $\mathcal{G}$ the global network - the set of all authors and publications in $\mathcal{N}$ 
-\item $\mathcal{M}$ the set of all subnetworks - ie $\{N_1,N_2,N_3,N_4,N_5\}$
-\item $c_n(\mathfrak{p})$ citation of a publication $\mathfrak{p}$ in a network $n$
-\item $\mathcal{C}_\mathfrak{p}^n$ =the set of publications which cites $\mathfrak{p}$ in a network $n$
-\item $wc_n(\mathfrak{p})$  weighted citation of a publication $\mathfrak{p}$ in a network $n$
-\item $\mathcal{A}_\mathfrak{a}^n$ the set of publications for an author $\mathfrak{a}$ in a network $n$
-\item $pir_n(\mathfrak{a})$ the PIR  score of an author in a Network $n$ in $\mathcal{M}$
-\item $npir(\mathfrak{a})$ the PIR score of an author  $\mathfrak{a}$ in the Network  $\mathcal{N}$ 
-\item $ir(\mathfrak{a})$ partitioning of a research metric for an author $\mathfrak{a}$ 
-\item $ic_{d_i}(\mathfrak{a})$ = total \# in-degree count for an author $\mathfrak{a}$  for drug $d_i$. (ie. = $\|\mathcal{A}_\mathfrak{a}^{d_i}\|$)
-\item $ic_n(\mathfrak{a})$ = total \# in-degree count for an author $\mathfrak{a}$  in  $\mathcal{N}$ (i.e = $\|\mathcal{A}_\mathfrak{a}^{N}\|$)
-\item $ nrbr_{d_i}(\mathfrak{a}) $ modified RBR score normalized to its network $\mathcal{N}$ for a drug $d_i$
-\item $ grbr_{d_i}(\mathfrak{a}) $ modified RBR score normalized to the global network $\mathcal{G}$  for a drug $d_i$
-\end{itemize}
-
-\textbf{PIR Score}: We define the global network $\mathcal{N}$ as the union of the each individual sub-network of a therapeutic $d_i$. In other words 
-$$ \mathcal{N} = \cup_{i =1}^{5} \mathcal{N}_i $$
-Let $c_n(\mathfrak{p})$ be the citation score of the the paper $\mathfrak{p}$ in a network $n$, and $\mathcal{C}_\mathfrak{p}^n$ be the set of publication which cites $\mathfrak{p}$.
-Then we define the weighted citation of a paper $\mathfrak{p}$ as $$wc_n(\mathfrak{p}) = c_n(\mathfrak{p}) + \sum_{g\in \mathcal{C}_\mathfrak{p}^n}  c_n(g) $$
-Let $\mathcal{A}_a^n$ be the set of publications for an author $\mathfrak{a}$ in a Network $n$.
-Then the PIR score  for an author $\mathfrak{a}$  in network $n$ is defined as $$ pir_n(\mathfrak{a}) =  \sum_{p\in \mathcal{A}_a^n}  wc_n(\mathfrak{p}) $$
-
-More simply, the PIR score for an author  $\mathfrak{a}$ in a Network $n$ is  $$ pir_n(\mathfrak{a}) =  \sum_{p\in \mathcal{A}_a^n } \big[c_n(p) + \sum_{g\in \mathcal{C}_\mathfrak{p}^n}  c_n(g)\big] $$
-
-Next we define the nPIR score $npir(\mathfrak{a})$, which is $pir$ score based on the  total network $\mathcal{N}$.
-For convenience, instead of denoting it $pir_N$, we use $npir$   Furthermore  we define the isolation of  research  metric $ir(\mathfrak{a}):\mathcal{R}\rightarrow [1,\infty]$  of an author $\mathfrak{a}$ as
-$$ir(\mathfrak{a})= \dfrac{ npir({\mathfrak{a}})} {\sum_{1}^{5} pir_{d_i}(\mathfrak{a})} $$
-where $\mathcal{R}$ is the set of all authors in $\mathcal{N}$  and  $pir_{d_i}(\mathfrak{a})$ is the PIR score of the author $\mathfrak{a}$ restricted to only drug network $\mathcal{D}_i$ .
-If $ir(\mathfrak{a})$ approaches 1, the author's $\mathfrak{a}$ contribution to each drug is partitioned.
-The greater the $ir$, the closer  the interaction of the author's papers between the networks.
-
-\textbf{RBR Score}:
-\begin{itemize}
-\item nRBR or network RBR is the ratio of an authors' count of publications in a network to the total number of the publications in the global Network. 
-Lets define in-degree count $ic_{d_i}(\mathfrak{a})$ of an author $\mathfrak{a}$ as the total number of the publication which is in the network $\mathcal{N}_i$ of the drug $d_i$, similarly lets $ic_{n}$ be the number of the paper that author $\mathfrak{a}$ published in the total Network(5-drug's network) $\mathcal{N}$.
-Then we define, nRBR of an author $\mathfrak{a}$  for a drug $d_i$ as follow.
-$$ nrbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{N}(\mathfrak{a})}$$
-\item gRBR or global RBR is the ratio of an author's count of publications in a network to the author's total publication count.
-$\mathcal{G}$.
-Thus, $grbr$ score of an author  $\mathfrak{a}$  for the drug $d_i$ is defined as
-$$grbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{G}(\mathfrak{a})}$$
-where $ic_{G}$ is the total number of publication that an author $\mathfrak{a}$ currently has.
-\end{itemize}
-
-\subsection*{Etiam eget sapien nibh.}
-
-% For figure citations, please use "Fig" instead of "Figure".
-Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
-
-% Place figure captions after the first paragraph in which they are cited.
-
-% Results and Discussion can be combined.
-\section*{Results and Discussion}
-
-Scientific publications form the backbone of each of these five networks.
+\section*{Results and Discussion} Scientific publications form the backbone of each of these five networks.
 The initial assumptions of appropriate citation and retrospective citation discovery (Introduction) suggest that network nodes that are common to multiple networks are likely to be influential.
 Accordingly.
-we explored the extent and nature of intersections across networks, we calculated intersection counts for all possible combinations of Alemtuzumab, Imatinib, Nelarabine, Ramucirumab, and Sunitinib (Table 3).
-14 publications are cited in all five networks and are shown in Table 4.
+we explored the extent and nature of intersections across networks, we calculated intersection counts for all possible combinations of Alemtuzumab, Imatinib, Nelarabine, Ramucirumab, and Sunitinib (S1 Table 1).
+We also applied intersection analysis as above at a finer level of granularity by computing intersection counts for first generation citations (citing\_pmid) and second generation citations (cited\_sid).
+The results are displayed as Venn diagrams in Figures 1 and 2 respectively.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.15]{citing_pmid.png}
+\caption{{\bf Publications Common To First Generation References in Networks}
+Intersections were calculated across all five networks for citing\_pmids (the first generation of references) and displayed as a Venn diagram.
+No publications are common to all five networks.
+A single publication is cited in four of five networks.
+Abbreviations: alem (Alemtuzumab),imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
+\label{fig1}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.15]{cited_sid.png}
+\caption{{\bf Publications Common To Second Generation References in Networks}
+Intersections were calculated across all five networks for cited\_sids (the second generation of references) and displayed as a Venn diagram.
+14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
+\label{fig2}
+\end{figure}
 
@@
 \vspace{2.5 mm}
-\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies.
-A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature.
-Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve literature cited by this foundational set (cited\_sid).
-Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field}
+\caption{{\bf Intersection of Five Networks: Second Generation Publications} Publications common to all networks at the second generation level (cited\_sid, Fig 2). } 
 \label{table4}
@@
 \end{table}
+At the network level, 14 publications comprise the intersection of all five networks.
+Strikingly, not even one publication is common to all five networks at the first generation level although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies\cite{bibKohler}, is cited in four out of five networks.
+All 14 publications, the intersection of five networks, were in the second generation of citations and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references.
+We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4), analytical and structural biochemistry techniques (3) and cancer biology (2).
+Of these last two, one is a review of the p53 gene\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia\cite{bibFolkman}.
+Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the the general scientific literature \cite{bibVanNoorden}.
+As the subject of another study, we are actively working on a scalable strategy to characterize the entire dataset as well as all combinations of intersections.
 
-Thus, we also applied intersection analysis as above at a finer level of granularity by computing intersection counts for first generation citations (citing\_pmid) and second generation citations (cited\_sid).
-The results are displayed as Venn diagrams in Figures 1 and 2 respectively.
-Strikingly, no publications are common to all five networks at the first generation level although a single publication, the highly influential work of Kohler and Milstein\cite{bibKohler}, is cited in four out of five networks.
-All 14 publications cited in our set of five networks were in the second generation of citations and another 198 were found  across various the four-network combinations, roughly an order of magnitude greater than the case of cited references.
-We manually grouped the 14 publications using high level descriptive terms and noted statistical techniques (5 publications), molecular and cell biological methods (4), analytical and structural biochemistry techniques (3) and cancer biology (2).
-Of these last two, one is a review of the p53 gene [cite] and the second is a study of angiogenesis in children with acute lymphoblastic leukemia [cite].
-Thus, the majority of this small set of 14 publications concerns methods that are heavily cited in these therapeutic development networks.
-We are actively working on characterizing the entire dataset as well as intersecting subsets using methods that would scale to thousands of publications and these results will be shared in another publication [needs to be reworded].
-
-\begin{table}[!ht]
-%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\scalebox{0.9}{
-\begin{tabular}{|l+l|l|l|l|l|l|l|}
-\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
-Therapeutic & citing\_pmid count & citing\_sid count & cited\_sid count  & cited\_pmid count  \\ \hline
-$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
-$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
-$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
-$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
-$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
-\end{tabular}
-}
-\vspace{2.5 mm}
-\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies.
-A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature.
-Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve cited publications (cited\_sid).
-Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field}
-\label{table2}
-%\end{adjustwidth}
-\end{table}
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=0.15]{citing_pmid.png}
-\caption{{\bf Publications Common To First Generation References in Networks}
-Intersections were calculated across all five networks for citing\_pmids (the first generation of references) as well as cited\_sids (the second generation of references) and displayed as a Venn diagram.
-No publications are common to all five networks.
-A single publication is cited in four of five networks.
-Abbreviations: alem (Alemtuzumab),imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
-\label{fig1}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=0.15]{cited_sid.png}
-\caption{{\bf Publications Common To Second Generation References in Networks}
-Intersections were calculated across all five networks for cited\_sids (the first generation of references) as well as cited\_sids (the second generation of references) and displayed as a Venn diagram.
-14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
-\label{fig2}
-\end{figure}
-
-\subsection*{Network Features}
-\subsection*{Intersection Across Networks} this is a 
-\subsection*{Supporting awards and peer-review}
-\subsection*{Future Directions}
-
-\begin{table}[!ht]
-%\begin{adjustwidth}{-0.51in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\vspace{2.5 mm}
-\scalebox{0.8}{
-\begin{tabular}{|l| l| l| l| l| l| l| l|}
-\hline
-alem(A) & imat(I) & nela(N) & ramu(R) & suni(S) & combination  & intersection\_count &no\_of\_drugs\\ 
- \hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
-X & X & X & X & X & AINRS &  \textbf{14} & 5 \\ 
-\hline
-X & X &  & X & X & AIRS & \textbf{107} & 4 \\ 
-\hline
-X & X & X & X &  & AINR &  28 & 4 \\ 
-\hline
-X & X & X &  & X & AINS &  25 & 4 \\ 
-\hline
-& X & X & X & X & INRS &  22 & 4 \\ 
-\hline
-X &  & X & X & X & ANRS &  16 & 4 \\ 
-\hline 
-& X &  & X & X & IRS & \textbf{1762} & 3 \\ 
-\hline
-X & X &  & X &  & AIR & 231 & 3 \\ 
-\hline
-X & X &  &  & X & AIS & 211 & 3 \\ 
-\hline
-X &  &  & X & X & ARS & 156 & 3 \\ 
-\hline
-X & X & X &  &  & AIN &  81 & 3 \\ 
-\hline
-X &  & X & X &  & ANR &  56 & 3 \\ 
-\hline 
-& X & X &  & X & INS &  49 & 3 \\ 
-\hline
-& X & X & X &  & INR &  44 & 3 \\ 
-\hline
- &  & X & X & X & NRS &  40 & 3 \\ 
-\hline
-X &  & X &  & X & ANS &  32 & 3 \\ 
-\hline 
-&  &  & X & X & RS & \textbf{7442} & 2 \\ 
-\hline
-& X &  &  & X & IS & 5415 & 2 \\ 
-\hline
-& X &  & X &  & IR & 2507 & 2 \\ 
-\hline
-X & X &  &  &  & AI & 1240 & 2 \\ 
-\hline
-X &  &  & X &  & AR & 448 & 2 \\ 
-\hline
-X &  &  &  & X & AS & 359 & 2 \\ 
-\hline
-X &  & X &  &  & AN & 334 & 2 \\ 
-\hline 
-& X & X &  &  & IN & 232 & 2 \\ 
-\hline
-&  & X & X &  & NR & 115 & 2 \\ 
-\hline 
- &  & X &  & X & NS & 111 & 2 \\ 
-\hline
-&  &  & X &  & R & \textbf{49006} & 1 \\ 
-\hline 
-&  &  &  & X & S & 34257 & 1 \\ 
-\hline 
-& X &  &  &  & I & 27706 & 1 \\ 
-\hline
-X &  &  &  &  & A & 8978 & 1 \\ 
-\hline
-&  & X &  &  & N & 2498 & 1 \\ 
-\hline
-\end{tabular}}
-\vspace{2.5 mm}
-\caption{
-{\bf Intersecting Publications Across Networks} Intersections were calculated for the set of publications associated with each network.
-Both citing and cited references were included in each set and  Scopus identifiers were used to to minimize information loss (Table 2).
-Intersection counts are shown for all possible combinations of the five therapeutics.
-The largest intersection count in each combination group is shown in boldface.
-Therapeutic names are abbreviated as follows: alem (Alemtuzumab), imat(Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni (Sunitinib).
-}
-
-%\begin{flushleft} Intersections were calculated for the set of publications associated with each network.
-Both citing and cited references were included in each set and  Scopus Ids were used as identifiers to minimize loss of data when mapping back to pmids.
-Intersection counts are shown for all possible combinations of the five therapeutics.
-The largest intersection count in each combination group is shown in boldface.
-%\end{flushleft}
-\label{table3}
-%\end{adjustwidth}
-\end{table}
-
-%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
-\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}
-\subsubsection*{3rd Level Heading.}
-
-Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
-
-\begin{enumerate}
-	\item{react}
-	\item{diffuse free particles}
-	\item{increment time by dt and go to 1}
-\end{enumerate}
-
-\subsection*{Sed ac quam id nisi malesuada congue.}
-
-Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
-
-\begin{itemize}
-	\item First bulleted item.
-	\item Second bulleted item.
-	\item Third bulleted item.
-\end{itemize}
-
-%\section*{Discussion}
-
-\section*{Conclusion}
-
-CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
-Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna.
-Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-Nam condimentum sem eget mollis euismod.
-Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex.
-Nunc est dui, sodales sed mauris nec, auctor sagittis leo.
-Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor.
-For more information, see \nameref{S1_Appendix}.
+Not restricted to  drug discovery and cures alone, the approach can be used to support efficient explorations of science history, an understanding of collaboration across domains, enrich portfolio analysis, planning and optimization, and enable communications of the societal value of research.
+While finer critical evaluation of the content of datasets is perhaps best left to experts, the methodology is broadly accessible and can be thought of as another tool for citizen science.
 
@@
 
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{S1_Fig}
-{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
+\paragraph*{S1 File.}
+\label{S1_File}
+{\bf Network Calculations} The basis of calculations for network metrics.
 
@@
 \label{S2_Fig}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 File.}
-\label{S1_File}
-{\bf Lorem Ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Video.}
-\label{S1_Video}
 {\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
@@
 
-\section*{Acknowledgments}
-Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Nam id pretium nisi.
-Sed ac quam id nisi malesuada congue.
-Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
-
-\begin{eqnarray}
-\label{eq:schemeP} 
-	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
-\end{eqnarray}
+\section*{Acknowledgments} We thank NETE for its support of the nascent Netelabs concept.
 
@@
 
-\begin{figure}[!h]
-\caption{{\bf Bold the figure title.}
-Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
-\includegraphics{citing_pmid.png}
-\label{fig2}
-\end{figure}
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here.
-% 
 \begin{thebibliography}{10}
@@
 
-\bibitem{bibLauer}
-Lauer MS.
-\newblock {{P}CSK9 Inhibitors: Lots of Work Done, Lots More to Do.}
-\newblock Ann Intern Med. 2016 Mar; 164(9):624-625.
+\bibitem{bibMaldame}
+Maldame, J.
+\newblock {{T}he Importance Of The History Of Science In Intellectual Formation}
+\newblock Scripta Varia 2002 104:237-248
 
@@
 
-\bibitem{bibMaldame}
-Maldame, J.
-\newblock {{T}he Importance Of The History Of Science In Intellectual Formation}
-\newblock Scripta Varia 2002 104:237-248
+\bibitem{bibLauer}
+Lauer MS.
+\newblock {{P}CSK9 Inhibitors: Lots of Work Done, Lots More to Do.}
+\newblock Ann Intern Med. 2016 Mar; 164(9):624-625.
 
@@
 \newblock { {C}ontinuous cultures of fused cells secreting antibody of predefined specificity.}
-\newblock Nature. 1975 256: 495?497
+\newblock Nature. 1975 256: 495-497
+
+\bibitem{bibLevine}
+Levine, AJ.
+\newblock {{p53}, the cellular gatekeeper for growth and division.}
+\newblock Cell. 1997 Feb 7;88(3):323-31.
+
+\bibitem{bibFolkman}
+Perez-Atayde AR, Sallan SE, Tedrow U, Connors S, Allred E, Folkman J.
+\newblock {{Spectrum} of tumor angiogenesis in the bone marrow of children with acute lymphoblastic leukemia}
+\newblock Am J Pathol. 1997 Mar;150(3):815-21.
+
+\bibitem{bibVanNoorden}
+Van Noorden R, Maher B, Nuzzo R.
+\newblock {{T}he top 100 papers}
+\newblock Nature 2014 514: 550?553
 
@@
 \newblock PLoS Genet. 2011 Oct;7(10):e1002337.
-
 \end{thebibliography}
-
 \end{document}

### 2017-05-30 Paper/plos-latex-template/plos_latex_template.tex
updates

@@
 To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble component events in the history of a cure and analyze them.
-The methodology is extensible beyond cure networks and its use supports (i) efficiency in  exploring  the scientific history of a research advance (ii) improved documenting and understanding of collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
-Building upon techniques for single networks and linking the work of approximately 250,000 authors in 100,000 scientific publications, we have conducted a case study of five anti-cancer therapeutics for the purpose of exploring the relationship across networks.
-We have enriched the content of these five networks by annotating them with information on research awards as well as peer review that preceded these awards.
+This methodology is extensible beyond cure networks and its use supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
+As a proof of principle, we have conducted a case study of five anti-cancer therapeutics.
+For the purpose of exploring the relationship across networks, we have built upon a technique for single networks and linked the work of approximately 250,000 authors in 100,000 scientific publications, we have enriched the content of networks for these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards.
 Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as a core set of awards from the National Institutes of Health that supported this research.
@@
 Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will uncover previous influential discovery (\textit{ibid}).
-Further, when coupled with the knowledge that accrues from the use of the drug, the knowledge of a drug development network enables a recursive learning of the pathogenesis of the disease it is being used to treat\cite{bibChan}.
+Beyond using a digital methodology to assemble a set of facts about a major scientific advance, however, these studies also support a contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time\cite{bibMaldame}.
+Coupled with the knowledge that accrues from the clinical use of the drug, knowledge of a drug development network also enables a recursive learning of the pathogenesis of the disease it is being used to treat as as been noted for the burgeoning field of immunotherapeutics\cite{bibChan}.
 
-Beyond using a digital methodology to assemble a set of facts about a major scientific advance, however, these studies support a contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time\cite{bibMaldame}.
+Such studies (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases (ii) support strategic communications to oversight bodies, and (iii) help communicate the societal value of research\cite {bibLauer}.
 Williams and colleagues have elegantly demonstrated the feasibility and value of data mining and network analysis using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}).
 These authors observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-related research over a period greater than 100 years.
-Such studies (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases (ii) support strategic communications to oversight bodies, and (iii) help communicate the societal value of research\cite {bibMaldame,bibLauer}.
 
@@
 Ascertaining the nature of the interactions, if any, between networks, is also of considerable interest since it would support an understanding of collaboration across networks as well as common features of science networks.
-Lastly, scaling from case studies to mapping the entire domain of drug development may be beneficial in understanding and optimizing activities in the pharmaceutical industry.
+Lastly, scaling from case studies to mapping the entire domain of drug development may be beneficial in future resource allocation and optimization of drug development activities.
 
-To address these questions, we have enhanced the original approach to (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extended single network analysis to map publications and authors across multiple networks (v) refactored the network analysis code of Williams et al.
+To address these questions, we have enhanced prior art to (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extended single network analysis to map publications and authors across multiple networks (v) refactored the network analysis code of Williams et al.
 for better performance.
 To evaluate these extensions, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer.
-We present the results of this case study as a step towards mapping the universe of FDA-approved drugs and biologicals and a dataset that can be interrogated by other researchers.
+We present the results of this case study as a body of work for interrogation and improvement by other researchers, and a step towards mapping the universe of FDA-approved drugs and biologicals.
 
@@
 
-\textbf{FDA documents} The drugs@fda website\cite{bib6} was searched for each of the five therapeutics and cited references in the medical review document were manually extracted and matched to pmids.
+\textbf{FDA documents} The drugs@fda website\cite{bibFDA} was searched for each of the five therapeutics and cited references in the medical review document were manually extracted and matched to pmids.
 FDA Approval Summaries, articles published in journals by FDA staff, were available for all five therapeutics and contain cited references.
@@
 Identification of this patent was performed using multiple web sources.
-The US patent number was then used to identify the patent and the non-patent citation list from Google Patents \cite{bib8} was manually processed by searching PubMed for appropriate pmids.
+The US patent number was then used to identify the patent and the non-patent citation list from Google Patents \cite{bibGooglePatents} was manually processed by searching PubMed for appropriate pmids.
 While we developed a citation matching tool for non-patent literature for this purpose, the accuracy of manual searches was far higher and were used to generate the data in this study.
 
-\textbf{Post-approval literature reviews} Review articles published after a therapeutic's approval by the FDA are independent assessments of the the development of a therapeutic.
+\textbf{Post-approval literature reviews} Review articles published after a therapeutic's approval by the FDA are independent studies of the the development of a therapeutic.
 Accordingly, PubMed was searched for review articles of a therapeutic that were published between the date of FDA approval and one year following the date of approval and cited references in these reviews were extracted using PubMed and Scopus.
@@
 
-Both citing and cited pmids were mapped to NIH grants and peer review panels (study sections) using information made publicly available by NIH through NIH ExPORTER.
+Both citing and cited pmids were mapped to NIH grants and peer review panels (study sections) using information made publicly available by NIH through NIH ExPORTER\cite{bibNIHExPORTER}.
 The Center for Scientific Review at NIH organizes the review of the majority of grant applications submitted to the NIH and has over 170 chartered study sections with defined scientific interests and relatively stable reviewer membership.
 Thus, we enriched our network data by identifying those study sections associated with the awards that supported publications in our networks.
-Since Special Emphasis Panels vary in scientific interests from year to year, we restricted our mapping to chartered study sections at the Center for Scientific Review.
 
@@
 All 14 publications, the intersection of five networks, were in the second generation of citations and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references.
-We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4), analytical and structural biochemistry techniques (3) and cancer biology (2).
+We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4 publications), analytical and structural biochemistry techniques (3 publications) and cancer biology (2 publications).
 Of these last two, one is a review of the p53 gene\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia\cite{bibFolkman}.
 Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the the general scientific literature \cite{bibVanNoorden}.
-As the subject of another study, we are actively working on a scalable strategy to characterize the entire dataset as well as all combinations of intersections.
+As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks.
 
-Not restricted to  drug discovery and cures alone, the approach can be used to support efficient explorations of science history, an understanding of collaboration across domains, enrich portfolio analysis, planning and optimization, and enable communications of the societal value of research.
-While finer critical evaluation of the content of datasets is perhaps best left to experts, the methodology is broadly accessible and can be thought of as another tool for citizen science.
+With its annual budget of approximately US\$32 billion, NIH is a major funder of biomedical research.
+We took advantage of publicly available data\cite{bibNIHExPORTER} to identify grant support for the publications in our five networks by mapping them to pmids.
+A total 19,104 unique grant numbers was harvested of which 112 were found in all five networks.
+These awards were grouped by major type  and visualized (Fig 3.).
+Of note, Research Program Projects and Center grants is proportionately larger in the intersection group when compared to the total population where the proportion of research projects is larger.
+We speculate that the broader and collaborative nature of such awards may be more likely to result in a methods-rich population of publications than the more focused research project kind of award but further and more rigorous study is needed to elucidate this question.
+The two populations of publications and grants exist in a `many to many' relationship in that each publication can acknowledge support from multiple grants and each grant can support multiple publications.
+Further, a significant loss of information when mapping from cited\_sid to cited\_pmid.
+Thus we believe that these numbers could be an underestimate of actual grant support that needs to be interpreted in the context of the false-positive and false-negative content of the publicly available data.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.15]{proj_percent.png}
+\caption{{\bf NIH Research Support} Grant and contract support for publications from NIH in the five networks was identified using ExPORTER data (Materials and Methods).
+19,104 unique project numbers were identified of which 112 projects were common to all five networks.
+Projects were grouped by mechanism (i) P-  Research Program Projects and Centers (ii) R- Research Projects (iii) M-General Clinical Research Centers Programs (iv) N-Research and Development-Related Contracts (v) U-Cooperative Agreements (vi) T-Training Programs (vii) Z- Intramural Research.
+For each mechanism, the number of projects in the intersection of all five networks was plotted against the number in the union of all five networks (both expressed as percentages of their respective totals).
+A higher proportion of Research Program Projects and Centers awards is found in the intersection group.}
+\label{fig3}
+\end{figure}
+
+Not restricted to  drug discovery and cures alone, our approach offers burden-reduction in explorations of science history, contributes to the understanding of collaboration across domains, enriches portfolio analysis, planning and optimization, and enables communications of the societal value of research.
+While finer critical evaluation of the content of datasets generated through this approach is perhaps best left to experts, the methodology is broadly accessible and can be viewed as another tool for citizen science.
+
+Research support from NIH is typically made through a two stage peer-review process.
+The Center for Scientific Review at NIH reviews between 50,000-60,000 grant applications each year\cite{bibBoyack}, a process involving more than 15,000 expert reviewers and individual Institutes and Centers manage smaller scale peer review operations.
+Thus, another layer of collaborative scientific activity preceded the awards that supported research that in turn resulted in the scientific output captured in these five networks.
+To describe this layer at a high-level, we matched the awards in the the five networks to the peer review panels (study sections) that evaluated them for scientific merit and calculated the intersection and union of these peer review panels.
+Eighty eight unique panel identifiers formed the intersection.
+Of these, 11 are distinguishable as Special Emphasis Panels that could be either one-time or recurring panels with temporary members, the remaining 77 are chartered panels with relatively stable membership.
+Some of these panels no longer exist and public records are not easily available to determine their scientific focus.
+For the X that could be classified (Supplemental), it is evident that they represent a rich mix of basic sciences such as chemistry, biophysics, cell biology, clinical sciences such as pathology, radiology, endocrinology.
+Four hundred and seven unique panel identifiers formed the union of all five networks.
+Of these 28 were Special Emphasis Panels, the remaining 379 panels were chartered as in the case of the intersection.
+These data provide evidence of broad input from invited experts in a collaborative activity that selects promising scientific projects.
+Assuming an average of 25 reviewers per panel (the number is likely to range from 5-40) and not considering that some of these panels are likely to have met met multiple times during the lifespan of the awards in question, a minimum of 10,000 experts comprised this additional layer of scientific regulation.
+We believe that the actual number is likely to be at least double.
 
@@
 
-\section*{Acknowledgments} We thank NETE for its support of the nascent Netelabs concept.
+\section*{Acknowledgments} %We thank Sandeep Somaiya for his support of of the nascent Netelabs concept. We thank Tandy Warnow, and Andy Chan for helpful suggestions.
 
@@
 Lauer MS.
-\newblock {{P}CSK9 Inhibitors: Lots of Work Done, Lots More to Do.}
+\newblock {{P}CSK9 Inhibitors: Lots of Work Done, Lots More to Do}
 \newblock Ann Intern Med. 2016 Mar; 164(9):624-625.
@@
 
+\bibitem{bibGooglePatents}
+Google Corporation
+\newblock {{G}oogle Patents}
+\newblock https://patents.google.com/
+
 \bibitem{bibNIHExPORTER}
@@
 \newblock https://exporter.nih.gov/
-
-\bibitem{bibGooglePatents}
-Google Corporation
-\newblock {{G}oogle Patents}
-\newblock https://patents.google.com/
 
@@
 \newblock {{T}he top 100 papers}
-\newblock Nature 2014 514: 550?553
+\newblock Nature 2014 514: 550-553
+
+\bibitem{bibBoyack}
+Boyack KW, Chen M-C, Chacko G. 
+\newblock {{C}haracterization of the Peer Review Network at the Center for Scientific Review, National Institutes of Health}
+\newblock  PLoS One 2014 /10.1371/journal.pone.0104244
 
@@
 infection through a transposon insertion followed by a {D}uplication}.
-\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
+\newblock PLoS Gene 2011 Oct;7(10):e1002337.
 \end{thebibliography}

### 2017-05-31 assembly/load_interim_results.R
clip SourceYear from 1900-2015

@@ -118,5 +118,5 @@ write.delim(ramu_m3, file="ramu_pubref.tsv", quote = FALSE, row.names = FALSE, s
 write.delim(suni_m3, file="suni_pubref.tsv", quote = FALSE, row.names = FALSE, sep = "\t")
 
 
-w
+
 

### 2017-05-31 assembly/exp_proj_link.R
clip SourceYear from 1900-2015

@@ -15,13 +15,23 @@ setwd("~/NETELabs_CaseStudies/assembly/interim_results")
 # save(interim_results,file="interim_results.RData")
 
 # Read in pub_out (pmid-SID) and pub_cites (PubSID to SID) 
+
+# Need to add clipper to restrict SourceYear from 1900-2015.
+
 pub_out <- read.csv("pub_out.csv",colClasses=rep("character",6))
 pub_cites <- read.csv("pub_cites.csv",colClasses=rep("character",9))
+pub_cites$SourceYear <- as.integer(pub_cites$SourceYear)
+
+library(dplyr)
+pub_cites <- pub_cites %>% filter(SourceYear >=1900 & SourceYear <=2015)
+
+
 # free up memory
 # rm(interim_results)
 # print str stats
 str(pub_out)
 str(pub_cites)
+
 
 # Read in exporter link and projects data
 exp_link <- read.csv("~//NETELabs_CaseStudies/assembly/final_results/exporter_links.csv",colClasses=(rep("character",2)))
@@ -67,7 +77,7 @@ ramu_m2 <- merge(ramu_m1,pub_cites[,1:2],by.x="SID",by.y="citingSID",all.x=TRUE)
 suni_m2 <- merge(suni_m1,pub_cites[,1:2],by.x="SID",by.y="citingSID",all.x=TRUE)
 
 # rearrange columns and change column names for better comprehension
-library(dplyr)
+
 alem_m2 <- alem_m2 %>% select(year, pmid=id,citingSID=SID,citedSID)
 imat_m2 <- imat_m2 %>% select(year, pmid=id,citingSID=SID,citedSID,year)
 nela_m2 <- nela_m2 %>% select(year, pmid=id,citingSID=SID,citedSID,year)
@@ -126,14 +136,86 @@ suni_proj <- merge(suni_pre_exp,exp_link,by.x="combined_pmid",by.y="pmid")
 proj_intersect <- unique(Reduce(intersect,list(alem_proj$project_number,imat_proj$project_number,nela_proj$project_number,ramu_proj$project_number,suni_proj$project_number)))
 proj_intersect <- data.frame(proj_number=proj_intersect,stringsAsFactors=FALSE)
 proj_intersect <- proj_intersect %>% mutate(IC=substring(proj_number,4,5),Mechanism=substring(proj_number,1,3))
+proj_intersect <- proj_intersect %>% mutate(PType=substring(Mechanism,1,1))
+
[…]

### 2017-06-01 assembly/final_results/global_RBR.R
script for global RBR

@@ -1,0 +1,49 @@
+# Calculate Global RBR
+
+setwd("~/Dropbox/ERNIE_Pico/globalscores/")
+temp <- list.files(pattern="*.csv")
+rbr_list <- list()
+for (i in 1:length(temp)) {
+	rbr_list[[i]] <- read.csv(temp[i],stringsAsFactors=FALSE,header=TRUE)
+}
+names(rbr_list) <- temp
+rm(i)
+
+alem_gRBR_at <- rbr_list[[1]]
+global_author_list <- rbr_list[[2]]
+imat_gRBR_at <- rbr_list[[3]]
+nela_gRBR_at <- rbr_list[[4]]
+ramu_gRBR_at <- rbr_list[[5]]
+suni_gRBR_at <- rbr_list[[6]]
+
+global_author_list <- global_author_list[,c(1,24)]
+
+temp_alem_gRBR_at <- alem_gRBR_at[,c(1,3,4)]
+temp_imat_gRBR_at <- imat_gRBR_at[,c(1,3,4)]
+temp_nela_gRBR_at <- nela_gRBR_at[,c(1,3,4)]
+temp_ramu_gRBR_at <- ramu_gRBR_at[,c(1,3,4)]
+temp_suni_gRBR_at <- suni_gRBR_at[,c(1,3,4)]
+
+global_doc_counts <- rbind(temp_alem_gRBR_at,temp_imat_gRBR_at,temp_nela_gRBR_at,temp_ramu_gRBR_at,temp_suni_gRBR_at)
+global_doc_counts <- unique(global_doc_counts)
+
+global_RBR <- merge(global_doc_counts,global_author_list,by.x="auth",by.y="authSID")
+
+library(dplyr)
+
+global_RBR <-  global_RBR %>% select(authSID=auth,globalInDegree,article_count,total_docCount) %>%
+mutate(global_RBR_a=globalInDegree/article_count,global_RBR_t=globalInDegree/total_docCount) %>%
+arrange(desc(global_RBR_a))
+
+print(paste("The total number of rows is",nrow(global_RBR)))
+print(paste("The number of infinity values in global_RBR_a is",nrow(global_RBR[global_RBR$global_RBR_a==Inf,])))
+print(paste("The number of values where global_RBR_a >1 is",nrow(global_RBR[global_RBR$global_RBR_a>1,])))
+
[…]

### 2017-06-02 assembly/alex_cscape.R
updating all R scripts

@@ -1,0 +1,99 @@
+# Generate Venn Diagrams for biblio and grant data 
+rm(list=ls())
+setwd("~/NETELabs_CaseStudies/assembly/interim_results/")
+load(".RData")
+# else run load_interim_results.R
+
+alem_citing_pmid <- alem_m3$citing_pmid[!is.na(alem_m3$citing_pmid)]
+imat_citing_pmid <- imat_m3$citing_pmid[!is.na(imat_m3$citing_pmid)]
+nela_citing_pmid <- nela_m3$citing_pmid[!is.na(nela_m3$citing_pmid)]
+ramu_citing_pmid <- ramu_m3$citing_pmid[!is.na(ramu_m3$citing_pmid)]
+suni_citing_pmid <- suni_m3$citing_pmid[!is.na(suni_m3$citing_pmid)]
+
+alem_cited_pmid <- alem_m3$cited_pmid[!is.na(alem_m3$cited_pmid)]
+imat_cited_pmid <- imat_m3$cited_pmid[!is.na(imat_m3$cited_pmid)]
+nela_cited_pmid <- nela_m3$cited_pmid[!is.na(nela_m3$cited_pmid)]
+ramu_cited_pmid <- ramu_m3$cited_pmid[!is.na(ramu_m3$cited_pmid)]
+suni_cited_pmid <- suni_m3$cited_pmid[!is.na(suni_m3$cited_pmid)]
+
+alem_citing_sid <- alem_m3$citing_sid[!is.na(alem_m3$citing_sid)]
+imat_citing_sid <- imat_m3$citing_sid[!is.na(imat_m3$citing_sid)]
+nela_citing_sid <- nela_m3$citing_sid[!is.na(nela_m3$citing_sid)]
+ramu_citing_sid <- ramu_m3$citing_sid[!is.na(ramu_m3$citing_sid)]
+suni_citing_sid <- suni_m3$citing_sid[!is.na(suni_m3$citing_sid)]
+
+alem_cited_sid <- alem_m3$cited_sid[!is.na(alem_m3$cited_sid)]
+imat_cited_sid <- imat_m3$cited_sid[!is.na(imat_m3$cited_sid)]
+nela_cited_sid <- nela_m3$cited_sid[!is.na(nela_m3$cited_sid)]
+ramu_cited_sid <- ramu_m3$cited_sid[!is.na(ramu_m3$cited_sid)]
[…]

### 2017-06-02 assembly/exp_proj_link.R

@@ -16,7 +16,7 @@ setwd("~/NETELabs_CaseStudies/assembly/interim_results")
 
 # Read in pub_out (pmid-SID) and pub_cites (PubSID to SID) 
 
-# Need to add clipper to restrict SourceYear from 1900-2015.
+# Clip SourceYear to restrict from 1900-2015.
 
 pub_out <- read.csv("pub_out.csv",colClasses=rep("character",6))
 pub_cites <- read.csv("pub_cites.csv",colClasses=rep("character",9))

### 2017-06-02 assembly/load_interim_results.R

@@ -96,13 +96,24 @@ nela_m3 <- merge(nela_m2,pub_out[,1:2],by.x="citedSID",by.y="SID",all.x=TRUE)
 colnames(nela_m3) <- c("cited_sid","year","citing_pmid","citing_sid","cited_pmid")
 nela_m3 <- nela_m3 %>% mutate(drug="nela") %>% select(citing_pmid,citing_sid,cited_sid,cited_pmid,year,drug)
 
+
 ramu_m3 <- merge(ramu_m2,pub_out[,1:2],by.x="citedSID",by.y="SID",all.x=TRUE)
 colnames(ramu_m3) <- c("cited_sid","year","citing_pmid","citing_sid","cited_pmid")
 ramu_m3 <- ramu_m3 %>% mutate(drug="ramu") %>% select(citing_pmid,citing_sid,cited_sid,cited_pmid,year,drug)
+ramu_glob <- ramu_m3 %>% mutate(drug="ramu") %>% select(citing_pmid,citing_sid,cited_sid,cited_pmid,year)
 
 suni_m3 <- merge(suni_m2,pub_out[,1:2],by.x="citedSID",by.y="SID",all.x=TRUE)
 colnames(suni_m3) <- c("cited_sid","year","citing_pmid","citing_sid","cited_pmid")
 suni_m3 <- suni_m3 %>% mutate(drug="suni") %>% select(citing_pmid,citing_sid,cited_sid,cited_pmid,year,drug)
+
+
+alem_glob <- alem_m3 %>% mutate(drug="alem") %>% select(citing_pmid,citing_sid,cited_sid,cited_pmid,year)
+imat_glob <- imat_m3 %>% mutate(drug="imat") %>% select(citing_pmid,citing_sid,cited_sid,cited_pmid,year)
+nela_glob <- nela_m3 %>% mutate(drug="nela") %>% select(citing_pmid,citing_sid,cited_sid,cited_pmid,year)
+ramu_glob <- ramu_m3 %>% mutate(drug="ramu") %>% select(citing_pmid,citing_sid,cited_sid,cited_pmid,year)
+suni_glob <- suni_m3 %>% mutate(drug="suni") %>% select(citing_pmid,citing_sid,cited_sid,cited_pmid,year)
+
+glob_pubref <- rbind(alem_glob,imat_glob,nela_glob,ramu_glob,suni_glob) %>% unique()
 
 write.csv(alem_m3,file="alem_pubref.csv")
[…]

### 2017-06-08 Paper/plos-latex-template/Supplemental.tex
updates

@@
 
+\begin{table}[!ht]
+\centering
+\vspace{2.5 mm}
+\begin{tabular}{|l| l| l|}
+\hline
+Name& nPIR & PPR \\
+\hline
+\hline
+Ferrara N.	 & 46693 & 1.12 \\ 
+Folkman J. & 23660 & 1.15 \\ 
+Ullrich A. & 23034 & 1.46 \\ 
+Jain R. & 15267 & 1.13 \\ 
+Heldin C.	& 15148 & 1.21 \\ 
+Druker B.	& 15088 & 1.16 \\ 
+Schlessinger J.	& 14996 & 1.48 \\ 
+Dvorak H.	 & 14230 & 1.13 \\ 
+ Alitalo K.	& 13812 & 1.24 \\ 
+ Slamon D. & 13587 & 1.46 \\ 
+ Baselga J. & 12908 & 1.36 \\ 
+ Kantarjian H. & 12029 & 1.17 \\ 
+ Hicklin D.	 & 11775 & 1.17 \\ 
+ Witte O. & 11449 & 1.08 \\ 
+ Hanahan D. & 11072 & 1.19 \\ 
+ Buchdunger E.	 & 11032 & 1.22 \\ 
+ Risau W.	& 10950 & 1.24 \\ 
+ Talpaz M.	 & 10713 & 1.13 \\ 
+ Mendelsohn J.	 & 10534 & 1.54 \\ 
+ Lydon N. & 9988 & 1.18 \\ 
+ Goldman J. & 9927 & 1.11 \\ 
+ Shibuya M. & 9639 & 1.21 \\ 
+ Kitamura Y. & 9486 & 1.24 \\ 
+ Waldmann H. & 9363 & 1.04 \\ 
+ Kerbel R.	 & 9266 & 1.16 \\ 
+   \hline
+\end{tabular}
+\vspace{2.5 mm}
+\caption{
+{\bf Elite Performers} Researchers with the highest nPIR scores in the network of 5 anti-cancer therapeutics are listed.
+Also shown for each researcher is their PIRpartitionRatio (PPR).
+The nPIR indicates influence across all five networks and the PPR provides an estimate of how this influence is partitioned across each of the five networks (Materials and Methods).
+This list and its ordering should be considered in the context of the data being analyzed and not interpreted as an absolute ordering of research excellence in the field.}
+\label{table2}
+\end{table}
+
 \end{document}

### 2017-06-08 Paper/plos-latex-template/Tables_Figs.tex
updates

--- 2017-05-30 Paper/plos-latex-template/plos_latex_template.tex
@@
 
-% create \thickcline for thick horizontal lines of variable length
+% added by George
+%\usepackage{wrapfig}
+%\usepackage{caption}
+\usepackage{subcaption}
+
+% create \thickline for thick horizontal lines of variable length
 \newlength\savedwidth
@@
 \renewcommand{\figurename}{Fig}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
 
@@
 \begin{document}
-\vspace*{0.2in}
 
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline{Research Synergy and Drug Development: Bright Stars in Neighboring Constellations} % Please use "title case" (capitalize all terms in the title except conjunctions, prepositions, and articles).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Samet Keserci\textsuperscript{1},
-%Samet Keserci\textsuperscript{1,2\Yinyang},
-Eric Livingston\textsuperscript{2},
-Lingtian Wan\textsuperscript{1,\textcurrency},
-Alexander R. Pico\textsuperscript{3},
-%Name5 Surname\textsuperscript{2\ddag},
-%Name6 Surname\textsuperscript{2\ddag},
- \& George Chacko\textsuperscript{1*}
-%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
-\\
-\bigskip
-\textbf{1} Netelabs, NET ESolutions Corporation, McLean, VA, USA
-\\
-\textbf{2} Elsevier Research Intelligence, Elsevier Inc., Bethesda, MD, USA
-\\
-\textbf{3} Gladstone Institutes, University of California San Francisco, San Francisco, CA, USA
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-%\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-%\ddag These authors also contributed equally to this work.
-
-% Current address notes
-\textcurrency Current Address: Facebook Corporation, Menlo Park, CA, USA % change symbol to "\textcurrency a" if more than one current address note
-% \textcurrency b Insert second current address 
-% \textcurrency c Insert third current address
-
-% Deceased author note
-%\dag Deceased
-
-% Group/Consortium Author Note
-%\textpilcrow Membership list can be found in the Acknowledgments section.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-*Correspondence: george@nete.com
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-
-Drug discovery and the subsequent availability of new breakthrough therapeutics or `cures' are compelling examples of societal benefit from advances in research.
-Such advances are invariably collaborative, involving the contributions of many scientists in a `cure network' where prior theory and experiment is built upon.
-To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble component events in the history of a cure and analyze them.
-The methodology is extensible beyond cure networks and its use supports (i) efficiency in  exploring  the scientific history of a research advance (ii) improved documenting and understanding of collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
-Building upon techniques for single networks and linking the work of approximately 250,000 authors in 100,000 scientific publications, we have conducted a case study of five anti-cancer therapeutics for the purpose of exploring the relationship across networks.
-We have enriched the content of these five networks by annotating them with information on research awards as well as peer review that preceded these awards.
-Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as a core set of awards from the National Institutes of Health that supported this research.
-Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented by these networks.
-
-\linenumbers
-
-\section*{Introduction}
-
-Data mining of public data sources coupled with network analysis enables the assembly and quantitative description of research discoveries that were influential in the development of a breakthrough therapeutic or `cure'.
-The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents the progress of concepts from basic research to a cure is termed a `cure network' \cite {bibWilliams}.
-Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will uncover previous influential discovery (\textit{ibid}).
-Further, when coupled with the knowledge that accrues from the use of the drug, the knowledge of a drug development network enables a recursive learning of the pathogenesis of the disease it is being used to treat\cite{bibChan}.
-
-Beyond using a digital methodology to assemble a set of facts about a major scientific advance, however, these studies support a contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time\cite{bibMaldame}.
-Williams and colleagues have elegantly demonstrated the feasibility and value of data mining and network analysis using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}).
-These authors observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-related research over a period greater than 100 years.
-Such studies (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases (ii) support strategic communications to oversight bodies, and (iii) help communicate the societal value of research\cite {bibMaldame,bibLauer}.
-
-Extending this methodology to study additional cures and significant research advances in general is a logical next step.
-Ascertaining the nature of the interactions, if any, between networks, is also of considerable interest since it would support an understanding of collaboration across networks as well as common features of science networks.
-Lastly, scaling from case studies to mapping the entire domain of drug development may be beneficial in understanding and optimizing activities in the pharmaceutical industry.
-
-To address these questions, we have enhanced the original approach to (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extended single network analysis to map publications and authors across multiple networks (v) refactored the network analysis code of Williams et al.
-for better performance.
-To evaluate these extensions, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer.
-We present the results of this case study as a step towards mapping the universe of FDA-approved drugs and biologicals and a dataset that can be interrogated by other researchers.
-
-\section*{Materials and Methods}  A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration was selected for this study (Table 1).
-Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab are humanized antibodies that target cell surface receptors.
-For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.\cite{bibWilliams} but with specific modifications detailed below.
-An allowance of 2 months was also made for `publication lag' when assembling referenced material.
-For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included.
-For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (below).
+\vspace{30mm}
 
@@
 The active ingredient for each of these five therapeutics is listed in column 1.
+The unique identifier for each therapeutic is the FDA assigned NDA or BLA number.
 While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic.
@@
 \end{table}
-
-\textbf{Clinical trials} The national clinical trials database (clinicaltrials.gov) was searched for clinical trials of the five therapeutics that completed on or the data of FDA approval.
-Both cited references and publications from these clinical trials were collected if they were published within the approval date plus two months.
-To capture publications associated with the clinical trials that were not displayed in clinical trials.gov, PubMed was also searched with the unique identifier (NCT number) of any clinical trials that were identified.
-To capture publications of clinical trials not registered in clinicaltrials.gov, PubMed was searched using the therapeutic name as keyword, publication type as ``clinical trial'', and an appropriate date restriction as in searches of clinicaltrials.gov.
-For example, the search term (((``alemtuzumab"[Supplementary Concept] OR ``alemtuzumab"[All Fields]) OR (``alemtuzumab"[Supplementary Concept] OR ``alemtuzumab"[All Fields] OR ``campath"[All Fields])) AND (``1900/0101"[PDAT] : ``2001/07/31''[PDAT])) AND ``clinical trial"[Publication Type] was used to identify publications of clinical trials for Alemtuzumab.
-
-\textbf{FDA documents} The drugs@fda website\cite{bib6} was searched for each of the five therapeutics and cited references in the medical review document were manually extracted and matched to pmids.
-FDA Approval Summaries, articles published in journals by FDA staff, were available for all five therapeutics and contain cited references.
-If the published date of a citation exceeded the approval date plus two months, the publication was not included.
-
-\textbf{Patents} For each therapeutic a single patent was identified that best represented the most relevant invention to the therapeutic at hand.
-Identification of this patent was performed using multiple web sources.
-The US patent number was then used to identify the patent and the non-patent citation list from Google Patents \cite{bib8} was manually processed by searching PubMed for appropriate pmids.
-While we developed a citation matching tool for non-patent literature for this purpose, the accuracy of manual searches was far higher and were used to generate the data in this study.
-
-\textbf{Post-approval literature reviews} Review articles published after a therapeutic's approval by the FDA are independent assessments of the the development of a therapeutic.
-Accordingly, PubMed was searched for review articles of a therapeutic that were published between the date of FDA approval and one year following the date of approval and cited references in these reviews were extracted using PubMed and Scopus.
-
-\textbf{Pre-approval literature searches} Literature searches were performed using PubMed with a date range of 1900/01/01 to two months post-FDA approval.
-For example, the search term ((alemtuzumab) OR campath) AND (``1900/01/01"[Date - Publication] : ``2001/07/31"[Date - Publication]) was used to retrieve articles of interest relevant to alemtuzumab.
-
-Citing\_pmids from the five different sources above  were combined and deduplicated.
-Using the Scopus database and its APIs, these citing\_pmids were mapped to Scopus identifiers (citing\_sid) from which a second generation of cited references (cited\_sid) was extracted., These cited\_sids, were in turn, mapped back to pmids (cited\_pmid).
-Whereas mapping between PubMed and Scopus identifiers at the citing\_pmid and citing\_sid stage resulted in 1\% or less information loss, mapping at the cited\_sid to cited\_pmid resulted in 15-20 \% information loss.
-Accordingly the Scopus data  was used as the backbone of the publication component of the network and the cited\_pmid information was treated as an annotation layer.
-These observations are summarized in Table 2 and include the count of null values when mapping from citing\_sid to cited\_sid.
+\clearpage
 
@@
 \end{table}
-
-Both citing and cited pmids were mapped to NIH grants and peer review panels (study sections) using information made publicly available by NIH through NIH ExPORTER.
-The Center for Scientific Review at NIH organizes the review of the majority of grant applications submitted to the NIH and has over 170 chartered study sections with defined scientific interests and relatively stable reviewer membership.
-Thus, we enriched our network data by identifying those study sections associated with the awards that supported publications in our networks.
-Since Special Emphasis Panels vary in scientific interests from year to year, we restricted our mapping to chartered study sections at the Center for Scientific Review.
-
-The resultant data were modeled as hierarchical networks and analyzed using metrics based on network topology.
-We calculated the propagated in-degree rank (PIR) metric of Williams \cite {bibWilliams}.
-PIR represents the sum of weighted citation scores for all articles in a network that can be attributed to an author.
-In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a globalPIR score, which was normalized to the sum of PIR scores within each network.
-Secondly, we calculated the RBR metric of Williams et al.
-(\textit{ibid}) with some modifications.
-The RBR metric is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author.
-In its original specification, the background dataset for RBR was constructed by keyword searches of PubMed.
-A potential weakness of this keyword based approach is that keywords do not effectively capture the field or the total output of an author even if multiple background samples are taken.
-Therefore, we created two new variants of the RBR; network RBR (nRBR) and document-based RBR (dRBR).
-nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total output of an author and use it as background.
-Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively.
-The details of how these metrics were calculated are provided in supplementary material \nameref{S1_File}.\\
-\vspace{2.5 mm}
-
-\section*{Results and Discussion} Scientific publications form the backbone of each of these five networks.
-The initial assumptions of appropriate citation and retrospective citation discovery (Introduction) suggest that network nodes that are common to multiple networks are likely to be influential.
-Accordingly.
-we explored the extent and nature of intersections across networks, we calculated intersection counts for all possible combinations of Alemtuzumab, Imatinib, Nelarabine, Ramucirumab, and Sunitinib (S1 Table 1).
-We also applied intersection analysis as above at a finer level of granularity by computing intersection counts for first generation citations (citing\_pmid) and second generation citations (cited\_sid).
-The results are displayed as Venn diagrams in Figures 1 and 2 respectively.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=0.15]{citing_pmid.png}
-\caption{{\bf Publications Common To First Generation References in Networks}
-Intersections were calculated across all five networks for citing\_pmids (the first generation of references) and displayed as a Venn diagram.
-No publications are common to all five networks.
-A single publication is cited in four of five networks.
-Abbreviations: alem (Alemtuzumab),imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
-\label{fig1}
-\end{figure}
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=0.15]{cited_sid.png}
-\caption{{\bf Publications Common To Second Generation References in Networks}
-Intersections were calculated across all five networks for cited\_sids (the second generation of references) and displayed as a Venn diagram.
-14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
-\label{fig2}
-\end{figure}
+\clearpage
 
@@
 \caption{{\bf Intersection of Five Networks: Second Generation Publications} Publications common to all networks at the second generation level (cited\_sid, Fig 2). } 
-\label{table4}
+\label{table3}
 \end{adjustwidth}
 \end{table}
-At the network level, 14 publications comprise the intersection of all five networks.
-Strikingly, not even one publication is common to all five networks at the first generation level although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies\cite{bibKohler}, is cited in four out of five networks.
-All 14 publications, the intersection of five networks, were in the second generation of citations and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references.
-We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4), analytical and structural biochemistry techniques (3) and cancer biology (2).
-Of these last two, one is a review of the p53 gene\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia\cite{bibFolkman}.
-Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the the general scientific literature \cite{bibVanNoorden}.
-As the subject of another study, we are actively working on a scalable strategy to characterize the entire dataset as well as all combinations of intersections.
+\clearpage
 
-Not restricted to  drug discovery and cures alone, the approach can be used to support efficient explorations of science history, an understanding of collaboration across domains, enrich portfolio analysis, planning and optimization, and enable communications of the societal value of research.
-While finer critical evaluation of the content of datasets is perhaps best left to experts, the methodology is broadly accessible and can be thought of as another tool for citizen science.
+\begin{figure}[!h]
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.95\linewidth]{citing_pmid.png}
+  %\caption{}
+  \label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.95\linewidth]{cited_sid.png}
+  %\caption{}
+  \label{fig:sub2}
+\end{subfigure}
+\caption{{\bf Intersecting Publications in Five Networks}  \emph{Left Panel.} Intersections were calculated across all five networks for citing\_pmids (the first generation of references) and displayed as a Venn diagram.
+No publications are common to all five networks.
+A single publication is cited in four of five networks.
+\emph{Right Panel.} Intersections were calculated across all five networks for cited\_sids (the second generation of references) and displayed as a Venn diagram.
+14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib)}
+\label{fig:test}
+\end{figure}
 
-\section*{Supporting Information}
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.1]{cy_core14_v2csv_6b.png}
+\caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic.
+Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5).
+14  publications are common to all five networks (Table 3) and are colored red.
+The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly.
+Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
+\label{fig3}
+\end{figure}
+\clearpage
 
-\paragraph*{S1 File.}
-\label{S1_File}
-{\bf Network Calculations} The basis of calculations for network metrics.
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=0.1]{proj_percent.png}
+\caption{{\bf NIH Research Support} Grant and contract support for publications from NIH in the five networks was identified using ExPORTER data (Materials and Methods).
+19,104 unique project numbers were identified of which 112 projects were common to all five networks.
+Projects were grouped by mechanism (i) P-  Research Program Projects and Centers (ii) R- Research Projects (iii) M-General Clinical Research Centers Programs (iv) N-Research and Development-Related Contracts (v) U-Cooperative Agreements (vi) T-Training Programs (vii) Z- Intramural Research.
+For each mechanism, the number of projects in the intersection of all five networks was plotted against the number in the union of all five networks (both expressed as percentages of their respective totals).
+A higher proportion of Research Program Projects and Centers awards is found in the intersection group.}
+\label{fig4}
+\end{figure}
+\clearpage
 
-\paragraph*{S2 Fig.}
-\label{S2_Fig}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Appendix.}
-\label{S1_Appendix}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Table.}
-\label{S1_Table}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\section*{Acknowledgments} We thank NETE for its support of the nascent Netelabs concept.
-
-\nolinenumbers
-
-\begin{thebibliography}{10}
-
-\bibitem{bibWilliams}
-Williams RS, Lotia S., Holloway AK, Pico AR.
-\newblock {{F}rom Scientific Discovery to Cures: Bright Stars within a Galaxy.}
-\newblock Cell. 2015 Sep; 163:21--23
-
-\bibitem{bibMaldame}
-Maldame, J.
-\newblock {{T}he Importance Of The History Of Science In Intellectual Formation}
-\newblock Scripta Varia 2002 104:237-248
-
-\bibitem{bibChan}
-O'Shea JJ, Kanno, Y., Chan AC.
-\newblock {{I}n Search of Magic Bullets: The Golden Age of Immunotherapeutics}
-\newblock Cell. 2014 Mar; 157:227-240
-
-\bibitem{bibLauer}
-Lauer MS.
-\newblock {{P}CSK9 Inhibitors: Lots of Work Done, Lots More to Do.}
-\newblock Ann Intern Med. 2016 Mar; 164(9):624-625.
-
-\bibitem{bibFDA}
-Federal Drug Administration.
-\newblock {{D}rugs@FDA: FDA Approved Drug Products}
-\newblock https://www.accessdata.fda.gov/scripts/cder/daf/
-
-\bibitem{bibNIHExPORTER}
-National Institutes of Health.
-\newblock {{N}IH ExPORTER}
-\newblock https://exporter.nih.gov/
-
-\bibitem{bibGooglePatents}
-Google Corporation
-\newblock {{G}oogle Patents}
-\newblock https://patents.google.com/
-
-\bibitem{bibKohler}
-K\"ohler, G., Milstein, C.
-\newblock { {C}ontinuous cultures of fused cells secreting antibody of predefined specificity.}
-\newblock Nature. 1975 256: 495-497
-
-\bibitem{bibLevine}
-Levine, AJ.
-\newblock {{p53}, the cellular gatekeeper for growth and division.}
-\newblock Cell. 1997 Feb 7;88(3):323-31.
-
-\bibitem{bibFolkman}
-Perez-Atayde AR, Sallan SE, Tedrow U, Connors S, Allred E, Folkman J.
-\newblock {{Spectrum} of tumor angiogenesis in the bone marrow of children with acute lymphoblastic leukemia}
-\newblock Am J Pathol. 1997 Mar;150(3):815-21.
-
-\bibitem{bibVanNoorden}
-Van Noorden R, Maher B, Nuzzo R.
-\newblock {{T}he top 100 papers}
-\newblock Nature 2014 514: 550?553
-
-\bibitem{bibn}
-Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
-\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
-infection through a transposon insertion followed by a {D}uplication}.
-\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
-\end{thebibliography}
 \end{document}

### 2017-06-08 Paper/plos-latex-template/plos_latex_template.tex
updates

@@
 
-% create \thickcline for thick horizontal lines of variable length
+% added by George
+%\usepackage{wrapfig}
+
+% create \thickline for thick horizontal lines of variable length
 \newlength\savedwidth
@@
 \noalign{\global\arrayrulewidth\savedwidth}}
+
+% WATERMARKS
+\usepackage{draftwatermark}
+\SetWatermarkText{Confidential}
+\SetWatermarkScale{4}
 
@@
 \\
-\textbf{3} Gladstone Institutes, University of California San Francisco, San Francisco, CA, USA
+\textbf{3} Gladstone Institutes, San Francisco, CA, USA
 \\
@@
 % Current address notes
-\textcurrency Current Address: Facebook Corporation, Menlo Park, CA, USA % change symbol to "\textcurrency a" if more than one current address note
+\textcurrency Current Address: Facebook Inc., Menlo Park, CA, USA % change symbol to "\textcurrency a" if more than one current address note
 % \textcurrency b Insert second current address 
@@
 
-Drug discovery and the subsequent availability of new breakthrough therapeutics or `cures' are compelling examples of societal benefit from advances in research.
-Such advances are invariably collaborative, involving the contributions of many scientists in a `cure network' where prior theory and experiment is built upon.
-To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble component events in the history of a cure and analyze them.
-This methodology is extensible beyond cure networks and its use supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
+Drug discovery and subsequent availability of a new breakthrough therapeutic or `cure' is a compelling example of societal benefit from research advances.
+These advances are invariably collaborative, involving the contributions of many scientists to a discovery network in which theory and experiment are built upon.
+To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic.
+This methodology is extensible beyond the history of a therapeutic and its use supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
 As a proof of principle, we have conducted a case study of five anti-cancer therapeutics.
-For the purpose of exploring the relationship across networks, we have built upon a technique for single networks and linked the work of approximately 250,000 authors in 100,000 scientific publications, we have enriched the content of networks for these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards.
+We have linked the work of over 220,000 authors in roughly 92,000 scientific publications that capture the research crucial for the development of these five therapeutics.
+We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards.
 Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as a core set of awards from the National Institutes of Health that supported this research.
-Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented by these networks.
+Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented in these networks.
 
@@
 
-Data mining of public data sources coupled with network analysis enables the assembly and quantitative description of research discoveries that were influential in the development of a breakthrough therapeutic or `cure'.
+Data mining of public data sources coupled with network analysis enables the quantitative description of research discoveries that were influential in the development of a breakthrough therapeutic or `cure'.
 The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents the progress of concepts from basic research to a cure is termed a `cure network' \cite {bibWilliams}.
 Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will uncover previous influential discovery (\textit{ibid}).
-Beyond using a digital methodology to assemble a set of facts about a major scientific advance, however, these studies also support a contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time\cite{bibMaldame}.
-Coupled with the knowledge that accrues from the clinical use of the drug, knowledge of a drug development network also enables a recursive learning of the pathogenesis of the disease it is being used to treat as as been noted for the burgeoning field of immunotherapeutics\cite{bibChan}.
+Beyond using a digital methodology to assemble a set of facts about a major scientific advance, a deeper contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time\cite{bibMaldame} is enabled.
+Such studies (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases \cite {bibLauer} (ii) support strategic communications to oversight bodies, and (iii) help communicate the societal value of research.
+Importantly too, when coupled with information that accrues from clinical use of a drug, knowledge of its development network enables a recursive uncovering of the pathogenesis of the disease it is being used to treat as noted for the burgeoning field of immunotherapeutics\cite{bibChan}.
 
-Such studies (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases (ii) support strategic communications to oversight bodies, and (iii) help communicate the societal value of research\cite {bibLauer}.
 Williams and colleagues have elegantly demonstrated the feasibility and value of data mining and network analysis using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}).
-These authors observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-related research over a period greater than 100 years.
+They observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-related research over a period greater than 100 years.
+These authors also suggest that thoughtful metrics derived from this concept could inform decision making by funders.
 
-Extending this methodology to study additional cures and significant research advances in general is a logical next step.
-Ascertaining the nature of the interactions, if any, between networks, is also of considerable interest since it would support an understanding of collaboration across networks as well as common features of science networks.
-Lastly, scaling from case studies to mapping the entire domain of drug development may be beneficial in future resource allocation and optimization of drug development activities.
+Extending the methodology to study additional cures and significant research advances is a logical next step.
+Ascertaining the nature of the interactions, if any, between networks, is also of considerable interest since it supports an understanding of collaboration across networks as well as common features of science networks.
+Lastly, even if ambitious, scaling from case studies to mapping the entire domain of drug development is likely to be beneficial in planning, resource allocation and optimization of drug development activities.
 
-To address these questions, we have enhanced prior art to (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extended single network analysis to map publications and authors across multiple networks (v) refactored the network analysis code of Williams et al.
-for better performance.
-To evaluate these extensions, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer.
+To address these questions, we have built upon prior art for single networks to (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extended single network analysis to map publications and authors across multiple networks.
+For evaluation, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer.
 We present the results of this case study as a body of work for interrogation and improvement by other researchers, and a step towards mapping the universe of FDA-approved drugs and biologicals.
@@
 \section*{Materials and Methods}  A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration was selected for this study (Table 1).
-Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab are humanized antibodies that target cell surface receptors.
+Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab (Campath) are humanized antibodies that target the CD52 and vEGFR-2 cell surface receptors respectively.
 For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.\cite{bibWilliams} but with specific modifications detailed below.
@@
 For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (below).
+\textbf{[Insert Table 1]}
 
-\begin{table}[!ht]
-%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\scalebox{0.9}{
-\begin{tabular}{|l+l|l|l|l|l|l|l|}
-\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
-Therapeutic & FDA Approval Date & Unique Identifier & US Patent & Publication Date  \\ \hline
-$Alemtuzumab$ & May 2001 & BLA: 103948 & US5846534 & Dec 1998\\ \hline
-$Imatinib$ & May 2001 & NDA: 021335 & US5521184 &  May 1996 \\ \hline
-$Nelarabine$ & Oct 2005 & NDA: 021877 & US5424295 & Jun 1995  \\ \hline
-$Ramucirumab$ & Apr 2014 & BLA: 125477 & US7498414 & Mar 2009  \\ \hline
-$Sunitinib$ & Jan 2006  & NDA: 021938  & US6573293 & Jun 2003 \\ \hline
-\end{tabular}}
-\vspace{2 mm}
-\caption{
-{\bf Case Studies of Five Anti-Cancer Agents} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies.
-The active ingredient for each of these five therapeutics is listed in column 1.
-While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic.
-The publication date for each patent is listed in the last column.}
-%\begin{flushleft}  
-%\end{flushleft}
-\label{table1}
-%\end{adjustwidth}
-\end{table}
-
-\textbf{Clinical trials} The national clinical trials database (clinicaltrials.gov) was searched for clinical trials of the five therapeutics that completed on or the data of FDA approval.
+\textbf{Clinical trials} The national clinical trials database (clinicaltrials.gov) was searched for clinical trials of the five therapeutics that completed by the data of FDA approval.
 Both cited references and publications from these clinical trials were collected if they were published within the approval date plus two months.
@@
 \textbf{FDA documents} The drugs@fda website\cite{bibFDA} was searched for each of the five therapeutics and cited references in the medical review document were manually extracted and matched to pmids.
-FDA Approval Summaries, articles published in journals by FDA staff, were available for all five therapeutics and contain cited references.
-If the published date of a citation exceeded the approval date plus two months, the publication was not included.
+FDA Approval Summaries published in journals by FDA staff, were available for all five therapeutics and contain cited references.
+If the published date of a citated reference exceeded the approval date plus two months, the publication was not included.
 
@@
 Citing\_pmids from the five different sources above  were combined and deduplicated.
-Using the Scopus database and its APIs, these citing\_pmids were mapped to Scopus identifiers (citing\_sid) from which a second generation of cited references (cited\_sid) was extracted., These cited\_sids, were in turn, mapped back to pmids (cited\_pmid).
-Whereas mapping between PubMed and Scopus identifiers at the citing\_pmid and citing\_sid stage resulted in 1\% or less information loss, mapping at the cited\_sid to cited\_pmid resulted in 15-20 \% information loss.
+Using the Scopus database and its APIs, these citing\_pmids were mapped to Scopus identifiers (citing\_sid) from which a second generation of cited references (cited\_sid) was extracted.
+These cited\_sids, were in turn, mapped back to pmids (cited\_pmid).
+Whereas mapping between PubMed and Scopus identifiers at the citing\_pmid and citing\_sid stage resulted in 1\% or less information loss, mapping at the cited\_sid to cited\_pmid resulted in a loss of roughly 15-20 \% of target records.
 Accordingly the Scopus data  was used as the backbone of the publication component of the network and the cited\_pmid information was treated as an annotation layer.
-These observations are summarized in Table 2 and include the count of null values when mapping from citing\_sid to cited\_sid.
+These observations are summarized in Table 2.
+\textbf{[Insert Table 2]}
 
-\begin{table}[!ht]
-%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\scalebox{0.9}{
-\begin{tabular}{|l+l|l|l|l|l|l|l|}
-\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
-Therapeutic & citing\_pmid count & citing\_sid count & cited\_sid count  & cited\_pmid count  \\ \hline
-$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
-$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
-$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
-$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
-$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
-\end{tabular}
-}
-\vspace{2.5 mm}
-\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies.
-A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature (Materials and Methods).
-Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve cited publications (cited\_sid).
-Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field}
-\label{table2}
-%\end{adjustwidth}
-\end{table}
-
-Both citing and cited pmids were mapped to NIH grants and peer review panels (study sections) using information made publicly available by NIH through NIH ExPORTER\cite{bibNIHExPORTER}.
-The Center for Scientific Review at NIH organizes the review of the majority of grant applications submitted to the NIH and has over 170 chartered study sections with defined scientific interests and relatively stable reviewer membership.
+Both citing and cited pmids were mapped to NIH grants and peer review panels (study sections) using public information available through NIH ExPORTER\cite{bibNIHExPORTER}.
 Thus, we enriched our network data by identifying those study sections associated with the awards that supported publications in our networks.
 
-The resultant data were modeled as hierarchical networks and analyzed using metrics based on network topology.
-We calculated the propagated in-degree rank (PIR) metric of Williams \cite {bibWilliams}.
+The resultant data were modeled as networks and analyzed using metrics based on network topology.
+We calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams \cite {bibWilliams}.
 PIR represents the sum of weighted citation scores for all articles in a network that can be attributed to an author.
-In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a globalPIR score, which was normalized to the sum of PIR scores within each network.
-Secondly, we calculated the RBR metric of Williams et al.
-(\textit{ibid}) with some modifications.
-The RBR metric is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author.
+In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a networkPIR (nPIR) score, which was also normalized to the sum of individual PIR scores within each network as the PIRpartitionRatio (PPR) as a way to measure inter-network influence.
+RBR is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author.
 In its original specification, the background dataset for RBR was constructed by keyword searches of PubMed.
 A potential weakness of this keyword based approach is that keywords do not effectively capture the field or the total output of an author even if multiple background samples are taken.
-Therefore, we created two new variants of the RBR; network RBR (nRBR) and document-based RBR (dRBR).
-nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total output of an author and use it as background.
+Therefore, we created two new variants of the RBR; network RBR (nRBR) and global-based RBR (gRBR).
+nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total article output of an author as background.
 Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively.
 The details of how these metrics were calculated are provided in supplementary material \nameref{S1_File}.\\
-\vspace{2.5 mm}
 
-\section*{Results and Discussion} Scientific publications form the backbone of each of these five networks.
-The initial assumptions of appropriate citation and retrospective citation discovery (Introduction) suggest that network nodes that are common to multiple networks are likely to be influential.
-Accordingly.
-we explored the extent and nature of intersections across networks, we calculated intersection counts for all possible combinations of Alemtuzumab, Imatinib, Nelarabine, Ramucirumab, and Sunitinib (S1 Table 1).
-We also applied intersection analysis as above at a finer level of granularity by computing intersection counts for first generation citations (citing\_pmid) and second generation citations (cited\_sid).
-The results are displayed as Venn diagrams in Figures 1 and 2 respectively.
+\textbf{Analysis}.
+All data used in this study were acquired exclusively from the sources listed above.
+Computations were performed on infrastructure owned or leased by NET ESolutions, Elsevier , or the Gladstone Institutes.
+Code and scripts used in this study were written in Java, Python, SQL, and R and are archived on a publicly accessible Github repository\cite{bibGithub}.
+Network visualization was performed using Cytoscape\cite{bibCytoscape}.
+\section*{Results and Discussion}
 
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=0.15]{citing_pmid.png}
-\caption{{\bf Publications Common To First Generation References in Networks}
-Intersections were calculated across all five networks for citing\_pmids (the first generation of references) and displayed as a Venn diagram.
-No publications are common to all five networks.
-A single publication is cited in four of five networks.
-Abbreviations: alem (Alemtuzumab),imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
-\label{fig1}
-\end{figure}
+\subsection*{Publications} Scientific publications form the backbone of each of these five networks.
+Our initial assumptions of appropriate citation and retrospective citation discovery (Introduction) suggest that network nodes that are common to multiple networks are likely to be influential.
+We calculated intersection counts for all possible combinations of publications in the Alemtuzumab, Imatinib, Nelarabine, Ramucirumab, and Sunitinib networks (S1 Table 1).
+We also applied intersection analysis at a finer level of granularity by computing intersection counts for both first generation citations (citing\_pmid) and second generation citations (cited\_sid).
+The results are displayed as Venn diagrams in Figure 1.
+\textbf{[Insert Fig.
+1]}
 
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=0.15]{cited_sid.png}
-\caption{{\bf Publications Common To Second Generation References in Networks}
-Intersections were calculated across all five networks for cited\_sids (the second generation of references) and displayed as a Venn diagram.
-14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
-\label{fig2}
-\end{figure}
-
-\begin{table}[!ht]
-\begin{adjustwidth}{-1.0in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
-\scalebox{0.8}{\begin{tabular}{|l+l|l|l|l|l|l|l|}
-\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
-\hline
-SourceYear & SourceName & Author(s) \\ 
-  \hline
-1958 & J. Am. Stat. Assoc. & Kaplan E.R., Meier P. \\ 
-1963 & Science & Jerne, N. K. and Nordin, A. A.  \\ 
-1972 & J R Stat Soc & Cox DR.  \\ 
-1976 & Anal. Biochem. & Bradford MM \\ 
-1977 & Br J Cancer & R. Peto, M.C. Pike, and P. Armitage  \\ 
-1977 & Proc. Natl. Acad. Sci. & Sanger, F., S. Nicklen, and A.R. Coulson.  \\ 
-1983 & J Immunol Methods & Mosmann T  \\ 
-1984 & Adv Enzyme Regul & T.C. Chou, and P. Talalay  \\ 
-1989 & Molecular Cloning: A Laboratory Manual & Sambrook, J., Fritsch, E. and Maniatis, T.  \\ 
-1994 & Acta Crystallogr D & Collaborative Computational Project 4 \\ 
-1994 & Acta Crystallogr. A & Navaza J.  \\ 
-1997 & Cell & Levine, A. J. \\ 
-1997 & Am. J. Pathol. & Perez-Atayde, A. R., Sallan, S. E., Tedrow, U., Connors, S., Allred, E., and Folkman, J.  \\ 
-1998 & CA: A Cancer Journal for Clinicians & SH Landis T Murray S Bolden PA Wingo \\ 
-\hline
-\end{tabular}}
-\vspace{2.5 mm}
-\caption{{\bf Intersection of Five Networks: Second Generation Publications} Publications common to all networks at the second generation level (cited\_sid, Fig 2). } 
-\label{table4}
-\end{adjustwidth}
-\end{table}
-At the network level, 14 publications comprise the intersection of all five networks.
-Strikingly, not even one publication is common to all five networks at the first generation level although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies\cite{bibKohler}, is cited in four out of five networks.
-All 14 publications, the intersection of five networks, were in the second generation of citations and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references.
-We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4 publications), analytical and structural biochemistry techniques (3 publications) and cancer biology (2 publications).
+The intersection of all five networks consists of 14 publications out of a total of 91,991 unique Scopus identifiers.
+Strikingly, not even a single publication is common to all five networks at the first generation level (citing\_sid) although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies\cite{bibKohler}, is cited in four out of five networks.
+All 14 publications are in the second generation of citations (cited\_sid) and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references.
+We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4 publications), analytical and structural biology techniques (3 publications) and cancer biology (2 publications).
 Of these last two, one is a review of the p53 gene\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia\cite{bibFolkman}.
-Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the the general scientific literature \cite{bibVanNoorden}.
+Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the general scientific literature \cite{bibVanNoorden}.
+The relationship between core publications and their therapeutic networks is visualized in Fig 3.
+\textbf{[Insert Fig.
+2]}.
 As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks.
 
-With its annual budget of approximately US\$32 billion, NIH is a major funder of biomedical research.
+\subsection*{Grant Support} With its annual budget of approximately US\$32 billion, NIH is a major funder of biomedical research through its granting program.
+Understanding the nature and extent of NIH grant support for the research represented in our five networks, provides insight into the funding programs that enabled this research.
 We took advantage of publicly available data\cite{bibNIHExPORTER} to identify grant support for the publications in our five networks by mapping them to pmids.
 A total 19,104 unique grant numbers was harvested of which 112 were found in all five networks.
+At the intersection of five networks, the reason the number of grants is larger than the number of publications is because publications and grants exist in a `many to many' relationship in that each publication can acknowledge support from multiple grants and each grant can support multiple publications.
 These awards were grouped by major type  and visualized (Fig 3.).
-Of note, Research Program Projects and Center grants is proportionately larger in the intersection group when compared to the total population where the proportion of research projects is larger.
-We speculate that the broader and collaborative nature of such awards may be more likely to result in a methods-rich population of publications than the more focused research project kind of award but further and more rigorous study is needed to elucidate this question.
-The two populations of publications and grants exist in a `many to many' relationship in that each publication can acknowledge support from multiple grants and each grant can support multiple publications.
-Further, a significant loss of information when mapping from cited\_sid to cited\_pmid.
-Thus we believe that these numbers could be an underestimate of actual grant support that needs to be interpreted in the context of the false-positive and false-negative content of the publicly available data.
+Of note, support from Research Program Projects and Center grants is proportionately larger in the intersection group when compared to the total population where the proportion of research projects is larger.
+A significant loss of information occurs when mapping from cited\_sid to cited\_pmid (Table 2).
+Thus we believe that these numbers are an underestimate of actual grant support from NIH.
+Also missing from this analysis, however, are details of research support from other funding agencies and industry, which are questions that we intend to pursue.
+Even so, these data testify to a recurring theme of collaboration and breadth of community engagement that is also seen at the publication level.
+We speculate that the broader and collaborative nature of such awards may be more likely to result in a methods-rich population of publications than the more focused research project award but elucidation will require further and more rigorous study.
 
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=0.15]{proj_percent.png}
-\caption{{\bf NIH Research Support} Grant and contract support for publications from NIH in the five networks was identified using ExPORTER data (Materials and Methods).
-19,104 unique project numbers were identified of which 112 projects were common to all five networks.
-Projects were grouped by mechanism (i) P-  Research Program Projects and Centers (ii) R- Research Projects (iii) M-General Clinical Research Centers Programs (iv) N-Research and Development-Related Contracts (v) U-Cooperative Agreements (vi) T-Training Programs (vii) Z- Intramural Research.
-For each mechanism, the number of projects in the intersection of all five networks was plotted against the number in the union of all five networks (both expressed as percentages of their respective totals).
-A higher proportion of Research Program Projects and Centers awards is found in the intersection group.}
-\label{fig3}
-\end{figure}
-
-Not restricted to  drug discovery and cures alone, our approach offers burden-reduction in explorations of science history, contributes to the understanding of collaboration across domains, enriches portfolio analysis, planning and optimization, and enables communications of the societal value of research.
-While finer critical evaluation of the content of datasets generated through this approach is perhaps best left to experts, the methodology is broadly accessible and can be viewed as another tool for citizen science.
-
-Research support from NIH is typically made through a two stage peer-review process.
-The Center for Scientific Review at NIH reviews between 50,000-60,000 grant applications each year\cite{bibBoyack}, a process involving more than 15,000 expert reviewers and individual Institutes and Centers manage smaller scale peer review operations.
-Thus, another layer of collaborative scientific activity preceded the awards that supported research that in turn resulted in the scientific output captured in these five networks.
+\subsection*{Peer Review} Research support from NIH is typically made through a two stage peer-review process.
+The Center for Scientific Review at NIH manages first-stage scientific review of between 50,000-60,000 grant applications each year\cite{bibBoyack}, a process involving more than 15,000 expert reviewers.
+In addition, individual Institutes and Centers at NIH manage smaller scale peer review operations.
+Assuming an overall success rate of 20\%, peer review plays the role of a collaborative scientific activity and that serves as a selection layer strongly influencing granting outcomes.
 To describe this layer at a high-level, we matched the awards in the the five networks to the peer review panels (study sections) that evaluated them for scientific merit and calculated the intersection and union of these peer review panels.
@@
 Of these, 11 are distinguishable as Special Emphasis Panels that could be either one-time or recurring panels with temporary members, the remaining 77 are chartered panels with relatively stable membership.
-Some of these panels no longer exist and public records are not easily available to determine their scientific focus.
-For the X that could be classified (Supplemental), it is evident that they represent a rich mix of basic sciences such as chemistry, biophysics, cell biology, clinical sciences such as pathology, radiology, endocrinology.
+Some of these panels are no longer active and public records are not easily available to determine their scientific focus.
+For the 74 panels that could be classified (Supplemental), beyond an obvious focus on cancer, it is evident that the panels represent a rich mix of disciplines such as chemistry, biophysics, genetics, cell biology, and molecular biology; as well as AIDS, pathology, radiology, endocrinology, neurology, mental health, and child health.
 Four hundred and seven unique panel identifiers formed the union of all five networks.
@@
 These data provide evidence of broad input from invited experts in a collaborative activity that selects promising scientific projects.
-Assuming an average of 25 reviewers per panel (the number is likely to range from 5-40) and not considering that some of these panels are likely to have met met multiple times during the lifespan of the awards in question, a minimum of 10,000 experts comprised this additional layer of scientific regulation.
+Assuming an average of 25 reviewers per panel (the number is likely to range from 5-40) and excluding that some of these panels are likely to have met multiple times during the lifespan of the awards in question and that some of these applications for funding may have been reviewed multiple times, a minimum of 10,000 experts comprised this additional layer of scientific influence.
 We believe that the actual number is likely to be at least double.
+A more accurate estimate would be possible if historical records of participation in peer review were made publicly available by NIH.
+We do not have records of awards or peer review from sources other than NIH and this also is a focus of future investigation.
+
+\subsection*{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information).
+The nPIR metric describes the sum of weighted citation scores for all articles that a researcher has in all five networks.
+When combined with the PIRpartitionRatio (PPR), insight into cross-network influence is generated.
+A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied.
+Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would attenuate this limitation\cite{bibKinch} but this goal is unlikely to be achieved in the very short term and other data quality issues are likely to emerge.
+
+While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher.
+We found several instances in the top 10\% of PIR scores where the gRBR was significantly inaccurate (data not shown).
+This metric is therefore likely to be useful when the author disambiguation problem and article capture is resolved to the point where data quality is significantly improved and is not recommended except when strong confidence exists in the total productivity counts.
+In general, these metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (Supplemental Data).
+These `bright stars in neighboring constellations', represent elite performers in network(s) of clinical and basic science expertise again reinforcing the concept of collaborative translational achievements built upon a body of basic science.
+Beyond simple weighting and normalization that we have used, a variety of citation metrics such as SNIP\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study\cite{bibIoannidis}.
+
+In summary, we have developed and demonstrated a methodology not restricted to  drug discovery and cures alone, that offers burden-reduction in explorations of science history.
+It contributes to the understanding of collaboration across domains and can be used to  enrich portfolio analysis, planning and optimization, as well as communications of the societal value of research.
+The approach can be easily adapted to study the collaborative history within and across research portfolios of groups of researchers and targeted programs such as the Clinical and Translational Science Award (CTSA) Program.
+While finer critical evaluation of the content of datasets generated through this approach is best left to experts, the methodology is broadly accessible and can also be viewed as another tool for citizen science.
+Overall, no single metric will provide useful answers, instead expert interpretation of multiple metrics best matched to curated datasets is likely to yield greater value.
 
@@
 
-\paragraph*{S1 Appendix.}
-\label{S1_Appendix}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Table.}
+\paragraph*{S3 Table.}
 \label{S1_Table}
@@
 
-\section*{Acknowledgments} %We thank Sandeep Somaiya for his support of of the nascent Netelabs concept. We thank Tandy Warnow, and Andy Chan for helpful suggestions.
+\section*{Acknowledgments} %We thank Sandeep Somaiya for his support of of the nascent Netelabs concept.
 
@@
 \bibitem{bibWilliams}
-Williams RS, Lotia S., Holloway AK, Pico AR.
+Williams RS, Lotia S, Holloway AK, Pico AR.
 \newblock {{F}rom Scientific Discovery to Cures: Bright Stars within a Galaxy.}
@@
 Maldame, J.
-\newblock {{T}he Importance Of The History Of Science In Intellectual Formation}
+\newblock {{T}he Importance Of The History Of Science In Intellectual Formation.}
 \newblock Scripta Varia 2002 104:237-248
@@
 O'Shea JJ, Kanno, Y., Chan AC.
-\newblock {{I}n Search of Magic Bullets: The Golden Age of Immunotherapeutics}
+\newblock {{I}n Search of Magic Bullets: The Golden Age of Immunotherapeutics.}
 \newblock Cell. 2014 Mar; 157:227-240
@@
 Lauer MS.
-\newblock {{P}CSK9 Inhibitors: Lots of Work Done, Lots More to Do}
+\newblock {{P}CSK9 Inhibitors: Lots of Work Done, Lots More to Do.}
 \newblock Ann Intern Med. 2016 Mar; 164(9):624-625.
@@
 Federal Drug Administration.
-\newblock {{D}rugs@FDA: FDA Approved Drug Products}
+\newblock {{D}rugs@FDA: FDA Approved Drug Products.}
 \newblock https://www.accessdata.fda.gov/scripts/cder/daf/
@@
 \bibitem{bibGooglePatents}
-Google Corporation
+Google Inc.
 \newblock {{G}oogle Patents}
@@
 \newblock https://exporter.nih.gov/
+
+\bibitem{bibGithub}
+\newblock {{N}ET ESolution, Netelabs Repository}
+\newblock https://github.com/NETESOLUTIONS/NETELabs
+
+\bibitem{bibCytoscape}
+Shannon P, Markiel A, Ozier O, Baliga N, Wang JT, Ramage D, et al.
+\newblock {{C}ytoscape: a software environment for integrated models of biomolecular interaction networks.}
+\newblock Genome Res. 2003 Nov;13(11):2498-504
 
@@
 \newblock {{T}he top 100 papers}
-\newblock Nature 2014 514: 550-553
+\newblock Nature. 2014 514: 550-553
 
@@
 \newblock {{C}haracterization of the Peer Review Network at the Center for Scientific Review, National Institutes of Health}
-\newblock  PLoS One 2014 /10.1371/journal.pone.0104244
+\newblock  PLoS One. 2014 10.1371/journal.pone.0104244
 
-\bibitem{bibn}
-Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
-\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
-infection through a transposon insertion followed by a {D}uplication}.
-\newblock PLoS Gene 2011 Oct;7(10):e1002337.
+\bibitem{bibKinch}
+Kinch MS, Haynesworth A, Kinch SL, Hoyer D.
+\newblock {{A}n overview of FDA-approved new molecular entities: 1827-2013}
+\newblock  Drug Discov Today. 2014 Aug; 19(8):1033-9 doi: 10.1016/j.drudis.2014.03.018.
+
+\bibitem{bibWaltman}
+Waltman L, van Eck NJ, van Leeuwen TN, Visser, MS.
+\newblock {{S}ome modifications to the SNIP journal impact indicator.}
+\newblock  J Informetrics. 2013.7(2), 272-285.
+
+\bibitem{bibIoannidis}
+Ioannidis JPA, Boyack K, Wouters PF.
+\newblock {{C}itation Metrics: A Primer on How (Not) to Normalize.}
+\newblock  PLoS Biology. 2016. 10.1371/journal.pbio.1002542
+
 \end{thebibliography}

### 2017-06-08 five_pack_stageI_assembly.R
updating

@@ -1,6 +1,7 @@
 # five_pack Stage I Assembly
 setwd("~/Desktop")
 rm(list=ls())
+library(dplyr)
 alem <- read.csv("~/NETELabs_CaseStudies/assembly/alemtuzumab_assembly/alem_eric_stage1.csv",stringsAsFactors=FALSE)
 imat <- read.csv("~/NETELabs_CaseStudies/assembly/imatinib_assembly/imat_eric_stage1.csv",stringsAsFactors=FALSE)
 nela <- read.csv("~/NETELabs_CaseStudies/assembly/nelarabine_assembly/nela_eric_stage1.csv",stringsAsFactors=FALSE)

### 2017-06-08 Bright_Stars/Java/CNI/DataLoader.java
Add files via upload

@@ -1,0 +1,765 @@
+
+/* Author : Samet Keserci
+ * Create Date: 2017-05-08
+ * 
+ * */
+
+import java.io.BufferedReader;
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.math.BigInteger;
+import java.nio.charset.StandardCharsets;
+import java.security.MessageDigest;
+import java.security.NoSuchAlgorithmException;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.Collections;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.Iterator;
+import java.util.List;
+import java.util.Set;
+import java.util.TreeMap;
+import java.util.TreeSet;
+
+import sun.security.provider.MD5;
+import sun.security.rsa.RSASignature.MD5withRSA;
+
+/*
+'ar': 'Article',
+'ip': 'Article in Press',
+'ab': 'Abstract Report',
+'bk': 'Book',
+'ch': 'Book Chapter',
+'bz': 'Business Article',
+'cp': 'Conference Paper',
+'cr': 'Conference Review',
+'ed': 'Editorial',
+'er': 'Erratum',
+'le': 'Letter',
+'no': 'Note',
+'pr': 'Press Release',
+'rp': 'Report',
+'re': 'Review',
+'sh': 'Short Survey'
+*/
+
+public class DataLoader {
+
+	static String home = System.getProperty("user.home");
+	static String work_dir = home + "/labdata1/NETELabs_CaseStudies/Network/";
+	static String input_dir = home + "/labdata1/NETELabs_CaseStudies/Network/input/";
+	static String mid_output_dir = home + "/labdata1/NETELabs_CaseStudies/Network/final_output/";
+	static String final_output_dir = home + "/labdata1/NETELabs_CaseStudies/Network/output/";
+
+	public HashMap<String, HashSet<String>> pub_citingPubSET(String drug_name, String input_dir, String output_dir)
+			throws IOException {
+
+		String drug_name_pub = drug_name + "_pubref.tsv";
+		String drug_name_auth = drug_name + "_authref.tsv";
+
+		HashMap<String, HashSet<String>> out = new HashMap<String, HashSet<String>>();
+
+		FileReader fReader = new FileReader(input_dir + drug_name_pub);
+		BufferedReader bReader = new BufferedReader(fReader);
+
[…]

### 2017-06-08 Bright_Stars/Java/CNI/Main.java

@@ -1,0 +1,156 @@
+
+/* Author : Samet Keserci
+ * Create Date: 2017-05-08
+ * 
+ * */
+
+
+import java.io.BufferedReader;
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.security.NoSuchAlgorithmException;
+import java.util.HashMap;
+
+import org.jgrapht.*;
+
+public class Main {
+
+	static String home = System.getProperty("user.home");
+	static String work_dir = home + "/labdata1/NETELabs_CaseStudies/Network/";
+	static String input_dir = home + "/labdata1/NETELabs_CaseStudies/Network/input/";
+	static String mid_output_dir = home + "/labdata1/NETELabs_CaseStudies/Network/intermediate_output/";
+	static String final_output_dir = home + "/labdata1/NETELabs_CaseStudies/Network/final_output/";
+	
+	
+	public void combiner(String global, String[] drug_list, String input_dir, String output_dir) throws IOException, NoSuchAlgorithmException {
+	
+		
+		
+		DataLoader loader = new DataLoader();
+		//HashMap<String,String> authSet = loader.AuthSet(global, input_dir, output_dir);
+		
+		HashMap<String,String> map_pir = new HashMap<String,String>();
+		HashMap<String,String> map_nrbr = new HashMap<String,String>();
+		HashMap<String,String> map_grbr = new HashMap<String,String>();
+
+		
+		FileReader fReader_pir = new FileReader(input_dir+"all_PIR.csv");
+		FileReader fReader_nrbr = new FileReader(input_dir+"all_nRBR.csv"); 
+		FileReader fReader_grbr = new FileReader(input_dir+"all_gRBR.csv"); 
+
+
+		BufferedReader bReader_pir = new BufferedReader(fReader_pir);
+		BufferedReader bReader_nrbr =  new BufferedReader(fReader_nrbr);
+		BufferedReader bReader_grbr = new BufferedReader(fReader_grbr);
+
+		
+		
+		String header_pir = bReader_pir.readLine();
+		String header_nrbr = bReader_nrbr.readLine(); 
+		String header_grbr = bReader_grbr.readLine();
+
+		
+		String header = header_pir +","+ header_nrbr.split(",",3)[2]+","+header_grbr.split(",",3)[2];
+		
[…]

### 2017-06-08 Bright_Stars/Java/CNI/Visualisation_data.java

@@ -1,0 +1,174 @@
+import java.io.BufferedReader;
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.util.HashMap;
+import java.util.HashSet;
+
+/* Author : Samet Keserci
+ * Create Date: 2017-05-08
+ * 
+ * */
+public class Visualisation_data {
+	
+	
+	static String home = System.getProperty("user.home");
+	static String work_dir = home + "/labdata1/NETELabs_CaseStudies/Network/";
+	static String input_dir = home + "/labdata1/NETELabs_CaseStudies/Network/input/";
+	static String mid_output_dir = home + "/labdata1/NETELabs_CaseStudies/Network/intermediate_output/";
+	static String final_output_dir = home + "/labdata1/NETELabs_CaseStudies/Network/final_output/";
+
+	
+	
+	public void topNpublication(int N, String global, String[] drugList, String input_dir, String out_dir){
+		
+		
+	}
+	
+	public void topNAuthor(int N, String global, String[] drugList, String input_dir, String out_dir){
+		
+		
+	}
+	
+	
+    public void CoauthorAuthorTopNpub(int N, String global, String[] drugList, String input_dir, String out_dir){
+		
+		
+	}
+    
+    
+    public HashMap<String,Integer> CorePublicationsList(int N, String global, String[] drugList, String input_dir, String out_dir){
+		
+    	HashMap<String,Integer> out = new HashMap<String,Integer>();
+    	
+		return out;
+	}
+    
+    
+    public HashMap<String,Integer> CoreAuthorsList(int N, String global, String[] drugList, String input_dir, String out_dir){
+		
+    	HashMap<String,Integer> out = new HashMap<String,Integer>();
+    	
+		return out;
+		
+	}
+    
+    
+    public  HashMap<String,HashSet<String>> CorePubNetwork(int N, String global, String[] drugList, String input_dir, String out_dir){
+		
+    	HashMap<String,HashSet<String>> out = new HashMap<String,HashSet<String>>();
+    	
+    	return out;
+		
+	}
+	
+    public  HashMap<String,HashSet<String>> CoreAuthorNetwork(int N, String global, String[] drugList, String input_dir, String out_dir){
+		
[…]

### 2017-06-08 Bright_Stars/R/ExPORTER_Project_Data.R
all R scripts for the Bright Stars study

@@ -1,0 +1,22 @@
+# load exporter projects files into a list
+rm(list = ls())
+# Read in ExPorter Project Data from downloaded csvs and pass the resultant  
+# data frame to darlin (NETE Labs Server)
+
+setwd("~/Desktop/ExPORTER/xCleaned")
+temp <- list.files(pattern = "*.csv")
+exp_projects <- list()
+for (i in 1:length(temp)) {
+	t <- read.csv(temp[i], stringsAsFactors = FALSE, header = TRUE)
+	t <- data.frame(t$APPLICATION_ID, t$ACTIVITY, t$ADMINISTERING_IC, t$APPLICATION_TYPE, t$CORE_PROJECT_NUM, 
+		t$FOA_NUMBER, t$FULL_PROJECT_NUM, t$STUDY_SECTION, t$STUDY_SECTION_NAME,stringsAsFactors=FALSE)
+	print(temp[i])
+	print(ncol(t))
+	print(colnames(t))
+	exp_projects[[i]] <- t
+}
+names(exp_projects) <- temp
+exp_projects_df <- do.call("rbind", exp_projects)
+colnames(exp_projects_df) <- casefold(colnames(exp_projects_df))
+colnames(exp_projects_df) <- substring(colnames(exp_projects_df),3)
+write.csv(exp_projects_df,file="exp_projects_df.csv",row.names=FALSE)

### 2017-06-08 Bright_Stars/R/NA_Counts.R

@@ -1,0 +1,25 @@
+# Counting NAs for cited_sids
+rm(list=ls())
+setwd("~/NETELabs_CaseStudies/assembly/interim_results")
+alem_pubref <- read.csv("alem_pubref.csv",stringsAsFactors=FALSE)
+imat_pubref <- read.csv("imat_pubref.csv",stringsAsFactors=FALSE)
+nela_pubref <- read.csv("nela_pubref.csv",stringsAsFactors=FALSE)
+ramu_pubref <- read.csv("ramu_pubref.csv",stringsAsFactors=FALSE)
+suni_pubref <- read.csv("suni_pubref.csv",stringsAsFactors=FALSE)
+setwd("~/NETELabs_CaseStudies/assembly/final_results")
+
+
+alem_cited_NA <- round(100*(sum(is.na(alem_pubref$cited_sid))/length(alem_pubref$cited_sid)),0)
+
+print(alem_cited_NA)
+imat_cited_NA <- round(100*(sum(is.na(imat_pubref$cited_sid))/length(imat_pubref$cited_sid)),0)
+print(imat_cited_NA)
+
+nela_cited_NA <- round(100*(sum(is.na(nela_pubref$cited_sid))/length(nela_pubref$cited_sid)),0)
+
+print(nela_cited_NA)
+ramu_cited_NA <- round(100*(sum(is.na(ramu_pubref$cited_sid))/length(ramu_pubref$cited_sid)),0)
+print(ramu_cited_NA)
+
+suni_cited_NA <- round(100*(sum(is.na(suni_pubref$cited_sid))/length(suni_pubref$cited_sid)),0)
+print(suni_cited_NA)

### 2017-06-08 Bright_Stars/R/SupExTest.R

@@ -1,0 +1,16 @@
+setwd("~/NETELabs_CaseStudies/assembly/interim_results/")
+t_alem <- read.csv("alem_pubref.csv",stringsAsFactors=FALSE)
+t_imat <- read.csv("imat_pubref.csv",stringsAsFactors=FALSE)
+t_nela <- read.csv("nela_pubref.csv",stringsAsFactors=FALSE)
+t_ramu <- read.csv("ramu_pubref.csv",stringsAsFactors=FALSE)
+t_suni <- read.csv("suni_pubref.csv",stringsAsFactors=FALSE)
+t_list <- list()
+t_list[[1]] <- unique(union(t_alem$cited_pmid,t_alem$cited_pmid))
+t_list[[2]] <- unique(union(t_imat$cited_pmid,t_imat$citing_pmid))
+t_list[[3]] <- unique(union(t_nela$cited_pmid,t_nela$citing_pmid))
+t_list[[4]] <- unique(union(t_ramu$cited_pmid,t_ramu$citing_pmid))
+t_list[[5]] <- unique(union(t_suni$cited_pmid,t_suni$citing_pmid))
+library(SuperExactTest)
+total <- length(t_list[[1]])+length(t_list[[2]])+length(t_list[[3]])+length(t_list[[4]])+length(t_list[[5]])
+t_test <- supertest(t_list)
+t_test$set.names <- c("alem","imat","nela","ramu","suni")

### 2017-06-08 Bright_Stars/R/Venn.R

@@ -1,0 +1,135 @@
+# Generate Venn Diagrams for biblio and grant data 
+rm(list=ls())
+setwd("~/NETELabs_CaseStudies/assembly/interim_results/")
+load(".RData")
+# else run load_interim_results.R
+
+alem_citing_pmid <- alem_m3$citing_pmid[!is.na(alem_m3$citing_pmid)]
+imat_citing_pmid <- imat_m3$citing_pmid[!is.na(imat_m3$citing_pmid)]
+nela_citing_pmid <- nela_m3$citing_pmid[!is.na(nela_m3$citing_pmid)]
+ramu_citing_pmid <- ramu_m3$citing_pmid[!is.na(ramu_m3$citing_pmid)]
+suni_citing_pmid <- suni_m3$citing_pmid[!is.na(suni_m3$citing_pmid)]
+
+alem_cited_pmid <- alem_m3$cited_pmid[!is.na(alem_m3$cited_pmid)]
+imat_cited_pmid <- imat_m3$cited_pmid[!is.na(imat_m3$cited_pmid)]
+nela_cited_pmid <- nela_m3$cited_pmid[!is.na(nela_m3$cited_pmid)]
+ramu_cited_pmid <- ramu_m3$cited_pmid[!is.na(ramu_m3$cited_pmid)]
+suni_cited_pmid <- suni_m3$cited_pmid[!is.na(suni_m3$cited_pmid)]
+
+alem_citing_sid <- alem_m3$citing_sid[!is.na(alem_m3$citing_sid)]
+imat_citing_sid <- imat_m3$citing_sid[!is.na(imat_m3$citing_sid)]
+nela_citing_sid <- nela_m3$citing_sid[!is.na(nela_m3$citing_sid)]
+ramu_citing_sid <- ramu_m3$citing_sid[!is.na(ramu_m3$citing_sid)]
+suni_citing_sid <- suni_m3$citing_sid[!is.na(suni_m3$citing_sid)]
+
+alem_cited_sid <- alem_m3$cited_sid[!is.na(alem_m3$cited_sid)]
+imat_cited_sid <- imat_m3$cited_sid[!is.na(imat_m3$cited_sid)]
+nela_cited_sid <- nela_m3$cited_sid[!is.na(nela_m3$cited_sid)]
+ramu_cited_sid <- ramu_m3$cited_sid[!is.na(ramu_m3$cited_sid)]
[…]

### 2017-06-08 Bright_Stars/R/exp_proj_link.R

@@ -1,0 +1,226 @@
+# Merge with projects and peer review data
+
+# load interim results files into a list
+rm(list=ls())
+# Load 9 csv files from Eric Livingston into a list
+
+setwd("~/NETELabs_CaseStudies/assembly/interim_results")
+# temp <- list.files(pattern="*.csv")
+# interim_results <- list()
+# for (i in 1:length(temp)) {
+#	interim_results[[i]] <- read.csv(temp[i],stringsAsFactors=FALSE,header=TRUE)
+#}
+# names(interim_results) <- temp
+# rm(i)
+# save(interim_results,file="interim_results.RData")
+
+# Read in pub_out (pmid-SID) and pub_cites (PubSID to SID) 
+
+# Clip SourceYear to restrict from 1900-2015.
+
+pub_out <- read.csv("pub_out.csv",colClasses=rep("character",6))
+pub_cites <- read.csv("pub_cites.csv",colClasses=rep("character",9))
+pub_cites$SourceYear <- as.integer(pub_cites$SourceYear)
+
+library(dplyr)
+pub_cites <- pub_cites %>% filter(SourceYear >=1900 & SourceYear <=2015)
+
+
+# free up memory
+# rm(interim_results)
+# print str stats
+str(pub_out)
+str(pub_cites)
+
+
+# Read in exporter link and projects data
+exp_link <- read.csv("~//NETELabs_CaseStudies/assembly/final_results/exporter_links.csv",colClasses=(rep("character",2)))
+exp_projects <- read.csv("~//NETELabs_CaseStudies/assembly/final_results/exporter_projects.csv",colClasses=(rep("character",9)))
+
+
+# load Stage I files that Eric used to generate pub_out and pub_cites
+alem <- read.csv("~/NETELabs_CaseStudies/assembly/alemtuzumab_assembly/alem_eric_stage1.csv",
+colClasses=c(rep("character",9)))
+imat <- read.csv("~/NETELabs_CaseStudies/assembly/imatinib_assembly/imat_eric_stage1.csv",
+colClasses=c(rep("character",9)))
+nela <- read.csv("~/NETELabs_CaseStudies/assembly/nelarabine_assembly/nela_eric_stage1.csv",
+colClasses=c(rep("character",9)))
[…]

### 2017-06-08 Bright_Stars/R/final_results.R

@@ -1,0 +1,170 @@
+# Work with final_results of 5/5/2017 from Eric.
+
+# load interim results files into a list
+rm(list=ls())
+# Load 9 csv files from Eric Livingston into a list
+
+setwd("~/NETELabs_CaseStudies/assembly/interim_results")
+temp <- list.files(pattern="*.csv")
+interim_results <- list()
+for (i in 1:length(temp)) {
+	interim_results[[i]] <- read.csv(temp[i],stringsAsFactors=FALSE,header=TRUE)
+}
+names(interim_results) <- temp
+rm(i)
+save(interim_results,file="interim_results.RData")
+
+# Extract pub_out (pmid-SID) and pub_cites (PubSID to SID) from list as data frames
+pub_out <- interim_results[['pub_out.csv']]
+pub_cites <- interim_results[['pub_cites.csv']]
+# free up memory
+rm(interim_results)
+# print str stats
+str(pub_out)
+str(pub_cites)
+
+# load Stage I files that Eric used to generate pub_out and pub_cites
+alem <- read.csv("~/NETELabs_CaseStudies/assembly/alemtuzumab_assembly/alem_eric_stage1.csv",
+stringsAsFactors=FALSE)
+imat <- read.csv("~/NETELabs_CaseStudies/assembly/imatinib_assembly/imat_eric_stage1.csv",
+stringsAsFactors=FALSE)
+nela <- read.csv("~/NETELabs_CaseStudies/assembly/nelarabine_assembly/nela_eric_stage1.csv",
+stringsAsFactors=FALSE)
+ramu <- read.csv("~/NETELabs_CaseStudies/assembly/ramucirumab_assembly/ramu_eric_stage1.csv",
+stringsAsFactors=FALSE)
+suni <- read.csv("~/NETELabs_CaseStudies/assembly/sunitinib_assembly/suni_eric_stage1.csv",
+stringsAsFactors=FALSE)
+
+# merge with pub_out to get corresponding SIDs
+alem_m1 <- merge(alem[,c(2,8)],pub_out[,1:2],by.x="id",by.y="PMID",all.x=TRUE)
+imat_m1 <- merge(imat[,c(2,8)],pub_out[,1:2],by.x="id",by.y="PMID",all.x=TRUE)
[…]

### 2017-06-08 Bright_Stars/R/five_pack_stageI_assembly.R

@@ -1,0 +1,20 @@
+# five_pack Stage I Assembly
+setwd("~/Desktop")
+rm(list=ls())
+library(dplyr)
+alem <- read.csv("~/NETELabs_CaseStudies/assembly/alemtuzumab_assembly/alem_eric_stage1.csv",stringsAsFactors=FALSE)
+imat <- read.csv("~/NETELabs_CaseStudies/assembly/imatinib_assembly/imat_eric_stage1.csv",stringsAsFactors=FALSE)
+nela <- read.csv("~/NETELabs_CaseStudies/assembly/nelarabine_assembly/nela_eric_stage1.csv",stringsAsFactors=FALSE)
+ramu <- read.csv("~/NETELabs_CaseStudies/assembly/ramucirumab_assembly/ramu_eric_stage1.csv",stringsAsFactors=FALSE)
+suni <- read.csv("~/NETELabs_CaseStudies/assembly/sunitinib_assembly/suni_eric_stage1.csv",stringsAsFactors=FALSE)
+five_pack_stageI <- rbind(alem,imat,nela,ramu,suni)
+five_pack_stageI <- five_pack_stageI[,-c(1,9)]
+colnames(five_pack_stageI) <- c("pmid","pubdate","firstauthor","lastauthor","source","title","year")
+five_pack_stageI[,"eid"] <- NA
+five_pack_stageI <- five_pack_stageI %>% select (pmid, eid, pubdate,firstauthor,lastauthor,source,title,year)
+library(dplyr)
+five_pack_stageI %>% nrow()
+five_pack_stageI %>% unique() %>% nrow()
+five_pack_stageI <- five_pack_stageI %>% unique()
+
+write.csv(five_pack_stageI,file="five_pack_stageI.csv",row.names=FALSE)

### 2017-06-08 Bright_Stars/R/imatinib_merge.R

@@ -1,0 +1,121 @@
+# imatinib_merge.R 
+# 4/13/2017
+# George Chacko
+
+# Metadata file 
+# imatinib_metadata
+
+# List of input files.
+# imatinib_fda_review.csv (single column, header is pmid)
+# imatinib_fda_pazdur.csv (single column, header is pmid)
+# imatinib_patent_npl.csv (single column, header is pmid)
+# imatinib_ct_nct.csv (two column, header is nct_id, pmid)
+# imatinib_ct_pubmed.csv (single column, header is pmid)
+# imatinib_pubmed.csv (single column, header is pmid)
+# imat_rev.csv (product of ~/NETELabs_CaseStudies/Review_Master/load_core_citation_data.R)
+
+setwd("~/NETELabs_CaseStudies/assembly/imatinib_assembly/")
+system("git pull")
+rm(list=ls())
+library(dplyr)
+
+## Clinical Trials Component
+#  Root to pubmed_derived clinical trials 
+imat_ct_pubmed <- read.csv("imatinib_ct_pubmed.csv",stringsAsFactors=FALSE)
+imat_ct1 <- imat_ct_pubmed %>% mutate(source="imatinib",stype="root",
+target=paste(pmid,"_ct",sep=""),ttype="ct") %>% select(source,stype,target,ttype)
+# pmid_ct to pmid1
+imat_ct2 <- imat_ct_pubmed %>% mutate(source=paste(pmid,"_ct",sep=""),stype="ct",target=pmid,
+ttype="pmid1") %>% select(source,stype,target,ttype) 
+
+# Root to nct_derived clinical trials
+imat_ct_nct <- read.csv("imatinib_ct_nct.csv",stringsAsFactors=FALSE)
+
+imat_ct3 <- imat_ct_nct %>% mutate(source="imatinib",stype="root",
+target=paste(pmid,"_ct",sep=""),ttype="ct") %>% select(source,stype,target,ttype)
+# nct to pmid1
+imat_ct4 <- imat_ct_nct %>% mutate(source=nct_id,stype="ct",target=pmid,
+ttype="pmid1") %>% select(source,stype,target,ttype) 
+
+## FDA Component
+# Scraped Medical Review derived
+imat_fda_review <- read.csv("imatinib_fda_review.csv",stringsAsFactors=FALSE)
[…]

### 2017-06-08 Bright_Stars/R/load_interim_results.R

@@ -1,0 +1,52 @@
+# load interim results files into a list
+rm(list=ls())
+setwd("~/Desktop/Interim_Results")
+temp <- list.files()
+interim_results <- list()
+for (i in 1:length(temp)) {
+	interim_results[[i]] <- read.csv(temp[i],stringsAsFactors=FALSE,header=TRUE)
+}
+names(interim_results) <- temp
+rm(i)
+pub_out <- interim_results[['pub_out.csv']]
+pub_cites <- interim_results[['pub_cites.csv']]
+rm(interim_results)
+alem <- read.csv("~//NETELabs_CaseStudies/assembly/alemtuzumab_assembly/alem_eric_stage1.csv",
+stringsAsFactors=FALSE)
+str(pub_out)
+str(pub_cites)
+str(alem)
+imat <- read.csv("~//NETELabs_CaseStudies/assembly/imatinib_assembly/imat_eric_stage1.csv",
+stringsAsFactors=FALSE)
+nela <- read.csv("~//NETELabs_CaseStudies/assembly/nelarabine_assembly/nela_eric_stage1.csv",
+stringsAsFactors=FALSE)
+ramu <- read.csv("~//NETELabs_CaseStudies/assembly/ramucirumab_assembly/ramu_eric_stage1.csv",
+stringsAsFactors=FALSE)
+suni <- read.csv("~//NETELabs_CaseStudies/assembly/sunitinib_assembly/suni_eric_stage1.csv",
+stringsAsFactors=FALSE)
+
+alem_m1 <- merge(alem[,2:3],pub_out[,1:2],by.x="id",by.y="PMID",all.x=TRUE)
+imat_m1 <- merge(imat[,2:3],pub_out[,1:2],by.x="id",by.y="PMID",all.x=TRUE)
+nela_m1 <- merge(nela[,2:3],pub_out[,1:2],by.x="id",by.y="PMID",all.x=TRUE)
+ramu_m1 <- merge(ramu[,2:3],pub_out[,1:2],by.x="id",by.y="PMID",all.x=TRUE)
+suni_m1 <- merge(suni[,2:3],pub_out[,1:2],by.x="id",by.y="PMID",all.x=TRUE)
+
+dim(alem_m1[!complete.cases(alem_m1),])
+dim(imat_m1[!complete.cases(imat_m1),])
[…]

### 2017-06-08 Bright_Stars/R/ramucirumab_merge.R

@@ -1,0 +1,126 @@
+# ramucirumab_merge.R 
+# 4/13/2017
+# George Chacko
+
+# Metadata file 
+# ramucirumab_metadata
+
+# List of input files.
+# ramucirumab_fda_review.csv (single column, header is pmid)
+# ramucirumab_fda_pazdur.csv (single column, header is pmid)
+# ramucirumab_patent_npl.csv (single column, header is pmid)
+# ramucirumab_ct_nct.csv (two column, header is nct_id, pmid)
+# ramucirumab_ct_pubmed.csv (single column, header is pmid)
+# ramucirumab_pubmed.csv (single column, header is pmid)
+# ramu_rev.csv (product of ~/NETELabs_CaseStudies/Review_Master/load_core_citation_data.R)
+
+setwd("~/NETELabs_CaseStudies/assembly/ramucirumab_assembly/")
+system("git pull")
+rm(list=ls())
+library(dplyr)
+
+## Clinical Trials Component
+#  Root to pubmed_derived clinical trials 
+ramu_ct_pubmed <- read.csv("ramucirumab_ct_pubmed.csv",stringsAsFactors=FALSE)
+ramu_ct1 <- ramu_ct_pubmed %>% mutate(source="ramucirumab",stype="root",
+target=paste(pmid,"_ct",sep=""),ttype="ct") %>% select(source,stype,target,ttype)
+# pmid_ct to pmid1
+ramu_ct2 <- ramu_ct_pubmed %>% mutate(source=paste(pmid,"_ct",sep=""),stype="ct",target=pmid,
+ttype="pmid1") %>% select(source,stype,target,ttype) 
+
+# Root to nct_derived clinical trials
+ramu_ct_nct <- read.csv("ramucirumab_ct_nct.csv",stringsAsFactors=FALSE)
+
+ramu_ct3 <- ramu_ct_nct %>% mutate(source="ramucirumab",stype="root",
+target=paste(pmid,"_ct",sep=""),ttype="ct") %>% select(source,stype,target,ttype)
+# nct to pmid1
+ramu_ct4 <- ramu_ct_nct %>% mutate(source=nct_id,stype="ct",target=pmid,
+ttype="pmid1") %>% select(source,stype,target,ttype) 
+
+## FDA Component
[…]

### 2017-06-08 Bright_Stars/R/reorderdrugnames.R

@@ -1,0 +1,22 @@
+# Takes intersection matrix from Keserci and reorder the drug
+# abbrevations alphabetically
+
+t <- read.csv("~/Dropbox/ERNIE_Pico/intersectMatrix.csv",stringsAsFactors=FALSE)
+t$no_of_drugs <- rowSums(t[,1:5])
+t$abbreviation <- toupper(t$abbreviation)
+library(dplyr)
+t[t=="0"] <- ""
+t[t=="1"] <- "X"
+t$no_of_drugs[t$no_of_drugs=="X"] <- 1
+colnames(t) <- c("alem(A)","imat,(I)","nela(N)","ramu(R)","suni(S)","Combination","Count","No_Of_Drugs" )
+t <- t[,c(1:5,6,8,7)]
+t <- t %>% arrange(desc(No_Of_Drugs,desc(Intersection)))
+t1 <- (strsplit(t$Combination,""))
+for (i in 1:length(t1)){
+	t2<-sort(t1[[i]])
+	t2<-paste(t2,collapse="")
+	t1[[i]]<- t2}
+t1 <- unlist(t1)
+t$Combination <- t1
+library(xtable)
+xtable(t)

### 2017-06-08 Bright_Stars/R/sunitinib_merge.R

@@ -1,0 +1,122 @@
+ # sunitinib_merge.R 
+# 4/14/2017
+# George Chacko
+
+# Metadata file 
+# sunitinib_metadata
+
+# List of input files.
+# sunitinib_fda_review.csv (single column, header is pmid)
+# sunitinib_fda_pazdur.csv (single column, header is pmid)
+# sunitinib_patent_npl.csv (single column, header is pmid)
+# sunitinib_ct_nct.csv (two column, header is nct_id, pmid)
+# sunitinib_ct_pubmed.csv (single column, header is pmid)
+# sunitinib_pubmed.csv (single column, header is pmid)
+# suni_rev.csv (product of ~/NETELabs_CaseStudies/Review_Master/load_core_citation_data.R)
+
+setwd("~/NETELabs_CaseStudies/assembly/sunitinib_assembly/")
+system("git pull")
+rm(list=ls())
+library(dplyr)
+
+## Clinical Trials Component
+#  Root to pubmed_derived clinical trials 
+suni_ct_pubmed <- read.csv("sunitinib_ct_pubmed.csv",stringsAsFactors=FALSE)
+suni_ct1 <- suni_ct_pubmed %>% mutate(source="sunitinib",stype="root",
+target=paste(pmid,"_ct",sep=""),ttype="ct") %>% select(source,stype,target,ttype)
+# pmid_ct to pmid1
+suni_ct2 <- suni_ct_pubmed %>% mutate(source=paste(pmid,"_ct",sep=""),stype="ct",target=pmid,
+ttype="pmid1") %>% select(source,stype,target,ttype) 
+
+# Root to nct_derived clinical trials
+suni_ct_nct <- read.csv("sunitinib_ct_nct.csv",stringsAsFactors=FALSE)
+
+suni_ct3 <- suni_ct_nct %>% mutate(source="sunitinib",stype="root",
+target=nct_id,ttype="ct") %>% select(source,stype,target,ttype)
+# nct to pmid1
+suni_ct4 <- suni_ct_nct %>% mutate(source=nct_id,stype="ct",target=pmid,
+ttype="pmid1") %>% select(source,stype,target,ttype) 
+
+## FDA Component
+# Scraped Medical Review derived
+suni_fda_review <- read.csv("sunitinib_fda_review.csv",stringsAsFactors=FALSE)
[…]

### 2017-06-09 Bright_Stars/LaTeX/Tables_Figs.tex
today's updates

--- 2017-06-08 Paper/plos-latex-template/Tables_Figs.tex
@@
 \begin{table}[!ht]
-%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-\scalebox{0.9}{
+\scalebox{1}{
 \begin{tabular}{|l+l|l|l|l|l|l|l|}
@@
 {\bf Case Studies of Five Anti-Cancer Agents} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies.
-The active ingredient for each of these five therapeutics is listed in column 1.
-The unique identifier for each therapeutic is the FDA assigned NDA or BLA number.
+The unique identifier for each therapeutic is an FDA assigned NDA or BLA number.
 While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic.
@@
 \label{table1}
-%\end{adjustwidth}
+\end{adjustwidth}
 \end{table}
@@
 \label{table2}
-%\end{adjustwidth}
+\end{adjustwidth}
 \end{table}
@@
 \begin{table}[!ht]
-\begin{adjustwidth}{-1.0in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\begin{adjustwidth}{-1.2in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-\scalebox{0.8}{\begin{tabular}{|l+l|l|l|l|l|l|l|}
+\scalebox{0.8}
+{\begin{tabular}{|l+l|l|l|l|l|l|l|}
 \hline
@@
   \hline
-1958 & J. Am. Stat. Assoc. & Kaplan E.R., Meier P. \\ 
-1963 & Science & Jerne, N. K. and Nordin, A. A.  \\ 
+1958 & J. Am. Stat. Assoc. & Kaplan ER, Meier P. \\ 
+1963 & Science & Jerne, NK and Nordin, AA.  \\ 
 1972 & J R Stat Soc & Cox DR.  \\ 
-1976 & Anal. Biochem. & Bradford MM \\ 
+1976 & Anal. Biochem. & Bradford MM. \\ 
 1977 & Br J Cancer & R. Peto, M.C. Pike, and P. Armitage  \\ 
-1977 & Proc. Natl. Acad. Sci. & Sanger, F., S. Nicklen, and A.R. Coulson.  \\ 
-1983 & J Immunol Methods & Mosmann T  \\ 
-1984 & Adv Enzyme Regul & T.C. Chou, and P. Talalay  \\ 
+1977 & Proc. Natl. Acad. Sci. & Sanger FS., Nicklen S, Coulson AR.  \\ 
+1983 & J Immunol Methods & Mosmann T.  \\ 
+1984 & Adv Enzyme Regul & Chou TC, Talalay P.  \\ 
 1989 & Molecular Cloning: A Laboratory Manual & Sambrook, J., Fritsch, E. and Maniatis, T.  \\ 
@@
 1994 & Acta Crystallogr. A & Navaza J.  \\ 
-1997 & Cell & Levine, A. J. \\ 
-1997 & Am. J. Pathol. & Perez-Atayde, A. R., Sallan, S. E., Tedrow, U., Connors, S., Allred, E., and Folkman, J.  \\ 
-1998 & CA: A Cancer Journal for Clinicians & SH Landis T Murray S Bolden PA Wingo \\ 
+1997 & Cell & Levine AJ. \\ 
+1997 & Am. J. Pathol. & Perez-Atayde AR, Sallan SE, Tedrow U, Connors S, Allred E, Folkman J.  \\ 
+1998 & CA: A Cancer Journal for Clinicians & Landis SH, Murray T,  Bolden S, Wingo PA. \\ 
 \hline
@@
 \vspace{2.5 mm}
-\caption{{\bf Intersection of Five Networks: Second Generation Publications} Publications common to all networks at the second generation level (cited\_sid, Fig 2). } 
+\caption{{\bf Intersection of Five Networks: Second Generation Publications} Publications at the intersection of all five networks are listed above.
+All 14 publications are found in the second generation of references(cited\_sid, Fig 2 Right Panel).
+}
 \label{table3}
@@
 \begin{figure}[!h]
+\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
+\scalebox{0.99}{
 \begin{subfigure}{.5\textwidth}
@@
   \includegraphics[width=.95\linewidth]{citing_pmid.png}
-  %\caption{}
   \label{fig:sub1}
@@
   \includegraphics[width=.95\linewidth]{cited_sid.png}
-  %\caption{}
   \label{fig:sub2}
-\end{subfigure}
-\caption{{\bf Intersecting Publications in Five Networks}  \emph{Left Panel.} Intersections were calculated across all five networks for citing\_pmids (the first generation of references) and displayed as a Venn diagram.
-No publications are common to all five networks.
+\end{subfigure}}
+\caption{{\bf Intersecting Publications in Five Networks} Intersections were calculated across all five networks for the first generation of references (citing\_pmids) and 
+as well as for the second generation of references (cited\_sids) and displayed as Venn diagrams.
+\emph{Left Panel.} No first generation publications are observed common to all five networks.
 A single publication is cited in four of five networks.
-\emph{Right Panel.} Intersections were calculated across all five networks for cited\_sids (the second generation of references) and displayed as a Venn diagram.
-14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib)}
+\emph{Right Panel.} 14  publications are common to all five networks.
+Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib)}
 \label{fig:test}
+\end{adjustwidth}
 \end{figure}
+\clearpage
 
 \begin{figure}[!h]
+\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-\includegraphics[scale=0.1]{cy_core14_v2csv_6b.png}
+\scalebox{1.3}{
+\includegraphics[scale=0.1]{cy_core14_v2csv_5.png}}
 \caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic.
@@
 Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
-\label{fig3}
+\label{fig2}
+\end{adjustwidth}
 \end{figure}
@@
 \begin{figure}[!h]
+\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
@@
 \caption{{\bf NIH Research Support} Grant and contract support for publications from NIH in the five networks was identified using ExPORTER data (Materials and Methods).
-19,104 unique project numbers were identified of which 112 projects were common to all five networks.
+19,104 unique project numbers were identified as sources of support for publications in all five networks.
+Of these, 112 projects were common to all five networks.
 Projects were grouped by mechanism (i) P-  Research Program Projects and Centers (ii) R- Research Projects (iii) M-General Clinical Research Centers Programs (iv) N-Research and Development-Related Contracts (v) U-Cooperative Agreements (vi) T-Training Programs (vii) Z- Intramural Research.
@@
 A higher proportion of Research Program Projects and Centers awards is found in the intersection group.}
-\label{fig4}
+\label{fig3}
+\end{adjustwidth}
 \end{figure}

### 2017-06-09 Bright_Stars/LaTeX/plos_latex_template.tex
today's updates

--- 2017-06-08 Paper/plos-latex-template/plos_latex_template.tex
@@
 % WATERMARKS
-\usepackage{draftwatermark}
-\SetWatermarkText{Confidential}
-\SetWatermarkScale{4}
+%\usepackage{draftwatermark}
+%\SetWatermarkText{Confidential}
+%\SetWatermarkScale{4}
 
@@
 \bigskip
-\textbf{1} Netelabs, NET ESolutions Corporation, McLean, VA, USA
+\textbf{1} NETE Labs, NET ESolutions Corporation, McLean, VA, USA
 \\
-\textbf{2} Elsevier Research Intelligence, Elsevier Inc., Bethesda, MD, USA
+\textbf{2} Research Intelligence, Elsevier Inc., New York, NY, USA
 \\
@@
 % Use the asterisk to denote corresponding authorship and provide email address in note below.
-*Correspondence: george@nete.com
+*Correspondence: netelabs@nete.com
 \end{flushleft}
@@
 To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic.
-This methodology is extensible beyond the history of a therapeutic and its use supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
+This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
 As a proof of principle, we have conducted a case study of five anti-cancer therapeutics.
-We have linked the work of over 220,000 authors in roughly 92,000 scientific publications that capture the research crucial for the development of these five therapeutics.
+We have linked the work of over 235,000 authors in roughly 103,000 scientific publications that capture the research crucial for the development of these five therapeutics.
 We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards.
-Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as a core set of awards from the National Institutes of Health that supported this research.
+Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as awards from the National Institutes of Health that supported this research.
 Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented in these networks.
@@
 The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents the progress of concepts from basic research to a cure is termed a `cure network' \cite {bibWilliams}.
-Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will uncover previous influential discovery (\textit{ibid}).
-Beyond using a digital methodology to assemble a set of facts about a major scientific advance, a deeper contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time\cite{bibMaldame} is enabled.
+Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will reveal previous influential discovery (\textit{ibid}).
+Beyond using a digital methodology to assemble a set of facts about a major scientific advance, a deeper contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time~\cite{bibMaldame} is enabled.
 Such studies (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases \cite {bibLauer} (ii) support strategic communications to oversight bodies, and (iii) help communicate the societal value of research.
-Importantly too, when coupled with information that accrues from clinical use of a drug, knowledge of its development network enables a recursive uncovering of the pathogenesis of the disease it is being used to treat as noted for the burgeoning field of immunotherapeutics\cite{bibChan}.
+Importantly too, when coupled with information that accrues from clinical use of a drug, knowledge of its development network enables a recursive uncovering of the pathogenesis of the disease it is being used to treat, as noted for the burgeoning field of immunotherapeutics~\cite{bibChan}.
 
 Williams and colleagues have elegantly demonstrated the feasibility and value of data mining and network analysis using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}).
-They observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-related research over a period greater than 100 years.
+They observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-relevant research over a period greater than 100 years.
 These authors also suggest that thoughtful metrics derived from this concept could inform decision making by funders.
@@
 For evaluation, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer.
-We present the results of this case study as a body of work for interrogation and improvement by other researchers, and a step towards mapping the universe of FDA-approved drugs and biologicals.
+We present the results of this case study as a body of work for further study by other researchers, and a step towards mapping the universe of FDA-approved drugs and biologicals.
 
@@
 Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab (Campath) are humanized antibodies that target the CD52 and vEGFR-2 cell surface receptors respectively.
-For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.\cite{bibWilliams} but with specific modifications detailed below.
+For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.~\cite{bibWilliams} but with specific modifications detailed below.
 An allowance of 2 months was also made for `publication lag' when assembling referenced material.
@@
 
-\textbf{FDA documents} The drugs@fda website\cite{bibFDA} was searched for each of the five therapeutics and cited references in the medical review document were manually extracted and matched to pmids.
+\textbf{FDA documents} The drugs@fda website~\cite{bibFDA} was searched for each of the five therapeutics and cited references in the medical review document were manually extracted and matched to pmids.
 FDA Approval Summaries published in journals by FDA staff, were available for all five therapeutics and contain cited references.
-If the published date of a citated reference exceeded the approval date plus two months, the publication was not included.
+If the published date of a cited reference in an Approval Summary exceeded the approval date plus two months, the publication was not included.
 
@@
 Identification of this patent was performed using multiple web sources.
-The US patent number was then used to identify the patent and the non-patent citation list from Google Patents \cite{bibGooglePatents} was manually processed by searching PubMed for appropriate pmids.
-While we developed a citation matching tool for non-patent literature for this purpose, the accuracy of manual searches was far higher and were used to generate the data in this study.
+The US patent number was then used to identify the patent and the non-patent citation list from Google Patents ~\cite{bibGooglePatents} was manually processed by searching PubMed for appropriate pmids.
+The accuracy of manual searches was far higher than a citation matching tool that we developed for for this purpose,and were used to generate the data in this study.
 
 \textbf{Post-approval literature reviews} Review articles published after a therapeutic's approval by the FDA are independent studies of the the development of a therapeutic.
-Accordingly, PubMed was searched for review articles of a therapeutic that were published between the date of FDA approval and one year following the date of approval and cited references in these reviews were extracted using PubMed and Scopus.
+Accordingly, PubMed was searched for review articles on these five therapeutics that were published between the date of FDA approval and a year following the date of approval.
+Cited references in these reviews were extracted using PubMed and Scopus.
+The review articles themselves were not included.
 
@@
 
-Citing\_pmids from the five different sources above  were combined and deduplicated.
-Using the Scopus database and its APIs, these citing\_pmids were mapped to Scopus identifiers (citing\_sid) from which a second generation of cited references (cited\_sid) was extracted.
-These cited\_sids, were in turn, mapped back to pmids (cited\_pmid).
+\textbf{PubMed and Scopus} Citing\_pmids from the five different sources above  were combined and deduplicated.
+Using the Scopus database and its APIs.
+The manually-generated list of pmids taken from the five sources mentioned (Clinical Trials, FDA Documents, Patents, Post-Approval Literature, and Pre-Approval Literature Searches) were searched in Scopus, using the basic Scopus Search API, to arrive at a list of Scopus IDs (citing\_sid) for the publications.
+The Scopus Abstract Retrieval API was then used to retrieve a more comprehensive record for each of the SIDs comprising that list of publications Next, for each of these publication records citing\_sid), we used the Scopus Author Retrieval API to retrieve a full record for each unique author in the  publication set.
+We also used the Abstract Retrieval API to collect records for each of the publications cited by the first generation of publications.
+This set of cited publications is the cited\_sid set.
+Using the same Author Retrieval API, we then gathered data for each of the unique authors affiliated with the cited\_sid publications.
+Completion of the process yields two sets of publications, citing\_sid and cited\_sid, with citation links between them and full information on all authors for both generations.
+Finally, for each author in the study, we used the standard Scopus Search API once more to retrieve a smaller record for every publication affiliated with them in Scopus, in order to tally their overall publication output.
+While author records in Scopus have overall publication counts as part of the record, by manually downloading each of them, we can store and count them by type (i.e.
+article, book chapter, Editorial, review, etc.).
+This allowed us to more precisely arrive at publication totals for only those publication types that are relevant for this study.
+[which are]
+
 Whereas mapping between PubMed and Scopus identifiers at the citing\_pmid and citing\_sid stage resulted in 1\% or less information loss, mapping at the cited\_sid to cited\_pmid resulted in a loss of roughly 15-20 \% of target records.
@@
 
-Both citing and cited pmids were mapped to NIH grants and peer review panels (study sections) using public information available through NIH ExPORTER\cite{bibNIHExPORTER}.
+Both citing and cited pmids were mapped to NIH grants and peer review panels (study sections) using public information available through NIHExPORTER~~\cite{bibNIHExPORTER}.
 Thus, we enriched our network data by identifying those study sections associated with the awards that supported publications in our networks.
 
-The resultant data were modeled as networks and analyzed using metrics based on network topology.
-We calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams \cite {bibWilliams}.
+\textbf{Networks} The resultant data were modeled as networks and analyzed using metrics based on network topology.
+We calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams ~~\cite{bibWilliams}.
 PIR represents the sum of weighted citation scores for all articles in a network that can be attributed to an author.
@@
 Computations were performed on infrastructure owned or leased by NET ESolutions, Elsevier , or the Gladstone Institutes.
-Code and scripts used in this study were written in Java, Python, SQL, and R and are archived on a publicly accessible Github repository\cite{bibGithub}.
-Network visualization was performed using Cytoscape\cite{bibCytoscape}.
+Code and scripts used in this study were written in Java, Python, SQL, and R and are archived on a publicly accessible Github repository~\cite{bibGithub}.
+Network visualization was performed using Cytoscape~\cite{bibCytoscape}.
 \section*{Results and Discussion}
 
-\subsection*{Publications} Scientific publications form the backbone of each of these five networks.
+\textbf{Publications} Scientific publications form the backbone of each of these five networks.
 Our initial assumptions of appropriate citation and retrospective citation discovery (Introduction) suggest that network nodes that are common to multiple networks are likely to be influential.
-We calculated intersection counts for all possible combinations of publications in the Alemtuzumab, Imatinib, Nelarabine, Ramucirumab, and Sunitinib networks (S1 Table 1).
+We calculated intersection counts for all possible combinations of publications in the Alemtuzumab, Imatinib, Nelarabine, Ramucirumab, and Sunitinib networks (\nameref{S2_Table 1}).
 We also applied intersection analysis at a finer level of granularity by computing intersection counts for both first generation citations (citing\_pmid) and second generation citations (cited\_sid).
@@
 The intersection of all five networks consists of 14 publications out of a total of 91,991 unique Scopus identifiers.
-Strikingly, not even a single publication is common to all five networks at the first generation level (citing\_sid) although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies\cite{bibKohler}, is cited in four out of five networks.
+Strikingly, not even a single publication is common to all five networks at the first generation level (citing\_sid) although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies~\cite{bibKohler}, is cited in four out of five networks.
 All 14 publications are in the second generation of citations (cited\_sid) and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references.
 We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4 publications), analytical and structural biology techniques (3 publications) and cancer biology (2 publications).
-Of these last two, one is a review of the p53 gene\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia\cite{bibFolkman}.
-Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the general scientific literature \cite{bibVanNoorden}.
+Of these last two, one is a review of the p53 gene~\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia~\cite{bibFolkman}.
+Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the general scientific literature ~\cite{bibVanNoorden}.
 The relationship between core publications and their therapeutic networks is visualized in Fig 3.
@@
 2]}.
-As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks.
+As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks using high level descriptive terms.
 
-\subsection*{Grant Support} With its annual budget of approximately US\$32 billion, NIH is a major funder of biomedical research through its granting program.
+\textbf{Grant Support} With its annual budget of approximately US\$32 billion, NIH is a major funder of biomedical research through its granting program.
 Understanding the nature and extent of NIH grant support for the research represented in our five networks, provides insight into the funding programs that enabled this research.
-We took advantage of publicly available data\cite{bibNIHExPORTER} to identify grant support for the publications in our five networks by mapping them to pmids.
+We took advantage of publicly available data~\cite{bibNIHExPORTER} to identify grant support for the publications in our five networks by mapping them to pmids.
 A total 19,104 unique grant numbers was harvested of which 112 were found in all five networks.
@@
 
-\subsection*{Peer Review} Research support from NIH is typically made through a two stage peer-review process.
-The Center for Scientific Review at NIH manages first-stage scientific review of between 50,000-60,000 grant applications each year\cite{bibBoyack}, a process involving more than 15,000 expert reviewers.
+\textbf{Peer Review} Research support from NIH is typically made through a two stage peer-review process.
+The Center for Scientific Review at NIH manages first-stage scientific review of between 50,000-60,000 grant applications each year~\cite{bibBoyack}, a process involving more than 15,000 expert reviewers.
 In addition, individual Institutes and Centers at NIH manage smaller scale peer review operations.
-Assuming an overall success rate of 20\%, peer review plays the role of a collaborative scientific activity and that serves as a selection layer strongly influencing granting outcomes.
+Crudely estimating success rate at 20\%, peer review plays the role of a collaborative scientific activity and that serves as a selection layer strongly influencing granting outcomes.
 To describe this layer at a high-level, we matched the awards in the the five networks to the peer review panels (study sections) that evaluated them for scientific merit and calculated the intersection and union of these peer review panels.
@@
 
-\subsection*{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information).
+\textbf{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information).
 The nPIR metric describes the sum of weighted citation scores for all articles that a researcher has in all five networks.
@@
 A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied.
-Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would attenuate this limitation\cite{bibKinch} but this goal is unlikely to be achieved in the very short term and other data quality issues are likely to emerge.
+Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would attenuate this limitation~\cite{bibKinch} but this goal is unlikely to be achieved in the very short term and other data quality issues are likely to emerge.
 
@@
 This metric is therefore likely to be useful when the author disambiguation problem and article capture is resolved to the point where data quality is significantly improved and is not recommended except when strong confidence exists in the total productivity counts.
-In general, these metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (Supplemental Data).
+In general, these metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (\nameref{S3_Table 2}).
 These `bright stars in neighboring constellations', represent elite performers in network(s) of clinical and basic science expertise again reinforcing the concept of collaborative translational achievements built upon a body of basic science.
-Beyond simple weighting and normalization that we have used, a variety of citation metrics such as SNIP\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study\cite{bibIoannidis}.
+Beyond simple weighting and normalization that we have used, a variety of citation metrics such as SNIP~\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study~\cite{bibIoannidis}.
 
@@
 While finer critical evaluation of the content of datasets generated through this approach is best left to experts, the methodology is broadly accessible and can also be viewed as another tool for citizen science.
-Overall, no single metric will provide useful answers, instead expert interpretation of multiple metrics best matched to curated datasets is likely to yield greater value.
+Overall, no single metric will provide useful answers, instead expert interpretation of multiple metrics best matched to curated datasets will yield greater value.
 
@@
 
-\paragraph*{S2 Fig.}
-\label{S2_Fig}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
+\paragraph*{S2 Table 1}
+\label{S2_Table 1}
+{\bf Intersecting Publications Across Networks.}
 
-\paragraph*{S3 Table.}
-\label{S1_Table}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
+\paragraph*{S3 Table 2}
+\label{S3_Table 2}
+{\bf Elite Performers in Networks}
 
-\section*{Acknowledgments} %We thank Sandeep Somaiya for his support of of the nascent Netelabs concept.
+\section*{Acknowledgments} We thank Sandeep Somaiya from NETE as well as Daniel Calto, M'hamed Aisati, Sherif El Shamy, and Holly J.
+Falk-Krzesinski from Elsevier for their support of this collaborative effort.
 
@@
 \newblock {{F}rom Scientific Discovery to Cures: Bright Stars within a Galaxy.}
-\newblock Cell. 2015 Sep; 163:21--23
+\newblock Cell. 2015 163:21--23.
 
@@
 \newblock {{T}he Importance Of The History Of Science In Intellectual Formation.}
-\newblock Scripta Varia 2002 104:237-248
+\newblock Scripta Varia 2002 104:237-248.
+
+\bibitem{bibLauer}
+Lauer MS.
+\newblock {{P}CSK9 Inhibitors: Lots of Work Done, Lots More to Do.}
+\newblock Ann Intern Med. 2016 164(9):624-625.
 
@@
 \newblock {{I}n Search of Magic Bullets: The Golden Age of Immunotherapeutics.}
-\newblock Cell. 2014 Mar; 157:227-240
-
-\bibitem{bibLauer}
-Lauer MS.
-\newblock {{P}CSK9 Inhibitors: Lots of Work Done, Lots More to Do.}
-\newblock Ann Intern Med. 2016 Mar; 164(9):624-625.
+\newblock Cell. 2014 157:227-240.
 
@@
 \newblock {{D}rugs@FDA: FDA Approved Drug Products.}
-\newblock https://www.accessdata.fda.gov/scripts/cder/daf/
+\newblock https://www.accessdata.fda.gov/scripts/cder/daf/.
 
@@
 \newblock {{G}oogle Patents}
-\newblock https://patents.google.com/
+\newblock https://patents.google.com/.
 
@@
 \newblock {{N}IH ExPORTER}
-\newblock https://exporter.nih.gov/
+\newblock https://exporter.nih.gov/.
 
 \bibitem{bibGithub}
-\newblock {{N}ET ESolution, Netelabs Repository}
-\newblock https://github.com/NETESOLUTIONS/NETELabs
+\newblock {{N}ET ESolutions, NETE Labs}
+\newblock https://github.com/NETESOLUTIONS/NETELabs\_CaseStudies/tree/master/Bright\_Stars.
 
@@
 \newblock {{C}ytoscape: a software environment for integrated models of biomolecular interaction networks.}
-\newblock Genome Res. 2003 Nov;13(11):2498-504
+\newblock Genome Res. 2003 13(11):2498-504.
 
@@
 \newblock { {C}ontinuous cultures of fused cells secreting antibody of predefined specificity.}
-\newblock Nature. 1975 256: 495-497
+\newblock Nature. 1975 256: 495-497.
 
@@
 \newblock {{p53}, the cellular gatekeeper for growth and division.}
-\newblock Cell. 1997 Feb 7;88(3):323-31.
+\newblock Cell. 1997 88(3):323-31.
 
@@
 \newblock {{Spectrum} of tumor angiogenesis in the bone marrow of children with acute lymphoblastic leukemia}
-\newblock Am J Pathol. 1997 Mar;150(3):815-21.
+\newblock Am J Pathol. 1997 150(3):815-21.
 
@@
 \newblock {{T}he top 100 papers}
-\newblock Nature. 2014 514: 550-553
+\newblock Nature. 2014 514: 550-553.
 
@@
 \newblock {{C}haracterization of the Peer Review Network at the Center for Scientific Review, National Institutes of Health}
-\newblock  PLoS One. 2014 10.1371/journal.pone.0104244
+\newblock  PLoS One. 2014 10.1371/journal.pone.0104244.
 
@@
 \newblock {{A}n overview of FDA-approved new molecular entities: 1827-2013}
-\newblock  Drug Discov Today. 2014 Aug; 19(8):1033-9 doi: 10.1016/j.drudis.2014.03.018.
+\newblock  Drug Discov Today. 2014 19(8):1033-9 doi: 10.1016/j.drudis.2014.03.018.
 
@@
 \newblock {{S}ome modifications to the SNIP journal impact indicator.}
-\newblock  J Informetrics. 2013.7(2), 272-285.
+\newblock  J Informetrics. 2013. 7(2): 272-285.
 
@@
 \newblock {{C}itation Metrics: A Primer on How (Not) to Normalize.}
-\newblock  PLoS Biology. 2016. 10.1371/journal.pbio.1002542
+\newblock  PLoS Biology. 2016. 10.1371/journal.pbio.1002542.
 

### 2017-06-09 Bright_Stars/LaTeX/preprint.tex
more of today's updates

--- 2017-06-09 Bright_Stars/LaTeX/plos_latex_template.tex
@@
 %\usepackage{wrapfig}
+\usepackage{subcaption}
 
@@
 % WATERMARKS
-%\usepackage{draftwatermark}
-%\SetWatermarkText{Confidential}
-%\SetWatermarkScale{4}
+\usepackage{draftwatermark}
+\SetWatermarkText{Draft}
+\SetWatermarkScale{3}
 
@@
 
+\begin{table}[!ht]
+\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\scalebox{1}{
+\begin{tabular}{|l+l|l|l|l|l|l|l|}
+\hline
+%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
+Therapeutic & FDA Approval Date & Unique Identifier & US Patent & Publication Date  \\ \hline
+$Alemtuzumab$ & May 2001 & BLA: 103948 & US5846534 & Dec 1998\\ \hline
+$Imatinib$ & May 2001 & NDA: 021335 & US5521184 &  May 1996 \\ \hline
+$Nelarabine$ & Oct 2005 & NDA: 021877 & US5424295 & Jun 1995  \\ \hline
+$Ramucirumab$ & Apr 2014 & BLA: 125477 & US7498414 & Mar 2009  \\ \hline
+$Sunitinib$ & Jan 2006  & NDA: 021938  & US6573293 & Jun 2003 \\ \hline
+\end{tabular}}
+\vspace{2 mm}
+\caption{
+{\bf Case Studies of Five Anti-Cancer Agents} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies.
+The unique identifier for each therapeutic is an FDA assigned NDA or BLA number.
+While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic.
+The publication date for each patent is listed in the last column.}
+%\begin{flushleft}  
+%\end{flushleft}
+\label{table1}
+\end{adjustwidth}
+\end{table}
+
 \textbf{Clinical trials} The national clinical trials database (clinicaltrials.gov) was searched for clinical trials of the five therapeutics that completed by the data of FDA approval.
@@
 
+\begin{table}[!ht]
+\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\scalebox{1}{
+\begin{tabular}{|l+l|l|l|l|l|l|l|}
+\hline
+%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
+Therapeutic & citing\_pmid count & citing\_sid count & cited\_sid count  & cited\_pmid count  \\ \hline
+$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
+$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
+$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
+$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
+$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
+\end{tabular}
+}
+\vspace{2.5 mm}
+\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies.
+A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature (Materials and Methods).
+Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve cited publications (cited\_sid).
+Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field}
+\label{table2}
+\end{adjustwidth}
+\end{table}
+
 Both citing and cited pmids were mapped to NIH grants and peer review panels (study sections) using public information available through NIHExPORTER~~\cite{bibNIHExPORTER}.
@@
 
+\begin{figure}[!h]
+\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\scalebox{0.99}
+{
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.95\linewidth]{citing_pmid.png}
+  \label{fig:sub1}
+\end{subfigure}
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.95\linewidth]{cited_sid.png}
+  \label{fig:sub2}
+\end{subfigure}
+}
+\caption{{\bf Intersecting Publications in Five Networks} Intersections were calculated across all five networks for the first generation of references (citing\_pmids) and 
+as well as for the second generation of references (cited\_sids) and displayed as Venn diagrams.
+\emph{Left Panel.} No first generation publications are observed common to all five networks.
+A single publication is cited in four of five networks.
+\emph{Right Panel.} 14  publications are common to all five networks.
+Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib)}
+\label{fig: test}
+\end{adjustwidth}
+\end{figure}
+
 The intersection of all five networks consists of 14 publications out of a total of 91,991 unique Scopus identifiers.
@@
 Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the general scientific literature ~\cite{bibVanNoorden}.
-The relationship between core publications and their therapeutic networks is visualized in Fig 3.
+The relationship between core publications and their therapeutic networks is visualized in Fig 2.
+As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks using high level descriptive terms.
 \textbf{[Insert Fig.
 2]}.
-As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks using high level descriptive terms.
+
+\begin{figure}[!h]
+\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\scalebox{1.3}{
+\includegraphics[scale=0.1]{cy_core14_v2csv_5.png}}
+\caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic.
+Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5).
+14  publications are common to all five networks (Table 3) and are colored red.
+The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly.
+Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
+\label{fig2}
+\end{adjustwidth}
+\end{figure}
 
@@
 We speculate that the broader and collaborative nature of such awards may be more likely to result in a methods-rich population of publications than the more focused research project award but elucidation will require further and more rigorous study.
+
+\begin{figure}[!h]
+\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\includegraphics[scale=0.1]{proj_percent.png}
+\caption{{\bf NIH Research Support} Grant and contract support for publications from NIH in the five networks was identified using ExPORTER data (Materials and Methods).
+19,104 unique project numbers were identified as sources of support for publications in all five networks.
+Of these, 112 projects were common to all five networks.
+Projects were grouped by mechanism (i) P-  Research Program Projects and Centers (ii) R- Research Projects (iii) M-General Clinical Research Centers Programs (iv) N-Research and Development-Related Contracts (v) U-Cooperative Agreements (vi) T-Training Programs (vii) Z- Intramural Research.
+For each mechanism, the number of projects in the intersection of all five networks was plotted against the number in the union of all five networks (both expressed as percentages of their respective totals).
+A higher proportion of Research Program Projects and Centers awards is found in the intersection group.}
+\label{fig3}
+\end{adjustwidth}
+\end{figure}
 
@@
 
-\section*{Acknowledgments} We thank Sandeep Somaiya from NETE as well as Daniel Calto, M'hamed Aisati, Sherif El Shamy, and Holly J.
-Falk-Krzesinski from Elsevier for their support of this collaborative effort.
+\section*{Acknowledgments} We thank Sandeep Somaiya from NETE as well as Holly J. Falk-Krzesinski from Elsevier for their support of this collaborative effort.
 

### 2017-06-11 Bright_Stars/Python/01 - Retrieve N1 Publications.py
Elsevier API Scripts

@@ -1,0 +1,166 @@
+# Retrieve N1 Publications
+# By: Eric Livingston (e.livingston@Elsevier.com)
+# Copyright © 2017 Elsevier B.V. All rights reserved.
+
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions are
+# met:
+
+# 1.	Redistributions of source code must retain the above copyright notice,
+#   	this list of conditions and the following disclaimer.
+
+# 2.	Redistributions in binary form must reproduce the above copyright
+#   	notice, this list of conditions and the following disclaimer in the
+#   	documentation and/or other materials provided with the distribution.
+
+# Neither the name of the copyright holder nor the names of its
+# contributors may be used to endorse or promote products derived from
+# this software without specific prior written permission.
+
+# THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS
+# IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED
+# TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A
+# PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+# HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+# SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED
+# TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
+# PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
+# LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+# NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+# SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+# Retrieves core (N1) set of initial publication from list of PubMed IDs
+# The ID file in the example contains pubmed IDs in column 1, and a blank column for
+# EIDs (Elsevier IDs). If the Pubmed ID is not found in Scopus, an exception for that
[…]

### 2017-06-11 Bright_Stars/Python/02 - Retrieve N1 Authors.py

@@ -1,0 +1,122 @@
+# Retrieve N1 Publication Authors
+# By: Eric Livingston (e.livingston@Elsevier.com)
+# Copyright © 2017 Elsevier B.V. All rights reserved.
+
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions are
+# met:
+
+# 1.	Redistributions of source code must retain the above copyright notice,
+#   	this list of conditions and the following disclaimer.
+
+# 2.	Redistributions in binary form must reproduce the above copyright
+#   	notice, this list of conditions and the following disclaimer in the
+#   	documentation and/or other materials provided with the distribution.
+
+# Neither the name of the copyright holder nor the names of its
+# contributors may be used to endorse or promote products derived from
+# this software without specific prior written permission.
+
+# THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS
+# IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED
+# TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A
+# PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+# HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+# SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED
+# TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
+# PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
+# LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+# NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+# SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+import json
+import fileinput
+import ElsevierClient as Elsevier
+from sortedcontainers import SortedList
+from sortedcontainers import SortedDict
+
+AUTH_FILE = "Output\\authors_scopus.json"
+N1_PUBS = "Output\\n1_pubs_scopus.json"
[…]

### 2017-06-11 Bright_Stars/Python/03 - Retrieve N2 Publications.py

@@ -1,0 +1,122 @@
+# Retrieve N2 Publications (those cited by N1)
+# By: Eric Livingston (e.livingston@Elsevier.com)
+# Copyright © 2017 Elsevier B.V. All rights reserved.
+
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions are
+# met:
+
+# 1.	Redistributions of source code must retain the above copyright notice,
+#   	this list of conditions and the following disclaimer.
+
+# 2.	Redistributions in binary form must reproduce the above copyright
+#   	notice, this list of conditions and the following disclaimer in the
+#   	documentation and/or other materials provided with the distribution.
+
+# Neither the name of the copyright holder nor the names of its
+# contributors may be used to endorse or promote products derived from
+# this software without specific prior written permission.
+
+# THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS
+# IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED
+# TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A
+# PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+# HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+# SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED
+# TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
+# PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
+# LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+# NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+# SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+import json
+import fileinput
+import ElsevierClient as Elsevier
+from sortedcontainers import SortedSet
+
+N1_PUBS = "Output\\n1_pubs_scopus.json"
+N2_PUBS = "Output\\n2_pubs_scopus.json"
[…]

### 2017-06-11 Bright_Stars/Python/04 - Retrieve N2 Authors.py

@@ -1,0 +1,117 @@
+# Retrieve N2 Authors
+# By: Eric Livingston (e.livingston@Elsevier.com)
+# Copyright © 2017 Elsevier B.V. All rights reserved.
+
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions are
+# met:
+
+# 1.	Redistributions of source code must retain the above copyright notice,
+#   	this list of conditions and the following disclaimer.
+
+# 2.	Redistributions in binary form must reproduce the above copyright
+#   	notice, this list of conditions and the following disclaimer in the
+#   	documentation and/or other materials provided with the distribution.
+
+# Neither the name of the copyright holder nor the names of its
+# contributors may be used to endorse or promote products derived from
+# this software without specific prior written permission.
+
+# THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS
+# IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED
+# TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A
+# PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+# HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+# SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED
+# TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
+# PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
+# LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+# NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+# SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+import json
+import fileinput
+import ElsevierClient as Elsevier
+from sortedcontainers import SortedList
+from sortedcontainers import SortedDict
+
+AUTH_FILE = "Output\\authors_scopus.json"
+N2_PUBS = "Output\\n2_pubs_scopus.json"
[…]

### 2017-06-11 Bright_Stars/Python/05 - Process Pubs and Authors.py

@@ -1,0 +1,107 @@
+# Process Pubs and Authors (format into standard Objects)
+# By: Eric Livingston (e.livingston@Elsevier.com)
+# Copyright © 2017 Elsevier B.V. All rights reserved.
+
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions are
+# met:
+
+# 1.	Redistributions of source code must retain the above copyright notice,
+#   	this list of conditions and the following disclaimer.
+
+# 2.	Redistributions in binary form must reproduce the above copyright
+#   	notice, this list of conditions and the following disclaimer in the
+#   	documentation and/or other materials provided with the distribution.
+
+# Neither the name of the copyright holder nor the names of its
+# contributors may be used to endorse or promote products derived from
+# this software without specific prior written permission.
+
+# THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS
+# IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED
+# TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A
+# PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+# HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+# SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED
+# TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
+# PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
+# LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+# NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+# SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+import json
+import jsonpickle
+import fileinput
+import ElsevierClient as Elsevier
+from sortedcontainers import SortedList
+
+AuthIDs = SortedList()
+PubIDs = SortedList()
[…]

### 2017-06-11 Bright_Stars/Python/06 - Output CSVs.py

@@ -1,0 +1,215 @@
+# Output CSVs (Base data used for analysis, importable into the SQL database
+# By: Eric Livingston (e.livingston@Elsevier.com)
+# Copyright © 2017 Elsevier B.V. All rights reserved.
+
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions are
+# met:
+
+# 1.	Redistributions of source code must retain the above copyright notice,
+#   	this list of conditions and the following disclaimer.
+
+# 2.	Redistributions in binary form must reproduce the above copyright
+#   	notice, this list of conditions and the following disclaimer in the
+#   	documentation and/or other materials provided with the distribution.
+
+# Neither the name of the copyright holder nor the names of its
+# contributors may be used to endorse or promote products derived from
+# this software without specific prior written permission.
+
+# THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS
+# IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED
+# TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A
+# PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+# HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+# SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED
+# TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
+# PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
+# LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+# NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+# SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+import csv
+import json
+import fileinput
+import ElsevierClient as Elsevier
+from sortedcontainers import SortedList
+
+N1_PUBS = "Output\\n1_publications.json"
[…]

### 2017-06-11 Bright_Stars/Python/07 - Retrieve All Author Pubs.py

@@ -1,0 +1,140 @@
+# Retrieve All Author Pubs (download smaller records for every publication by every author)
+# By: Eric Livingston (e.livingston@Elsevier.com)
+# Copyright © 2017 Elsevier B.V. All rights reserved.
+
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions are
+# met:
+
+# 1.	Redistributions of source code must retain the above copyright notice,
+#   	this list of conditions and the following disclaimer.
+
+# 2.	Redistributions in binary form must reproduce the above copyright
+#   	notice, this list of conditions and the following disclaimer in the
+#   	documentation and/or other materials provided with the distribution.
+
+# Neither the name of the copyright holder nor the names of its
+# contributors may be used to endorse or promote products derived from
+# this software without specific prior written permission.
+
+# THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS
+# IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED
+# TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A
+# PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+# HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+# SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED
+# TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
+# PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
+# LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+# NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+# SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+import json
+import fileinput
+import ElsevierClient as Elsevier
+from sortedcontainers import SortedList
+from multiprocessing.dummy import Pool as ThreadPool
+
[…]

### 2017-06-11 Bright_Stars/Python/08 - Count Author Output.py

@@ -1,0 +1,100 @@
+# Count Author Output (write out publication counts, by type, for each author, for analysis)
+# By: Eric Livingston (e.livingston@Elsevier.com)
+# Copyright © 2017 Elsevier B.V. All rights reserved.
+
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions are
+# met:
+
+# 1.	Redistributions of source code must retain the above copyright notice,
+#   	this list of conditions and the following disclaimer.
+
+# 2.	Redistributions in binary form must reproduce the above copyright
+#   	notice, this list of conditions and the following disclaimer in the
+#   	documentation and/or other materials provided with the distribution.
+
+# Neither the name of the copyright holder nor the names of its
+# contributors may be used to endorse or promote products derived from
+# this software without specific prior written permission.
+
+# THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS
+# IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED
+# TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A
+# PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+# HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+# SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED
+# TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
+# PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
+# LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+# NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+# SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+import csv
+import json
+import fileinput
+from sortedcontainers import SortedDict
+
+AUTHORS = "Output\\authors.json"
+AUTH_PUBS = 'Output\\auth_publications.json'
[…]

### 2017-06-11 Bright_Stars/Python/ElsevierClient.py

@@ -1,0 +1,730 @@
+# Elsevier Scopus Client module
+# By: Eric Livingston (e.livingston@Elsevier.com)
+# Copyright © 2017 Elsevier B.V. All rights reserved.
+
+# Redistribution and use in source and binary forms, with or without
+# modification, are permitted provided that the following conditions are
+# met:
+
+# 1.	Redistributions of source code must retain the above copyright notice,
+#   	this list of conditions and the following disclaimer.
+
+# 2.	Redistributions in binary form must reproduce the above copyright
+#   	notice, this list of conditions and the following disclaimer in the
+#   	documentation and/or other materials provided with the distribution.
+
+# Neither the name of the copyright holder nor the names of its
+# contributors may be used to endorse or promote products derived from
+# this software without specific prior written permission.
+
+# THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS
+# IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED
+# TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A
+# PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+# HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+# SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED
+# TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
+# PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
+# LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+# NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+# SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+import json
+import time
+import jsonpickle
+import urllib.request
+import urllib.parse
+import urllib.error
+import multiprocessing.dummy as multiprocessing
+from munch import *
+from sortedcontainers import SortedSet
+
+# Replace the string below with your Scopus API key
[…]

### 2017-06-11 Bright_Stars/LaTeX/preprint.tex
updates

@@
 The set of scientific publications, clinical trials, patents, and regulatory approvals, linked to each other by citation or assignment, that documents the progress of concepts from basic research to a cure is termed a `cure network' \cite {bibWilliams}.
-Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will reveal previous influential discovery (\textit{ibid}).
-Beyond using a digital methodology to assemble a set of facts about a major scientific advance, a deeper contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time~\cite{bibMaldame} is enabled.
-Such studies (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases \cite {bibLauer} (ii) support strategic communications to oversight bodies, and (iii) help communicate the societal value of research.
-Importantly too, when coupled with information that accrues from clinical use of a drug, knowledge of its development network enables a recursive uncovering of the pathogenesis of the disease it is being used to treat, as noted for the burgeoning field of immunotherapeutics~\cite{bibChan}.
+Reconstructing such networks enables a deeper contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time~\cite{bibMaldame}.
+Such studies also (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases \cite {bibLauer} (ii) support strategic communications to oversight bodies, and (iii) help communicate the societal value of research.
+The understanding of a therapeutic network, when coupled with information from clinical use of a therapeutic, also enables a recursive learning of the pathogenesis of the disease it is being used to treat, as has been noted for the burgeoning field of immunotherapeutics~\cite{bibChan}.
 
@@
 To address these questions, we have built upon prior art for single networks to (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extended single network analysis to map publications and authors across multiple networks.
+Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will reveal previous influential discovery~\cite{bibWilliams}.
 For evaluation, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer.
@@
 \section*{Materials and Methods}  A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration was selected for this study (Table 1).
-Imatinib and Sunitinib are tyrosine kinase inhibitors, Nelarabine is a nucleoside analog, and Ramucirumab and Alemtuzumab (Campath) are humanized antibodies that target the CD52 and vEGFR-2 cell surface receptors respectively.
+Imatinib~\cite{bibImatinib} and Sunitinib~\cite{bibSunitinib} are tyrosine kinase inhibitors, Nelarabine~\cite{bibNelarabine} is a nucleoside analog, and Ramucirumab~\cite{bibRamucirumab} and Alemtuzumab (Campath)~\cite{bibAlemtuzumab} are humanized antibodies that target the CD52 and vEGFR-2 cell surface receptors respectively.
 For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.~\cite{bibWilliams} but with specific modifications detailed below.
@@
 We calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams ~~\cite{bibWilliams}.
-PIR represents the sum of weighted citation scores for all articles in a network that can be attributed to an author.
+PIR represents the sum of aggregated citation scores (first and second degree only)  for all articles in a network that can be attributed to an author.
 In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a networkPIR (nPIR) score, which was also normalized to the sum of individual PIR scores within each network as the PIRpartitionRatio (PPR) as a way to measure inter-network influence.
@@
 All data used in this study were acquired exclusively from the sources listed above.
-Computations were performed on infrastructure owned or leased by NET ESolutions, Elsevier , or the Gladstone Institutes.
-Code and scripts used in this study were written in Java, Python, SQL, and R and are archived on a publicly accessible Github repository~\cite{bibGithub}.
+Computations were performed on infrastructure owned or leased by NET ESolutions, Elsevier, or the Gladstone Institutes.
+Code and scripts used in this study were written in Java, Python, and R and are archived on a publicly accessible Github repository~\cite{bibGithub}.
 Network visualization was performed using Cytoscape~\cite{bibCytoscape}.
+
 \section*{Results and Discussion} 
-
 \textbf{Publications} Scientific publications form the backbone of each of these five networks.
@@
 We also applied intersection analysis at a finer level of granularity by computing intersection counts for both first generation citations (citing\_pmid) and second generation citations (cited\_sid).
-The results are displayed as Venn diagrams in Figure 1.
+The results are displayed as Venn diagrams in Fig.
+1.
 \textbf{[Insert Fig.
@@
 Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the general scientific literature ~\cite{bibVanNoorden}.
-The relationship between core publications and their therapeutic networks is visualized in Fig 2.
+The relationship between core publications and their therapeutic networks is visualized in Fig.
+2.
 As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks using high level descriptive terms.
@@
 \scalebox{1.3}{
-\includegraphics[scale=0.1]{cy_core14_v2csv_5.png}}
+\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
 \caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic.
@@
 A significant loss of information occurs when mapping from cited\_sid to cited\_pmid (Table 2).
-Thus we believe that these numbers are an underestimate of actual grant support from NIH.
-Also missing from this analysis, however, are details of research support from other funding agencies and industry, which are questions that we intend to pursue.
+Thus we believe that these numbers may be an underestimate of actual grant support from NIH.
+Also missing from this analysis are details of research support from other funding agencies and industry, which are questions that we intend to pursue.
 Even so, these data testify to a recurring theme of collaboration and breadth of community engagement that is also seen at the publication level.
@@
 In addition, individual Institutes and Centers at NIH manage smaller scale peer review operations.
-Crudely estimating success rate at 20\%, peer review plays the role of a collaborative scientific activity and that serves as a selection layer strongly influencing granting outcomes.
+Considering a crude estimate of a 20\% success rate in funding, peer review can be viewed as a collaborative scientific activity and that serves as a selection layer for the upper fifth of applications, thus strongly influencing granting outcomes.
 To describe this layer at a high-level, we matched the awards in the the five networks to the peer review panels (study sections) that evaluated them for scientific merit and calculated the intersection and union of these peer review panels.
@@
 \textbf{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information).
-The nPIR metric describes the sum of weighted citation scores for all articles that a researcher has in all five networks.
-When combined with the PIRpartitionRatio (PPR), insight into cross-network influence is generated.
+The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks.
+The PIRpartitionRatio (PPR) results from normalizing nPIR to the sum of individual PIR scores to gain insight into holo-network influence.
 A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied.
-Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would attenuate this limitation~\cite{bibKinch} but this goal is unlikely to be achieved in the very short term and other data quality issues are likely to emerge.
+Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch} although other data related issues may well emerge.
 
-While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher.
-We found several instances in the top 10\% of PIR scores where the gRBR was significantly inaccurate (data not shown).
+While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher, which is sensitive to data quality in bibliometric databases.
+We found several instances in the top 10\% of PIR scores where the gRBR was implausible likely on account of polysemy, synonymy, or incompleteness.
 This metric is therefore likely to be useful when the author disambiguation problem and article capture is resolved to the point where data quality is significantly improved and is not recommended except when strong confidence exists in the total productivity counts.
-In general, these metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (\nameref{S3_Table 2}).
+These metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (\nameref{S3_Table 2}).
 These `bright stars in neighboring constellations', represent elite performers in network(s) of clinical and basic science expertise again reinforcing the concept of collaborative translational achievements built upon a body of basic science.
-Beyond simple weighting and normalization that we have used, a variety of citation metrics such as SNIP~\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study~\cite{bibIoannidis}.
+Beyond simple aggregation, weighting, and normalization that we have used, a variety of citation metrics such as SNIP~\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study~\cite{bibIoannidis}.
+The use of these citation measures will assume greater importance when scale up from small numbers of networks to a greater proportion of the global network.
 
-In summary, we have developed and demonstrated a methodology not restricted to  drug discovery and cures alone, that offers burden-reduction in explorations of science history.
-It contributes to the understanding of collaboration across domains and can be used to  enrich portfolio analysis, planning and optimization, as well as communications of the societal value of research.
+In summary, we have demonstrated a digital methodology based on data mining and network analysis, not restricted to  drug discovery and cures alone, that offers burden-reduction in explorations of science history.
+Beyond assembling a set of facts about a major scientific advance, it contributes to the understanding of collaboration across domains and can be used to  enrich portfolio analysis, planning and optimization, as well as communications of the societal value of research.
 The approach can be easily adapted to study the collaborative history within and across research portfolios of groups of researchers and targeted programs such as the Clinical and Translational Science Award (CTSA) Program.
 While finer critical evaluation of the content of datasets generated through this approach is best left to experts, the methodology is broadly accessible and can also be viewed as another tool for citizen science.
-Overall, no single metric will provide useful answers, instead expert interpretation of multiple metrics best matched to curated datasets will yield greater value.
+Overall, no single metric will provide useful answers, instead expert interpretation of multiple metrics best matched to curated datasets will be valuable.
 
@@
 
-\section*{Acknowledgments} We thank Sandeep Somaiya from NETE as well as Holly J. Falk-Krzesinski from Elsevier for their support of this collaborative effort.
+\section*{Acknowledgments}  This study would not have been possible without data that is made publicly available by NIH and the FDA.
+We thank Tandy Warnow for critical comments and advice on formalizing definitions.
+We thank Sandeep Somaiya from NETE and Holly J.
+Falk-Krzesinski from Elsevier for their support of this project.
 
@@
 \bibitem{bibMaldame}
-Maldame, J.
+Maldame J.
 \newblock {{T}he Importance Of The History Of Science In Intellectual Formation.}
@@
 \newblock Cell. 2014 157:227-240.
+
+\bibitem{bibImatinib}
+Buchdunger E, Zimmermann J, Mett H, Meyer T, M\"uller M, Druker BJ, Lydon NB.
+\newblock {{I}nhibition of the Abl protein-tyrosine kinase in vitro and in vivo by a 2-phenylaminopyrimidine derivative.}
+\newblock Cancer Res. 1996 56(1):100-4
+
+\bibitem{bibSunitinib}
+O'Farrell AM, Abrams TJ, Yuen HA, Ngai TJ, Louie SG, Yee KW, et al. 
+\newblock {{S}U11248 is a novel FLT3 tyrosine kinase inhibitor with potent activity in vitro and in vivo.}
+\newblock Blood. 2003 101(9):3597-605.
+
+\bibitem{bibNelarabine}
+Ho PT, Cheson BD, Phillips PH.
+\newblock {{C}linical trials referral resource. Clinical trials using compound 506U78.}
+\newblock Oncology (Williston Park). 1996 10(12):1831-2.
+
+\bibitem{bibRamucirumab}
+Krupitskaya Y, Wakelee HA.
+\newblock {{R}amucirumab, a fully human mAb to the transmembrane signaling tyrosine kinase VEGFR-2 for the potential treatment of cancer.}
+\newblock Curr Opin Investig Drugs. 2009 10(6):597-605.
+
+\bibitem{bibAlemtuzumab}
+Hale G, Bright S, Chumbley G, Hoang T, Metcalf D, Munro AJ, Waldmann H.
+\newblock {{R}emoval of T cells from bone marrow for transplantation: a monoclonal antilymphocyte antibody that fixes human complement.}
+\newblock Blood. 1983 62(4):873-82.
 
@@
 \bibitem{bibGithub}
+Keserci S, Livingston E, Wan L, Pico AR, Chacko G.
 \newblock {{N}ET ESolutions, NETE Labs}

### 2017-06-11 Bright_Stars/LaTeX/revised_math.tex
updates

\documentclass[12pt]{amsart}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsmath,amssymb}
\geometry{a4paper} 
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]

\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

% or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry

% See the ``Article customise'' template for come common customisations

\title{}
\author{}
\date{} % delete this line to display the current date

%%% BEGIN DOCUMENT
\begin{document}

% Use the asterisk to denote corresponding authorship and provide email address in note below.
\section*{Network Calculations}

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\vspace{.1in}

\paragraph{\textbf{Propagated Indegree Rank (PIR)}} 
In this study, we examine five therapeutics $d_1, d_2, \ldots, d_5$, and their networks $N_1, N_2, \ldots, N_5$.
The nodes of network $N_i$ are the publications associated to the therapeutic $d_i$, and the directed edges of $N_i$ are
obtained by the global network $\mathcal{G}$. Thus, we include a directed
edge between publications $x$ and $y$ if  and only if $x$ cites $y$  in $\mathcal{G}$. Hence, 
$N_i$ is a simple graph (no parallel edges and no self-loops).

We define  network $\mathcal{N}$ to be the graph-theoretic union of the
networks $N_1, N_2, \ldots, N_5$ (i.e., $\mathcal{N} =\cup_i N_i$). Thus, the nodes of the
network $\mathcal{N}$ are the nodes that appear in at least one network $N_i$, and we include a directed
edge between publications $x$ and $y$ if  and only if $x$ cites $y$ in at least one of the networks $N_i$; hence, 
$\mathcal{N}$ is a simple graph (no parallel edges and no self-loops).

Let $\mathfrak{n}$ denote some selected network $\mathcal{N}_i$, 
let $c_{\mathfrak{n}}(\mathfrak{p})$ be the citation score of publication $\mathfrak{p}$ in  $\mathfrak{n}$, and let $\mathcal{C}_\mathfrak{p}^\mathfrak{n}$ be the set of publications in $\mathfrak{\mathfrak{n}}$ that cite $\mathfrak{p}$.

We define the aggregated citation count for  $\mathfrak{p}$ within network $\mathfrak{\mathfrak{n}}$, denoted by  $ac_{\mathfrak{n}}(\mathfrak{p})$, by
$$ ac_{\mathfrak{n}}(\mathfrak{p}) = c_{\mathfrak{n}}(\mathfrak{p}) + \sum_{g\in \mathcal{C}_\mathfrak{p}^\mathfrak{n}}  c_{\mathfrak{n}}(g).$$

Let $\mathcal{A}_a^{\mathfrak{n}}$ be the set of publications for an author $\mathfrak{a}$ in  $\mathfrak{\mathfrak{n}}$. Then the PIR score  for  $\mathfrak{a}$  in network $\mathfrak{n}$ is defined by $$ pir_{\mathfrak{n}}(\mathfrak{a}) =  \sum_{p\in \mathcal{A}_a^{\mathfrak{n}}}  ac_{\mathfrak{n}}(\mathfrak{p}) $$

Hence, 
%the PIR score for author  $\mathfrak{a}$ in  $\mathfrak{n}$ is  
$$ pir_{\mathfrak{n}}(\mathfrak{a}) =  \sum_{p\in \mathcal{A}_a^{\mathfrak{n}} } \big[c_{\mathfrak{{\mathfrak{n}}}}(p) + \sum_{g\in \mathcal{C}_\mathfrak{p}^{\mathfrak{n}}}  c_{\mathfrak{{\mathfrak{n}}}}(g)\big] $$

Next we define the nPIR score  of author $\mathfrak{a}$ within network $\mathcal{N}$ (denoted by $nPIR\mathfrak{a}$) to  be  $pir_{\mathcal{N}}(\mathfrak{a})$; in other words
it is the $pir$ score based on the network $\mathcal{N}$.

%$npir(\mathfrak{a})$, which is $pir$ score based on the  total network $\mathcal{N}$.

% For convenience, instead of denoting it $pir_N$, we use $npir$   Furthermore

We define the PIR partition ratio (PPR)  of author $\mathfrak{a}$ (denoted by $ppr(\mathfrak{a})$)
to be 
%:\mathcal{A}\rightarrow [0,\infty]$  of author $\mathfrak{a}$ as 
$$ppr(\mathfrak{a})= \dfrac{ nPIR({\mathfrak{a}})} {\sum_{i=1}^{5} pir_{N_i}(\mathfrak{a})} $$
%where $\mathcal{A}$ is the set of authors in $\mathcal{N}$  and  $pir_{N_i}(\mathfrak{a})$.
% is the PIR score of the author $\mathfrak{a}$ in $\mathcal{N}_i$.
%restricted to only drug network $\mathcal{D}_i$ .

There are cases where PPR can be greater than 1.
% and one way this can occur is when an author's influence extends beyond $\mathcal{N}_i$ but within $\mathcal{N}$.

\vspace{.1in}

\paragraph{\textbf {Ratio of Basic Rankings (RBR)}}
\begin{itemize}
\item nRBR (i.e., network RBR) is the ratio of an author's publication count in a given network $\mathfrak{n}$ to the total publication count for that author  in $\mathcal{N}$.
 Thus, nRBR depends on both the author $\mathfrak{a}$ and the given network $\mathfrak{n}$, and is denoted by $nRBR(\mathfrak{a},\mathfrak{n})$.
%We define in-degree count $ic_{d_i}(\mathfrak{a})$ of an author $\mathfrak{a}$ as the total number of the publication which is in the network $\mathcal{N}_i$ of the drug $d_i$, similarly lets $ic_{n}$ be the number of the paper that author $\mathfrak{a}$ published in the total Network(5-drug's network) $\mathcal{N}$. Then we define, nRBR of an author $\mathfrak{a}$  for a drug $d_i$ as follow.
%$$ nrbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{N}(\mathfrak{a})}$$
\item gRBR, or global RBR, is the ratio of an author's count of publications in network $\mathfrak{n}$ to the author's total publication count in the global network $\mathcal{G}$,
and is denoted by gRBR$(\mathfrak{a},\mathfrak{n})$. 
%Thus, the $grlobRBR(\mathfrak{a},n)$ score of an author  $\mathfrak{a}$  for the drug $d_i$ is defined as 
%$$grbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{G}(\mathfrak{a})}$$
%where $ic_{G}$ is the total number of publication that an author $\mathfrak{a}$ currently has.
\end{itemize}
\noindent
nRBR$(\mathfrak{a},n)$ and gRBR$(\mathfrak{a},n)$ are both ratios with the same numerator but with different denominators, and  
$0 \leq$ nRBR$(\mathfrak{a},\mathfrak{n}) \leq$ gRBR$(\mathfrak{a},\mathfrak{n}) \leq 1$.

\end{document}
 Here in this study we focus on the $ppr$ values which is greated than 1. Greater the value, the higher the level of interactions(citation edges/flow) of the author's publication between other publications in the subnetworks. We have proved in Proposition 0.1 that a lower bound for ppr score of an author is 0.2. The cases where $ppr\leq1$  will be addressed in the next study due the coupling of intersection count and inter-citation issues.

\begin{proposition}
Let the set $\mathcal{K}$ be the union of $k\geq 2$ subnetworks, and N be the complete citation network of the set K. Then the lower bound for the $ppr$ score is 1/k. 
\end{proposition}

\begin{proof} Let $\mathcal{A}_\mathfrak{a}^N$ be the set publications $\{\mathfrak{p}_1,\mathfrak{p}_2,...,\mathfrak{p}_m\} $  written by an author $\mathfrak{a}$ in the whole network $\mathcal{N}$. For any $\mathfrak{p}_j \in \mathcal{A}_\mathfrak{a}^N$, lets define sequence of publication $S_r^n (\mathfrak{p}_j)$ be the sequence of publication(with duplicates) having exactly $r$ number of edges  apart in the directed graph of citation Network. Then, aggragated citation of a paper  $\mathfrak{p}_j$ in any network $\mathfrak{n}$ can also be written
$$wc_n(\mathfrak{p}_j) = |S_1^n(\mathfrak{p}_j)| + |S_2^n(\mathfrak{p}_j)|$$ 
where $|\cdot|$ defined as the length of the sequence. Since for any subnetwork $d_i$, $|S_r^{d_i}| \leq  |S_r^N| $
for $r \geq1$, we have then,

\begin{equation}
\begin{split}
\sum_{i=1}^k wc_{d_i}(\mathfrak{p}_j) &= \sum_{i=1}^k |S_1^{d_i}(\mathfrak{p}_j)| + |S_2^{d_i}(\mathfrak{p}_j)| \\
 &\leq \sum_{i=1}^k |S_1^{N}(\mathfrak{p}_j)| + |S_2^{N}(\mathfrak{p}_j)| \\
 &=k(|S_1^{N}(\mathfrak{p}_j)| + |S_2^{N}(\mathfrak{p}_j)|)\\
 &=k(wc_N(\mathfrak{p}_j))
\end{split}
\end{equation}

Next  using  inequality (1) and changing the order of sums due to finite index sum gives,

\begin{equation}
\begin{split}
\sum_{i=1}^k pir_{d_i}(\mathfrak{a})&=\sum_{i=1}^k \sum_{j=1}^m wc_{d_i}(\mathfrak{p}_j)=\sum_{j=1}^m \sum_{i=1}^k wc_{d_i}(\mathfrak{p}_j) \\
&\leq k\sum_{j=1}^m  wc_N(\mathfrak{p}_j) = k (npir(\mathfrak{a}))
\end{split}
\end{equation}

which implies that \\

\begin{equation}
\begin{split}
\dfrac{1}{k}\leq \dfrac{npir(\mathfrak{a})}{\sum_{i=1}^k pir_{d_i}(\mathfrak{a})}=ppr(\mathfrak{a})
\end{split}
\end{equation}

\end{proof}

\end{document}

### 2017-06-14 Bright_Stars/R/ExPORTER_Project_Data.R
Create ExPORTER_Project_Data.R

@@ -1,7 +1,8 @@
+# Read in ExPorter Project Data from downloaded csvs into a data frame. 
+# Because the number of columns changed over the years, we select a subset.
+
 # load exporter projects files into a list
 rm(list = ls())
-# Read in ExPorter Project Data from downloaded csvs and pass the resultant  
-# data frame to darlin (NETE Labs Server)
 
 setwd("~/Desktop/ExPORTER/xCleaned")
 temp <- list.files(pattern = "*.csv")

### 2017-07-06 Bright_Stars/LaTeX/preprint.tex

@@
 % WATERMARKS
-\usepackage{draftwatermark}
-\SetWatermarkText{Draft}
-\SetWatermarkScale{3}
+%\usepackage{draftwatermark}
+%\SetWatermarkText{Preprint}
+%\SetWatermarkScale{3}
 
@@
 %Samet Keserci\textsuperscript{1,2\Yinyang},
-Eric Livingston\textsuperscript{2},
+Eric B. Livingston\textsuperscript{2},
 Lingtian Wan\textsuperscript{1,\textcurrency},
@@
 As a proof of principle, we have conducted a case study of five anti-cancer therapeutics.
-We have linked the work of over 235,000 authors in roughly 103,000 scientific publications that capture the research crucial for the development of these five therapeutics.
+We have linked the work of roughly 237,000 authors in 106,000 scientific publications that capture the research crucial for the development of these five therapeutics.
 We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards.
@@
 
-\linenumbers
+%\linenumbers
 
@@
 
-\section*{Materials and Methods}  A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration was selected for this study (Table 1).
+\section*{Materials and Methods}  A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration (FDA) was selected for this study (Table 1).
 Imatinib~\cite{bibImatinib} and Sunitinib~\cite{bibSunitinib} are tyrosine kinase inhibitors, Nelarabine~\cite{bibNelarabine} is a nucleoside analog, and Ramucirumab~\cite{bibRamucirumab} and Alemtuzumab (Campath)~\cite{bibAlemtuzumab} are humanized antibodies that target the CD52 and vEGFR-2 cell surface receptors respectively.
@@
 For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included.
-For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (below).
-\textbf{[Insert Table 1]}
+For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (Table 1).
 
@@
 This allowed us to more precisely arrive at publication totals for only those publication types that are relevant for this study.
-[which are]
 
@@
 These observations are summarized in Table 2.
-\textbf{[Insert Table 2]}
 
@@
 Therefore, we created two new variants of the RBR; network RBR (nRBR) and global-based RBR (gRBR).
-nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total article output of an author as background.
-Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively.
+nRBR uses all publications in our set of five therapeutics as background and gRBR takes advantage of the Scopus author\_id to capture the total article output of an author as background.
+Thus, nRBR and gRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively.
 The details of how these metrics were calculated are provided in supplementary material \nameref{S1_File}.\\
@@
 1.
-\textbf{[Insert Fig.
-1]}
 
@@
 
-The intersection of all five networks consists of 14 publications out of a total of 91,991 unique Scopus identifiers.
+The intersection of all five networks consists of 14 publications out of a total of 106,720 unique Scopus identifiers (Supplemental Data, Table 1).
 Strikingly, not even a single publication is common to all five networks at the first generation level (citing\_sid) although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies~\cite{bibKohler}, is cited in four out of five networks.
@@
 As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks using high level descriptive terms.
-\textbf{[Insert Fig.
-2]}.
 
@@
 \includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
-\caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic.
+\caption{{\bf Core Publications in Networks}  The arcs of blue nodes identify first generation publications (citing\_sid) for each therapeutic.
 Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5).
@@
 
-\textbf{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information).
+\textbf{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information, Table 2).
 The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks.
@@
 While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher, which is sensitive to data quality in bibliometric databases.
-We found several instances in the top 10\% of PIR scores where the gRBR was implausible likely on account of polysemy, synonymy, or incompleteness.
+For example, we found several instances in the top 10\% of PIR scores where the gRBR was implausible likely on account of polysemy, synonymy, or incompleteness.
 This metric is therefore likely to be useful when the author disambiguation problem and article capture is resolved to the point where data quality is significantly improved and is not recommended except when strong confidence exists in the total productivity counts.
@@
 
-\section*{Supporting Information}
-
-\paragraph*{S1 File.}
-\label{S1_File}
-{\bf Network Calculations} The basis of calculations for network metrics.
-
-\paragraph*{S2 Table 1}
-\label{S2_Table 1}
-{\bf Intersecting Publications Across Networks.}
-
-\paragraph*{S3 Table 2}
-\label{S3_Table 2}
-{\bf Elite Performers in Networks}
-
 \section*{Acknowledgments}  This study would not have been possible without data that is made publicly available by NIH and the FDA.
 We thank Tandy Warnow for critical comments and advice on formalizing definitions.
-We thank Sandeep Somaiya from NETE and Holly J.
+We thank Sydney Gomes and Caitlin Werle for assistance with graphics.
+We thank Sandeep Somaiya from NETE as well as Daniel Calto and Holly J.
 Falk-Krzesinski from Elsevier for their support of this project.
 
-\nolinenumbers
+%\nolinenumbers
 
@@
 \end{thebibliography}
+
+\section*{Supporting Information}
+
+\paragraph*{S1 File.}
+\label{S1_File}
+{\bf Network Calculations} The basis of calculations for network metrics.
+
+\paragraph*{S2 Table 1}
+\label{S2_Table 1}
+{\bf Intersecting Publications Across Networks.}
+
+\paragraph*{S3 Table 2}
+\label{S3_Table 2}
+{\bf Elite Performers in Networks} 
 \end{document}

### 2017-07-06 Bright_Stars/Submission/biorxiv_supp.tex

--- 2017-06-11 Bright_Stars/LaTeX/revised_math.tex
@@
 \newtheorem{lemma}[theorem]{Lemma}
+
+\usepackage{changepage}
+\usepackage{graphics}
 
@@
 
-Next we define the nPIR score  of author $\mathfrak{a}$ within network $\mathcal{N}$ (denoted by $nPIR\mathfrak{a}$) to  be  $pir_{\mathcal{N}}(\mathfrak{a})$; in other words
+Next we define the nPIR score  of author $\mathfrak{a}$ within network $\mathcal{N}$ (denoted by $nPIR\mathfrak{(a)}$) to  be  $pir_{\mathcal{N}}(\mathfrak{a})$; in other words
 it is the $pir$ score based on the network $\mathcal{N}$.
 
-%$npir(\mathfrak{a})$, which is $pir$ score based on the  total network $\mathcal{N}$.
-
-% For convenience, instead of denoting it $pir_N$, we use $npir$   Furthermore
-
-We define the PIR partition ratio (PPR)  of author $\mathfrak{a}$ (denoted by $ppr(\mathfrak{a})$)
-to be 
-%:\mathcal{A}\rightarrow [0,\infty]$  of author $\mathfrak{a}$ as 
 $$ppr(\mathfrak{a})= \dfrac{ nPIR({\mathfrak{a}})} {\sum_{i=1}^{5} pir_{N_i}(\mathfrak{a})} $$
-%where $\mathcal{A}$ is the set of authors in $\mathcal{N}$  and  $pir_{N_i}(\mathfrak{a})$.
-% is the PIR score of the author $\mathfrak{a}$ in $\mathcal{N}_i$.
-%restricted to only drug network $\mathcal{D}_i$ .
 
 There are cases where PPR can be greater than 1.
-% and one way this can occur is when an author's influence extends beyond $\mathcal{N}_i$ but within $\mathcal{N}$.
 
-\vspace{.1in}
-
+\vspace{0.05 in}
 \paragraph{\textbf {Ratio of Basic Rankings (RBR)}}
@@
  Thus, nRBR depends on both the author $\mathfrak{a}$ and the given network $\mathfrak{n}$, and is denoted by $nRBR(\mathfrak{a},\mathfrak{n})$.
-%We define in-degree count $ic_{d_i}(\mathfrak{a})$ of an author $\mathfrak{a}$ as the total number of the publication which is in the network $\mathcal{N}_i$ of the drug $d_i$, similarly lets $ic_{n}$ be the number of the paper that author $\mathfrak{a}$ published in the total Network(5-drug's network) $\mathcal{N}$.
-Then we define, nRBR of an author $\mathfrak{a}$  for a drug $d_i$ as follow.
-%$$ nrbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{N}(\mathfrak{a})}$$
 \item gRBR, or global RBR, is the ratio of an author's count of publications in network $\mathfrak{n}$ to the author's total publication count in the global network $\mathcal{G}$,
 and is denoted by gRBR$(\mathfrak{a},\mathfrak{n})$. 
-%Thus, the $grlobRBR(\mathfrak{a},n)$ score of an author  $\mathfrak{a}$  for the drug $d_i$ is defined as 
-%$$grbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{G}(\mathfrak{a})}$$
-%where $ic_{G}$ is the total number of publication that an author $\mathfrak{a}$ currently has.
 \end{itemize}
@@
 
-\end{document}
- Here in this study we focus on the $ppr$ values which is greated than 1.
-Greater the value, the higher the level of interactions(citation edges/flow) of the author's publication between other publications in the subnetworks.
-We have proved in Proposition 0.1 that a lower bound for ppr score of an author is 0.2.
-The cases where $ppr\leq1$  will be addressed in the next study due the coupling of intersection count and inter-citation issues.
+\clearpage
 
-\begin{proposition}
-Let the set $\mathcal{K}$ be the union of $k\geq 2$ subnetworks, and N be the complete citation network of the set K. Then the lower bound for the $ppr$ score is 1/k. 
-\end{proposition}
+\begin{table}[!ht]
+\begin{adjustwidth}{-0.5 in}{0 in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{{\bf Intersection of Five Networks: Second Generation Publications}}
+\scalebox{0.8}{\begin{tabular}{|l+l|l|l|l|l|l|l|}
+\hline
+\hline
+SourceYear & SourceName & Author(s) \\ 
+  \hline
+1958 & J. Am. Stat. Assoc. & Kaplan ER, Meier P. \\ 
+1963 & Science & Jerne, NK and Nordin, AA.  \\ 
+1972 & J R Stat Soc & Cox DR.  \\ 
+1976 & Anal. Biochem. & Bradford MM. \\ 
+1977 & Br J Cancer & R. Peto, M.C. Pike, and P. Armitage  \\ 
+1977 & Proc. Natl. Acad. Sci. & Sanger FS., Nicklen S, Coulson AR.  \\ 
+1983 & J Immunol Methods & Mosmann T.  \\ 
+1984 & Adv Enzyme Regul & Chou TC, Talalay P.  \\ 
+1989 & Molecular Cloning: A Laboratory Manual & Sambrook, J., Fritsch, E. and Maniatis, T.  \\ 
+1994 & Acta Crystallogr D & Collaborative Computational Project 4 \\ 
+1994 & Acta Crystallogr. A & Navaza J.  \\ 
+1997 & Cell & Levine AJ. \\ 
+1997 & Am. J. Pathol. & Perez-Atayde AR, Sallan SE, Tedrow U, Connors S, Allred E, Folkman J.  \\ 
+1998 & CA: A Cancer Journal for Clinicians & Landis SH, Murray T,  Bolden S, Wingo PA. \\ 
+\hline
+\end{tabular}}
+\vspace{2.5 mm}
+\begin{flushleft}
+Publications at the intersection of all five networks are listed above. All 14 publications are found in the second generation of references(cited\_sid, Fig 2 Right Panel). 
+\end{flushleft}
+\label{table3}
+\end{adjustwidth}
+\end{table}
+\clearpage
 
-\begin{proof} Let $\mathcal{A}_\mathfrak{a}^N$ be the set publications $\{\mathfrak{p}_1,\mathfrak{p}_2,...,\mathfrak{p}_m\} $  written by an author $\mathfrak{a}$ in the whole network $\mathcal{N}$.
-For any $\mathfrak{p}_j \in \mathcal{A}_\mathfrak{a}^N$, lets define sequence of publication $S_r^n (\mathfrak{p}_j)$ be the sequence of publication(with duplicates) having exactly $r$ number of edges  apart in the directed graph of citation Network.
-Then, aggragated citation of a paper  $\mathfrak{p}_j$ in any network $\mathfrak{n}$ can also be written
-$$wc_n(\mathfrak{p}_j) = |S_1^n(\mathfrak{p}_j)| + |S_2^n(\mathfrak{p}_j)|$$ 
-where $|\cdot|$ defined as the length of the sequence. Since for any subnetwork $d_i$, $|S_r^{d_i}| \leq  |S_r^N| $
-for $r \geq1$, we have then,
-
-\begin{equation}
-\begin{split}
-\sum_{i=1}^k wc_{d_i}(\mathfrak{p}_j) &= \sum_{i=1}^k |S_1^{d_i}(\mathfrak{p}_j)| + |S_2^{d_i}(\mathfrak{p}_j)| \\
- &\leq \sum_{i=1}^k |S_1^{N}(\mathfrak{p}_j)| + |S_2^{N}(\mathfrak{p}_j)| \\
- &=k(|S_1^{N}(\mathfrak{p}_j)| + |S_2^{N}(\mathfrak{p}_j)|)\\
- &=k(wc_N(\mathfrak{p}_j))
-\end{split}
-\end{equation}
-
-Next  using  inequality (1) and changing the order of sums due to finite index sum gives,
-
-\begin{equation}
-\begin{split}
-\sum_{i=1}^k pir_{d_i}(\mathfrak{a})&=\sum_{i=1}^k \sum_{j=1}^m wc_{d_i}(\mathfrak{p}_j)=\sum_{j=1}^m \sum_{i=1}^k wc_{d_i}(\mathfrak{p}_j) \\
-&\leq k\sum_{j=1}^m  wc_N(\mathfrak{p}_j) = k (npir(\mathfrak{a}))
-\end{split}
-\end{equation}
-
-which implies that \\
-
-\begin{equation}
-\begin{split}
-\dfrac{1}{k}\leq \dfrac{npir(\mathfrak{a})}{\sum_{i=1}^k pir_{d_i}(\mathfrak{a})}=ppr(\mathfrak{a})
-\end{split}
-\end{equation}
-
-\end{proof}
+\begin{table}[!ht]
+\centering
+\caption{
+{\bf Elite Performers}}
+\vspace{2.5 mm}
+\begin{tabular}{|l| l| l|}
+\hline
+Name& nPIR & PPR \\
+\hline
+\hline
+Ferrara N.	 & 46693 & 1.12 \\ 
+Folkman J. & 23660 & 1.15 \\ 
+Ullrich A. & 23034 & 1.46 \\ 
+Jain R. & 15267 & 1.13 \\ 
+Heldin C.	& 15148 & 1.21 \\ 
+Druker B.	& 15088 & 1.16 \\ 
+Schlessinger J.	& 14996 & 1.48 \\ 
+Dvorak H.	 & 14230 & 1.13 \\ 
+ Alitalo K.	& 13812 & 1.24 \\ 
+ Slamon D. & 13587 & 1.46 \\ 
+ Baselga J. & 12908 & 1.36 \\ 
+ Kantarjian H. & 12029 & 1.17 \\ 
+ Hicklin D.	 & 11775 & 1.17 \\ 
+ Witte O. & 11449 & 1.08 \\ 
+ Hanahan D. & 11072 & 1.19 \\ 
+ Buchdunger E.	 & 11032 & 1.22 \\ 
+ Risau W.	& 10950 & 1.24 \\ 
+ Talpaz M.	 & 10713 & 1.13 \\ 
+ Mendelsohn J.	 & 10534 & 1.54 \\ 
+ Lydon N. & 9988 & 1.18 \\ 
+ Goldman J. & 9927 & 1.11 \\ 
+ Shibuya M. & 9639 & 1.21 \\ 
+ Kitamura Y. & 9486 & 1.24 \\ 
+ Waldmann H. & 9363 & 1.04 \\ 
+ Kerbel R.	 & 9266 & 1.16 \\ 
+  \hline
+\end{tabular}
+\vspace{2.5 mm}
+\begin{flushleft} Researchers with the highest nPIR scores in the network of 5 anti-cancer therapeutics are listed.
+Also shown for each researcher is their PIRpartitionRatio (PPR).
+The nPIR indicates influence across all five networks and the PPR provides an estimate of how this influence is partitioned across each of the five networks (Materials and Methods).
+This list and its ordering should be considered in the context of the data being analyzed and not interpreted as an absolute ordering of research excellence in the field.
+\end{flushleft}
+\label{table2}
+\end{table}
 

### 2017-07-06 Bright_Stars/Submission/submission.tex

--- 2017-06-11 Bright_Stars/LaTeX/preprint.tex
@@
 % WATERMARKS
-\usepackage{draftwatermark}
-\SetWatermarkText{Draft}
-\SetWatermarkScale{3}
+%\usepackage{draftwatermark}
+%\SetWatermarkText{Draft}
+%\SetWatermarkScale{3}
 
@@
 As a proof of principle, we have conducted a case study of five anti-cancer therapeutics.
-We have linked the work of over 235,000 authors in roughly 103,000 scientific publications that capture the research crucial for the development of these five therapeutics.
+We have linked the work of over 235,000 authors in roughly 106,000 scientific publications that capture the research crucial for the development of these five therapeutics.
 We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards.
@@
 For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included.
-For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (below).
-\textbf{[Insert Table 1]}
+For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (Table I).
 
@@
 \centering
+\caption{
+\textbf{Case Studies of Five Anti-Cancer Agents}}
 \scalebox{1}{
@@
 \end{tabular}}
-\vspace{2 mm}
-\caption{
-{\bf Case Studies of Five Anti-Cancer Agents} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies.
+\vspace{2.5 mm}
+\begin {flushleft} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies.
 The unique identifier for each therapeutic is an FDA assigned NDA or BLA number.
 While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic.
-The publication date for each patent is listed in the last column.}
-%\begin{flushleft}  
-%\end{flushleft}
+The publication date for each patent is listed in the last column.
+\end{flushleft}
 \label{table1}
@@
 \centering
+\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases}}
 \scalebox{1}{
@@
 \vspace{2.5 mm}
-\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies.
+\begin{flushleft}
+ Five anti-cancer therapeutics were selected as case studies.
 A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature (Materials and Methods).
 Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve cited publications (cited\_sid).
-Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field}
+Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field.
+\end{flushleft}
 \label{table2}
@@
   \centering
-  \includegraphics[width=.95\linewidth]{citing_pmid.png}
+%  \includegraphics[width=.95\linewidth]{}
   \label{fig:sub1}
@@
   \centering
-  \includegraphics[width=.95\linewidth]{cited_sid.png}
+ % \includegraphics[width=.95\linewidth]{}
   \label{fig:sub2}
@@
 
-The intersection of all five networks consists of 14 publications out of a total of 91,991 unique Scopus identifiers.
+The intersection of all five networks consists of 14 publications out of a total of 106,720 unique Scopus identifiers.
 Strikingly, not even a single publication is common to all five networks at the first generation level (citing\_sid) although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies~\cite{bibKohler}, is cited in four out of five networks.
@@
 \centering
-\scalebox{1.3}{
-\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
+%\scalebox{1.3}{
+%\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
 \caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic.
@@
 \centering
-\includegraphics[scale=0.1]{proj_percent.png}
+%\includegraphics[scale=0.1]{proj_percent.png}
 \caption{{\bf NIH Research Support} Grant and contract support for publications from NIH in the five networks was identified using ExPORTER data (Materials and Methods).
@@
 
-\section*{Supporting Information}
-
-\paragraph*{S1 File.}
-\label{S1_File}
-{\bf Network Calculations} The basis of calculations for network metrics.
-
-\paragraph*{S2 Table 1}
-\label{S2_Table 1}
-{\bf Intersecting Publications Across Networks.}
-
-\paragraph*{S3 Table 2}
-\label{S3_Table 2}
-{\bf Elite Performers in Networks}
+ \nolinenumbers
 
@@
 Falk-Krzesinski from Elsevier for their support of this project.
-
-\nolinenumbers
 
@@
 
+\section*{Supporting Information}
+
+\paragraph*{S1 File.}
+\label{S1_File}
+{\bf Network Calculations} The basis of calculations for network metrics.
+
+\paragraph*{S2 Table 1}
+\label{S2_Table 1}
+{\bf Intersecting Publications Across Networks.}
+
+\paragraph*{S3 Table 2}
+\label{S3_Table 2}
+{\bf Elite Performers in Networks}
+
 \end{thebibliography}

### 2017-07-06 drug_distance.R
adding simple Levenshtein script

@@ -1,0 +1,52 @@
+# This script takes a downloaded database from drugs@fda and imports the Products.txt file
+# into a dataframe. https://www.fda.gov/drugs/informationondrugs/ucm079750.htm
+# Then it extracts a single column of ActiveIngredients into a character
+# vector and grabs the first word of each string in it, suppresses duplicates, sorts, and does
+# minor cleanup. Next it takes all the keywords for a set of publications that are in PubMed
+# xm format, and concatenates all the keywords into a single vector with duplicate suppression.
+# Lastly, it builds a distance matrix between the two vectors, selects perfect matches and prints
+# them out as a sorted list for expert consideration.
+# Author: George Chacko
+# Date 7/6/2017
+
+drugs <- read.csv("~/Desktop/drugsatfda/Products.txt", stringsAsFactors = FALSE, sep = "\t")
+d1 <- casefold(drugs$ActiveIngredient)
+library(stringr)
+d1 <- word(d1, 1)
+d1 <- gsub("\\;$", "", d1)
+d1 <- unique(d1)
+d1 <- sort(d1)
+if (d1[1] == "") {
+	d1 <- d1[-1]
+}
+# test this code
+davey <- read.csv("~/Desktop/pub_med_test.csv", stringsAsFactors = FALSE)
+davey_trim <- davey[, -c(1:5)]
+davey_concat <- vector(mode="character",length=ncol(davey_trim))
+for (i in 1:ncol(davey_trim)) {
+	davey_concat <- c(davey_concat, davey_trim[, i])
+	davey_concat <- unique(davey_concat)
+}
+if (davey_concat[1] == "") {
+	davey_concat <- davey_concat[-1]
+}
+davey_concat <- sort(davey_concat)
+
+# distance matrix based on Levenshtein distances
+davey_dist <- adist(d1, davey_concat)
+# perfect matches
+perfect_hits <- which(davey_dist == 0, arr.ind = T)
+# Print Output
+print(paste("Number of exact matches is", length(perfect_hits[, 1]), sep = " "))
+print(paste("Number of exact matches is", length(perfect_hits[, 1]), sep = " "))
+print(paste("Number of exact matches is", length(perfect_hits[, 1]), sep = " "))
+
+# create vector of results
+final <- vector(mode = "character", length = length(perfect_hits[, 1]))
+for (i in 1:length(perfect_hits[, 1])) {
+	final[i] <- davey_concat[perfect_hits[i, 2]]
+}
+final <- sort(final)
+print(final)
+
+

### 2017-07-08 Bright_Stars/Submission/submission2.tex
begin revision for Sergi

--- 2017-07-06 Bright_Stars/Submission/submission.tex
@@
 
+%% Misc. Packages
+\usepackage{changes}
+\definechangesauthor[name={George Chacko}, color=orange]{gc}
+\setremarkmarkup{(#2)}
+
 \begin{document}
@@
 %Name6 Surname\textsuperscript{2\ddag},
- \& George Chacko\textsuperscript{1*}
+ George Chacko\textsuperscript{1*}
 %with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
@@
 
-\textbf{FDA documents} The drugs@fda website~\cite{bibFDA} was searched for each of the five therapeutics and cited references in the medical review document were manually extracted and matched to pmids.
-FDA Approval Summaries published in journals by FDA staff, were available for all five therapeutics and contain cited references.
+\textbf{FDA documents} The drugs@fda website~\cite{bibFDA} was searched for each of the five therapeutics.
+\added[id=gc,remark={response to request from editor}]{The medical review document was copied from the Review section under Approval Date(s) and History, Letters, Labels, Reviews and cited references in the medical review document were manually extracted and matched to pmids using, as search terms in the PubMed GUI, text strings from the citation that, typically, consisted of the last name of the first author, 3-5 words of the title, the year of publication, and journal name.} FDA Approval Summaries published in journals by FDA staff, were available for all five therapeutics and contain cited references.
 If the published date of a cited reference in an Approval Summary exceeded the approval date plus two months, the publication was not included.
 
-\textbf{Patents} For each therapeutic a single patent was identified that best represented the most relevant invention to the therapeutic at hand.
-Identification of this patent was performed using multiple web sources.
-The US patent number was then used to identify the patent and the non-patent citation list from Google Patents ~\cite{bibGooglePatents} was manually processed by searching PubMed for appropriate pmids.
-The accuracy of manual searches was far higher than a citation matching tool that we developed for for this purpose,and were used to generate the data in this study.
+\textbf{Patents} For each therapeutic\deleted[id=gc,remark=revise for clarity]{a single patent was identified that best represented the most relevant invention to the therapeutic at hand}\added[id=gc,remark=revised]{, the original patent for the therapeutic in question was identified using a combination of web searches, Google Patents, and the scientific literature}.
+\deleted[id=gc,remark=restate]{Identification of this patent was performed using multiple web sources.
+The US patent number was then used to identify the patent...} \added[id=gc,remark={use example}]{For example, US5521184, the original patent for imatinib was assigned to the Ciba-Geigy Corporation in 1996 listing Zimmermann as inventor.
+Such manual identification is greatly assisted by a knowledge of the drug development field}.
+The non-patent citation list for a patent was copied from Google Patents~\cite{bibGooglePatents} and manually processed by searching the PubMed GUI for appropriate pmids \added[id=gc,remark={response to request from editor}] {using text strings from the citation that, typically, consisted of the last name of the first author, 3-5 words of the title, the year of publication, and journal name.
+Returned hits were inspected for matches to the original citation in Google Patents and accepted only in the event of a high-degree of confidence in correctness} The accuracy of manual searches was far higher than a citation matching tool that we developed for for this purpose and were used to generate the data in this study.
 
@@
 All data used in this study were acquired exclusively from the sources listed above.
+\added[id=gc,remark={response to request from editor}]{Data used to generate the figures and tables in this study are available in a Mendeley Data repository~\cite{bibMendeley}}.
 Computations were performed on infrastructure owned or leased by NET ESolutions, Elsevier, or the Gladstone Institutes.
@@
 
+\added[id=gc,remark={expanded discussion of generalizability as per editor request}]{Here, we started with the literature directly cited in the approval process for five therapeutics, which are subject to multiple layers of independent assessment, i.e., patent awards, clinical trials, and FDA reviews that in turn contribute to the relevant literature.
+However, the only requirement of the current method is a starting set of articles.
+Any question premised upon the citation record and defined by a nucleus of articles can be addressed with this approach.
+The method is applicable to any other therapeutic or set of therapeutics, but also to medical devices, diagnostics, standards development, and research discoveries and protocols such as induced pluripotent (IPS) cells  or CRISPR-Cas9.
+Furthermore, the method is generalizable to sets of articles defined by groups of authors (e.g., consortia, programs), by institutions or departments, or by grant portfolios.
+The application of our method to the bibliographic record of a department, for example, would provide novel, network-based metrics by which to assess collaboration, productivity, translational impact, etc.
+No matter the application, the method is implicitly time-dependent, allowing one to make historical comparisons and to set future goals.
+Importantly, our improvements to the method as presented here allow for the analysis across sets of articles in addition to within, supporting higher level interrogations of the crosstalk and collaborations that connect groups.}
+
 In summary, we have demonstrated a digital methodology based on data mining and network analysis, not restricted to  drug discovery and cures alone, that offers burden-reduction in explorations of science history.
@@
 
+\bibitem{bibMendeley}
+Keserci S, Livingston, E, Wan  Lingtian, Pico A, Chacko, G.
+\newblock {{B}right Stars in Neighboring Constellations v4.}
+\newblock Mendeley Data http://dx.doi.org/10.17632/ysh53v7gpz.4
+
 \bibitem{bibGithub}

### 2017-07-10 Bright_Stars/Submission/submission2.tex
latest edits

@@
 This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
-As a proof of principle, we have conducted a case study of five anti-cancer therapeutics.
-We have linked the work of over 235,000 authors in roughly 106,000 scientific publications that capture the research crucial for the development of these five therapeutics.
+As proof of principle, we have conducted a case study of five anti-cancer therapeutics \added[id=gc,remark={expanded Abstract to state question of interest}]{to identify the collaborations that resulted in the successful development of these therapeutics as well as nodes of influence in these networks.} We have linked the work of over 235,000 authors in roughly 106,000 scientific publications that capture the research crucial for the development of these five therapeutics.
 We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards.
@@
 Reconstructing such networks enables a deeper contextual understanding of knowledge diffusion across disciplines, scientific interests, culture, and time~\cite{bibMaldame}.
-Such studies also (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases \cite {bibLauer} (ii) support strategic communications to oversight bodies, and (iii) help communicate the societal value of research.
+Such studies also (i) provide evidence for the broad collaborative platform of basic and translational research underlying major scientific advances such as cures for diseases \cite {bibLauer} (ii) support strategic communications, and (iii) help communicate the societal value of research.
 The understanding of a therapeutic network, when coupled with information from clinical use of a therapeutic, also enables a recursive learning of the pathogenesis of the disease it is being used to treat, as has been noted for the burgeoning field of immunotherapeutics~\cite{bibChan}.
@@
 Williams and colleagues have elegantly demonstrated the feasibility and value of data mining and network analysis using, as case studies, ivacaftor and ipilimumab, approved for the treatment of cystic fibrosis and melanoma respectively (\textit{vide supra}).
+Key assumptions in constructing these networks were that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will reveal previous influential discovery.
 They observed that `the nature of a cure discovery network is complex and fundamentally collaborative', noting in the case of ivacaftor, that at least 7,067 scientists with 5,666 unique affiliations contributed to ivacaftor-relevant research over a period greater than 100 years.
 These authors also suggest that thoughtful metrics derived from this concept could inform decision making by funders.
+.
 
-Extending the methodology to study additional cures and significant research advances is a logical next step.
-Ascertaining the nature of the interactions, if any, between networks, is also of considerable interest since it supports an understanding of collaboration across networks as well as common features of science networks.
-Lastly, even if ambitious, scaling from case studies to mapping the entire domain of drug development is likely to be beneficial in planning, resource allocation and optimization of drug development activities.
-
-To address these questions, we have built upon prior art for single networks to (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extended single network analysis to map publications and authors across multiple networks.
-Key assumptions in constructing these networks are that the references found in relevant documents are appropriate citations of new knowledge relevant to a given cure and that a further retrospective round of citation discovery will reveal previous influential discovery~\cite{bibWilliams}.
-For evaluation, we have conducted case studies of a cluster of five FDA-approved therapeutics for cancer.
-We present the results of this case study as a body of work for further study by other researchers, and a step towards mapping the universe of FDA-approved drugs and biologicals.
+ \added[id=gc,remark={clarification of question as per journal request}]{In this study, we document the collaboration networks underlying five FDA-approved therapeutics for cancer.
+Building upon prior art for single networks we (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extend single network analysis to map publications and authors across multiple networks.
+In addition, we identify collaboration across networks and describe the role of funding and peer review outlining a system of layered collaborative activity in scientific discover.
+By studying additional cures and research advances, we also proceed towards scaling from single case studies to mapping the entire domain of drug development with the expectation that such knowledge will be beneficial in planning, resource allocation and optimization of drug development research.
+We present the results of this case study as a body of work for further study by other researchers, and a step towards mapping the universe of FDA-approved drugs and biologicals.}
 
@@
 \textbf{FDA documents} The drugs@fda website~\cite{bibFDA} was searched for each of the five therapeutics.
-\added[id=gc,remark={response to request from editor}]{The medical review document was copied from the Review section under Approval Date(s) and History, Letters, Labels, Reviews and cited references in the medical review document were manually extracted and matched to pmids using, as search terms in the PubMed GUI, text strings from the citation that, typically, consisted of the last name of the first author, 3-5 words of the title, the year of publication, and journal name.} FDA Approval Summaries published in journals by FDA staff, were available for all five therapeutics and contain cited references.
+\added[id=gc,remark={response to request from editor}]{Under Approval Date(s) and History, Letters, Labels, Reviews, the medical review document was copied.
+Cited references in the medical review document were manually extracted and matched to pmids using, as search terms in the PubMed GUI, text strings from the citation that, typically, consisted of the last name of the first author, 3-5 words of the title, the year of publication, and journal name.} FDA Approval Summaries published in journals by FDA staff, were available for all five therapeutics and contain cited references.
 If the published date of a cited reference in an Approval Summary exceeded the approval date plus two months, the publication was not included.
@@
 The US patent number was then used to identify the patent...} \added[id=gc,remark={use example}]{For example, US5521184, the original patent for imatinib was assigned to the Ciba-Geigy Corporation in 1996 listing Zimmermann as inventor.
-Such manual identification is greatly assisted by a knowledge of the drug development field}.
+Manual identification is assisted by a knowledge of the field}.
 The non-patent citation list for a patent was copied from Google Patents~\cite{bibGooglePatents} and manually processed by searching the PubMed GUI for appropriate pmids \added[id=gc,remark={response to request from editor}] {using text strings from the citation that, typically, consisted of the last name of the first author, 3-5 words of the title, the year of publication, and journal name.
-Returned hits were inspected for matches to the original citation in Google Patents and accepted only in the event of a high-degree of confidence in correctness} The accuracy of manual searches was far higher than a citation matching tool that we developed for for this purpose and were used to generate the data in this study.
+Returned hits were inspected for matches to the original citation in Google Patents and accepted only in the event of a high-degree of confidence in correctness} The accuracy of manual searches was far higher than a citation matching tool that we developed for this purpose and were used to generate the data in this study.
 
@@
 \textbf{PubMed and Scopus} Citing\_pmids from the five different sources above  were combined and deduplicated.
-Using the Scopus database and its APIs.
-The manually-generated list of pmids taken from the five sources mentioned (Clinical Trials, FDA Documents, Patents, Post-Approval Literature, and Pre-Approval Literature Searches) were searched in Scopus, using the basic Scopus Search API, to arrive at a list of Scopus IDs (citing\_sid) for the publications.
+Using the Scopus database and its APIs, the manually-generated list of pmids taken from the five sources mentioned (Clinical Trials, FDA Documents, Patents, Post-Approval Literature, and Pre-Approval Literature Searches) were searched in Scopus, using the basic Scopus Search API, to arrive at a list of Scopus IDs (citing\_sid) for the publications.
 The Scopus Abstract Retrieval API was then used to retrieve a more comprehensive record for each of the SIDs comprising that list of publications Next, for each of these publication records citing\_sid), we used the Scopus Author Retrieval API to retrieve a full record for each unique author in the  publication set.
@@
 This allowed us to more precisely arrive at publication totals for only those publication types that are relevant for this study.
-[which are]
+\added[id=gc,remark={clarification on network calcuation}]{For the gRBR metric (below), we counted only article and article in press when computing total researcher productivity.}
 
@@
 Code and scripts used in this study were written in Java, Python, and R and are archived on a publicly accessible Github repository~\cite{bibGithub}.
-Network visualization was performed using Cytoscape~\cite{bibCytoscape}.
+\added[id=gc,remark={details of new computing procedures}] {The publicly available codes of the Williams study~\cite{bibLotia} were used as the basis for designing the codes used in our study.
+The previous codes were designed to generate graph objects and make use of graph methods such as breadth-first search (BFS) and depth-first search (DFS for graph traversal.
+In our approach, we used basic data structures like hash maps, hash sets, lists and aggregations and enriched the data with grants and peer review data.
+In the Williams study, assembly and analysis of each network took roughly 17 hours per drug, 10 of which are manual processing steps.
+While our process also involved expert level curation of a foundational set of references for each drug with a cost of roughly 2-5 hours, our network calculations and metrics ran in the order of minutes once the bibliometric data were assembled.} Network visualization was performed using Cytoscape~\cite{bibCytoscape}.
 
@@
 
-\textbf{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information).
+\textbf{Network Metrics}  \added[id=gc,remark={revise discussion of methodological advances}]{We built upon the work of Williams~\cite{bibWilliams} in several ways.
+Author disambiguation in the their code was not addressed beyond clustering by last name and first names.
+Further, network data were limited to authors, institutions and PMIDs and did not include cited grants and peer review data.
+We addressed author disambiguation through the use of Scopus authorIDs and enriched the data with grants and peer review data.
+Whereas, the original code was designed to handle a single drug and was never applied to a problem larger than 5000 articles, our code scales to larger article numbers and our metrics include cross-network calculations.To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information).
 The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks.
@@
 A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied.
-Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch} although other data related issues may well emerge.
+Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch}, although other data related issues may well emerge.}
 
@@
 
-\added[id=gc,remark={expanded discussion of generalizability as per editor request}]{Here, we started with the literature directly cited in the approval process for five therapeutics, which are subject to multiple layers of independent assessment, i.e., patent awards, clinical trials, and FDA reviews that in turn contribute to the relevant literature.
+\added[id=gc,remark={expanded discussion of generalizability as per editor request}]{In this study, we begin with the literature directly cited in the approval process for five therapeutics.
+The approval process for therapeutics is subject to multiple layers of independent assessment, i.e., patent awards, clinical trials, and FDA reviews, each of which cite relevant literature.
 However, the only requirement of the current method is a starting set of articles.
-Any question premised upon the citation record and defined by a nucleus of articles can be addressed with this approach.
-The method is applicable to any other therapeutic or set of therapeutics, but also to medical devices, diagnostics, standards development, and research discoveries and protocols such as induced pluripotent (IPS) cells  or CRISPR-Cas9.
-Furthermore, the method is generalizable to sets of articles defined by groups of authors (e.g., consortia, programs), by institutions or departments, or by grant portfolios.
-The application of our method to the bibliographic record of a department, for example, would provide novel, network-based metrics by which to assess collaboration, productivity, translational impact, etc.
+The method is applicable to any other therapeutic or set of therapeutics, but also to medical devices, diagnostics, standards development, and research discoveries and protocols such as induced pluripotent stem (iPS) cells~\cite{bibIPS}  or CRISPR-Cas9~\cite{bibCRISPR}.
+Thus, any question premised upon accessible citation records and defined by a nucleus of articles can be addressed with our approach.
+Furthermore, the method is also generalizable to sets of articles defined by groups of authors (e.g., consortia, programs), by institutions or departments, or by grant portfolios.
+The application of our method to the bibliographic record of a department, for example, would provide novel, network-based metrics by which to assess collaboration, productivity, and translational impact.
 No matter the application, the method is implicitly time-dependent, allowing one to make historical comparisons and to set future goals.
@@
 Beyond assembling a set of facts about a major scientific advance, it contributes to the understanding of collaboration across domains and can be used to  enrich portfolio analysis, planning and optimization, as well as communications of the societal value of research.
-The approach can be easily adapted to study the collaborative history within and across research portfolios of groups of researchers and targeted programs such as the Clinical and Translational Science Award (CTSA) Program.
-While finer critical evaluation of the content of datasets generated through this approach is best left to experts, the methodology is broadly accessible and can also be viewed as another tool for citizen science.
-Overall, no single metric will provide useful answers, instead expert interpretation of multiple metrics best matched to curated datasets will be valuable.
+The approach can be easily adapted to study the collaborative history within and across research portfolios of groups of researchers and targeted programs.
+\deleted[id=gc,remark={delete in view of previous paragraph}]{such as the Clinical and Translational Science Award (CTSA) Program.} While finer critical evaluation of the content of datasets generated through this approach is best left to experts, the methodology is broadly accessible and can be viewed as another tool for citizen science.
+Overall, no single metric will provide useful answers, instead expert interpretation of multiple metrics best matched to curated datasets will be of value.
 
@@
  \section*{Acknowledgments} This study would not have been possible without data that is made publicly available by NIH and the FDA.
-We thank Tandy Warnow for critical comments and advice on formalizing definitions.
-We thank Sandeep Somaiya from NETE and Holly J.
-Falk-Krzesinski from Elsevier for their support of this project.
+We thank Tandy Warnow from the University of Illinois Urbana-Champaign for critical comments and advice on formalizing definitions.
+We also thank Sandeep Somaiya from NETE and Holly J.
+Falk-Krzesinski, Daniel Calto, M'hamed Aisati, and Sherif El Shamy from Elsevier for their support of this collaboration.
 
@@
 
+\bibitem{bibLotia}
+Lotia, S., and Pico, A.P. 
+\newblock {{Gladstone Bibliometrics}
+\newblock https://github.com/ gladstone-institutes/bibliometrics/tree/1.0.1.
+
 \bibitem{bibCytoscape}
@@
 
+\bibitem{bibIPS}
+Takahashi K, Yamanaka S.
+\newblock {{I}nduction of pluripotent stem cells from mouse embryonic and adult fibroblast cultures by defined factors}
+\newblock  Cell. 2006. 25;126(4):663-76.
+
+\bibitem{bibCRISPR}
+Charpentier E, Doudna JA.
+\newblock {{B}iotechnology: Rewriting a genome}
+\newblock  Nature. 2013 7;495(7439):50-1. doi: 10.1038/495050a.
+
+\end{thebibliography}
+
 \section*{Supporting Information}
@@
 
-\end{thebibliography}
 \end{document}

### 2017-07-11 Bright_Stars/Submission/submission2.tex
update

@@
 % Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
+\usepackage{change}
 
@@
 % Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{last,fancyhdr,graphicx}
 \usepackage{epstopdf}
@@
 \setremarkmarkup{(#2)}
+\usepackage{listings}
 
@@
 These advances are invariably collaborative, involving the contributions of many scientists to a discovery network in which theory and experiment are built upon.
-To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic.
-This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.
-As proof of principle, we have conducted a case study of five anti-cancer therapeutics \added[id=gc,remark={expanded Abstract to state question of interest}]{to identify the collaborations that resulted in the successful development of these therapeutics as well as nodes of influence in these networks.} We have linked the work of over 235,000 authors in roughly 106,000 scientific publications that capture the research crucial for the development of these five therapeutics.
+To document and understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic.
+This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.\added[id=gc,remark={expanded Abstract to state question of interest}]{ Building upon prior art, we have conducted a case study of five anti-cancer therapeutics to identify the collaborations that resulted in the successful development of these therapeutics both within and across their respecive networks.} We have linked the work of over 235,000 authors in roughly 106,000 scientific publications that capture the research crucial for the development of these five therapeutics.
 We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards.
@@
  \added[id=gc,remark={clarification of question as per journal request}]{In this study, we document the collaboration networks underlying five FDA-approved therapeutics for cancer.
-Building upon prior art for single networks we (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extend single network analysis to map publications and authors across multiple networks.
-In addition, we identify collaboration across networks and describe the role of funding and peer review outlining a system of layered collaborative activity in scientific discover.
+Building upon prior art for single networks we (i) extend single network analysis to map publications and authors across multiple networks (ii) include information on research awards and peer review of grants (iii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iv) incorporate modified network metrics and data mining methods.
+We observe collaboration that extends across networks and describe the role of funding and peer review in sustaining a system of layered collaborative activity in scientific discovery.
 By studying additional cures and research advances, we also proceed towards scaling from single case studies to mapping the entire domain of drug development with the expectation that such knowledge will be beneficial in planning, resource allocation and optimization of drug development research.
@@
 \added[id=gc,remark={response to request from editor}]{Data used to generate the figures and tables in this study are available in a Mendeley Data repository~\cite{bibMendeley}}.
-Computations were performed on infrastructure owned or leased by NET ESolutions, Elsevier, or the Gladstone Institutes.
+Computations were performed on infrastructure owned or leased by NETE Solutions, Elsevier, or the Gladstone Institutes.
 Code and scripts used in this study were written in Java, Python, and R and are archived on a publicly accessible Github repository~\cite{bibGithub}.
@@
 The previous codes were designed to generate graph objects and make use of graph methods such as breadth-first search (BFS) and depth-first search (DFS for graph traversal.
-In our approach, we used basic data structures like hash maps, hash sets, lists and aggregations and enriched the data with grants and peer review data.
+In our approach, we used basic data structures like hash maps, hash sets, lists and aggregations and enriched the first generation set of references with data from Scopus, which indexes more scientific journals~\cite{bibFalagas}, cited references from post-approval literature reviews, cited references from FDA Approval Summaries, direct PubMed searches, grants and peer review data.
 In the Williams study, assembly and analysis of each network took roughly 17 hours per drug, 10 of which are manual processing steps.
-While our process also involved expert level curation of a foundational set of references for each drug with a cost of roughly 2-5 hours, our network calculations and metrics ran in the order of minutes once the bibliometric data were assembled.} Network visualization was performed using Cytoscape~\cite{bibCytoscape}.
+While our process also involved expert level curation of a foundational set of references for each drug with a cost of roughly 2-5 hours, our network calculations and metrics ran in the order of minutes once the bibliometric data were assembled.} Network visualization was performed using Cytoscape~\cite{bibCytoscape}.}
 
@@
 \begin{figure}[!h]
-\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
@@
 \label{fig: test}
-\end{adjustwidth}
+%\end{adjustwidth}
 \end{figure}
@@
 \label{fig2}
-\end{adjustwidth}
+%\end{adjustwidth}
 \end{figure}
@@
 \label{fig3}
-\end{adjustwidth}
+%\end{adjustwidth}
 \end{figure}
@@
 A more accurate estimate would be possible if historical records of participation in peer review were made publicly available by NIH.
-We do not have records of awards or peer review from sources other than NIH and this also is a focus of future investigation.
+We do not have records of funding awards or peer review from sources other than NIH and this is a focus of future investigation.
 
-\textbf{Network Metrics}  \added[id=gc,remark={revise discussion of methodological advances}]{We built upon the work of Williams~\cite{bibWilliams} in several ways.
-Author disambiguation in the their code was not addressed beyond clustering by last name and first names.
+\textbf{Network Metrics}  \added[id=gc,remark={revise discussion of methodological advances}]{We have built upon the work of Williams~\cite{bibWilliams} in several ways.
+Author disambiguation in their code was not addressed beyond clustering by last name and first names.
 Further, network data were limited to authors, institutions and PMIDs and did not include cited grants and peer review data.
 We addressed author disambiguation through the use of Scopus authorIDs and enriched the data with grants and peer review data.
-Whereas, the original code was designed to handle a single drug and was never applied to a problem larger than 5000 articles, our code scales to larger article numbers and our metrics include cross-network calculations.To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information).
+Whereas, the original code was designed to handle a single drug and was never applied to a problem larger than 5000 articles, our approach scales to over 100,000 articles and our metrics include cross-network calculations.To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as the new nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information).
 The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks.
-The PIRpartitionRatio (PPR) results from normalizing nPIR to the sum of individual PIR scores to gain insight into holo-network influence.
+The PIRpartitionRatio (PPR) is calculated from normalizing the nPIR metric for an researcher to the sum of the researcher's individual PIR scores for each network being studied.
 A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied.
@@
 
-While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher, which is sensitive to data quality in bibliometric databases.
+While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher, which in turn depends on data quality in bibliometric databases.
 We found several instances in the top 10\% of PIR scores where the gRBR was implausible likely on account of polysemy, synonymy, or incompleteness.
@@
 These metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (\nameref{S3_Table 2}).
-These `bright stars in neighboring constellations', represent elite performers in network(s) of clinical and basic science expertise again reinforcing the concept of collaborative translational achievements built upon a body of basic science.
+These `bright stars' are elite performers in network(s) of clinical and basic science researchers that reinforce the concept of collaborative translational achievements built upon a body of basic science.
 Beyond simple aggregation, weighting, and normalization that we have used, a variety of citation metrics such as SNIP~\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study~\cite{bibIoannidis}.
-The use of these citation measures will assume greater importance when scale up from small numbers of networks to a greater proportion of the global network.
+The use of these citation measures will assume greater importance with scale up from small numbers of networks to a greater proportion of the global research network.
 
@@
 \deleted[id=gc,remark={delete in view of previous paragraph}]{such as the Clinical and Translational Science Award (CTSA) Program.} While finer critical evaluation of the content of datasets generated through this approach is best left to experts, the methodology is broadly accessible and can be viewed as another tool for citizen science.
-Overall, no single metric will provide useful answers, instead expert interpretation of multiple metrics best matched to curated datasets will be of value.
+Overall, no single metric will provide very useful answers, instead expert interpretation of multiple metrics best matched to curated datasets will be of value.
 
@@
 \newblock Mendeley Data http://dx.doi.org/10.17632/ysh53v7gpz.4
+
+\bibitem{bibFalagas}
+Falagas ME, Pitsouni EI, Malietzis GA, Pappas G.
+\newblock{{C}omparison of PubMed, Scopus, Web of Science, and Google Scholar: strengths and weaknesses.}
+\newblock FASEB J. 2008 22(2):338-42.
 

### 2017-07-11 Bright_Stars/Submission/submission2.tex
second submission version as sent to PLOS One

@@
 % Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{change}
+\usepackage{changepage}
 
@@
 % Header and Footer with logo
-\usepackage{last,fancyhdr,graphicx}
+\usepackage{lastpage,fancyhdr,graphicx}
 \usepackage{epstopdf}
@@
 %% Misc. Packages
-\usepackage{changes}
+\usepackage[final]{changes}
 \definechangesauthor[name={George Chacko}, color=orange]{gc}
@@
 %\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
-\caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic.
+\caption{{\bf Core Publications in Networks}  The outer arcs of blue nodes identifies first generation publications (citing\_sid) for each therapeutic.
 Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5).
@@
 
-\textbf{Network Metrics}  \added[id=gc,remark={revise discussion of methodological advances}]{We have built upon the work of Williams~\cite{bibWilliams} in several ways.
-Author disambiguation in their code was not addressed beyond clustering by last name and first names.
-Further, network data were limited to authors, institutions and PMIDs and did not include cited grants and peer review data.
-We addressed author disambiguation through the use of Scopus authorIDs and enriched the data with grants and peer review data.
-Whereas, the original code was designed to handle a single drug and was never applied to a problem larger than 5000 articles, our approach scales to over 100,000 articles and our metrics include cross-network calculations.To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as the new nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information).
+\textbf{Network Metrics}  \added[id=gc,remark={revise discussion of methodological advances}]{We have built upon the work of Williams~\cite{bibWilliams} by addressing author disambiguation through the use of Scopus authorIDs and enriching the network data with grants and peer review data.
+Whereas, the original code was designed to handle a single drug and was not applied to a problem larger than 5000 articles, our approach scales to over 100,000 articles and our metrics include cross-network calculations.To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as the new nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information).
 The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks.
-The PIRpartitionRatio (PPR) is calculated from normalizing the nPIR metric for an researcher to the sum of the researcher's individual PIR scores for each network being studied.
+The PIRpartitionRatio (PPR) normalizes the nPIR metric for an researcher to the sum of the researcher's individual PIR scores for each network being studied.
 A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied.
@@
 K\"ohler, G., Milstein, C.
-\newblock { {C}ontinuous cultures of fused cells secreting antibody of predefined specificity.}
+\newblock {{C}ontinuous cultures of fused cells secreting antibody of predefined specificity.}
 \newblock Nature. 1975 256: 495-497.
